### 2020-08-15 templates_aimusic2020/paper.tex
Updates from Overleaf

%%%%%%%%%%%%%%%%%%%% file CSMC_MUME_LaTeX_Template.tex %%%%%%%%%%%%%%%%%%%%%
%
% This is the LaTeX source for the instructions to authors using
% the LaTeX document class 'llncs.cls' for contributions to
% the Journal of Creative Music Systems.
% Copyright: http://www.springer.com/lncs       Springer Heidelberg 2006/05/04
%
% It may be used as a template for your own input - copy it
% to a new file with a new name and use it as the basis
% for your article.
%
% NB: the document class 'llncs' has its own and detailed documentation, see
% ftp://ftp.springer.de/data/pubftp/pub/tex/latex/llncs/latex2e/llncsdoc.pdf
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[runningheads,a4paper]{llncs}

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{url}
\usepackage{apacite}
%added 
\usepackage[inline]{enumitem}    
\usepackage{subcaption}
\usepackage{caption}
\usepackage{threeparttable} %annotations for table
\usepackage{csquotes}

\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

\pagestyle{headings}

\begin{document}

\mainmatter  % start of an individual contribution

% first the title is needed
\title{Percussive Sound Generation with Virtual Listeners and Modular Synthesizers}

% a short form should be given in case it is too long for the running head
\titlerunning{Virtual Percussive Sound Generation}

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
\author{Amir Salimi \and Abram Hindle}
%
% if the names of the authors are too long for the running head, please use the format: AuthorA et al.
\authorrunning{Amir Salimi and Abram Hindle }

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{Department of Computing Science\\ University of Alberta \\ \email{asalimi@ualberta.ca}}

%
% NB: a more complex sample for affiliations and the mapping to the
% corresponding authors can be found in the file "llncs.dem"
% (search for the string "\mainmatter" where a contribution starts).
% "llncs.dem" accompanies the document class "llncs.cls".
%

\maketitle

\begin{abstract}
Digital sound artists often require a variety of percussive samples for their music. For more than two decades research involving digital synthesis, heuristic search, and neural networks has been used for the generation of novel sounds. Our goal is to generate one-shot percussive samples by leveraging modern AI technologies alongside scalable signal generation methods. We centered our approach around the combination of two central components: \begin {enumerate*} [label=(\roman*)] \item a \emph{virtual ear} capable of evaluating the proximity of unheard sounds to  and \item a dynamic \emph{virtual synthesizer} with a rich set of tractable parameters\end{enumerate*}. We present a generative pipeline that utilizes robust digital signal processing methods guided by supervised learning towards the generation of one-shot percussive sounds. We present our findings and measurements of the various approaches taken. Advantages, shortcomings and practicality of the employed methodologies are demonstrated. We share our curated dataset of sounds and codebase\footnote{\url{https://github.com/imilas/Synths_Stacks_Search}} which can be used for its further expansion.
\keywords{Automatic Synthesizer design. Machine Listening. Sound Analysis. Novelty and Originality}
\end{abstract}

\section{Preamble}
\subsection{Drums and Percussion}
Drums are a subcategory of percussive instruments. Drum sounds such as kick and snare are two of the most universally recognized examples of percussion~\cite{barry2005drum}. Almost any object which is struck to produce noise can be referred to as a drum~\cite{latham2002oxford}. The term \enquote{Percussion} often encompasses all drums and may include the additional instruments which may be rubbed, plucked, blown, etc; A more strict definition of percussion can be used interchangeably with drums~\cite{latham2002oxford}. We adapt this strict definition for this work as our concern is not the delineation between the two overlapping concepts, but with extraction and creation of novel sounds with characteristics shared between the two. As a result, we often use the terms \enquote{drum} and \enquote{percussion} interchangeably.

\subsection{Motivation and Goals}
Digital recordings of novel, one-shot\footnote{A single hit on the drum that captures its capabilities} drum sounds are not easy or cheap to find. Our goal here is to create a new, virtual source of novel drum sounds, which could then be used in electronic music compositions.

By relying on recordings of \textit{real life} drum sounds, we are limited by what instruments exist in the real world and whether or not we have access to clean, one-shot recordings. Our hypothesis is that the virtualization of sound generation can alleviate these material limitations.

\subsection{What Solution Do We Propose?}
To virtually create novel drum sounds, we need a generative source; One that produces audio based on some instructions. We also need a method of evaluation to help us determine which sounds resemble drums and are worth keeping. We also would like to know what instructions caused our audio source to make the sounds we liked. In short, our approach requires effective \textit{generation} and \textit{evaluation} of sounds. 
\subsection{How Can a Computer Make Sounds?}
Sounds are transmitted via waveforms. Your computer can emulate the physical characteristics of basic waveforms by evaluating the output of periodic functions such as sines and cosines. Evaluation of basic periodic functions is the simplest form of software audio generation~\cite{mitchell2009basicsynthChap5}.
This generative system is called an \textit{oscillator} and its output is a waveform which can be sent to your computer's digital-to-analog conversion system to create an audible signal. The combination and modification of these pure tones are the building blocks of digital signal processing (DSP).

\begin{figure*}[h]
\label{fig_example_sine}
\centering
\includegraphics[width=0.45\linewidth,angle =-90 ]{images/periodic_function.png}
\caption{A computer can simulate waveforms by utilizing periodic functions. Digital waveforms are discrete approximations of analogue waves. \cite{mitchell2009basicsynthChap5} }
\end{figure*}

 Most organic sounds---sounds from the natural environment, and its flora and fauna---are much more complex than the output of a single oscillator. However, with careful programming, DSP techniques can be used to replicate almost any sound, which is why they have powered commercial digital synthesizers for over half a century \cite{jenkins2019analog}. Another advantage to using DSP for sound generation is that the synthesizers we build using these functions are tractable: the output is determined by the input and reproducible. This makes the evaluation of a set of inputs (or parameters) to our synthesizers  simpler compared to the evaluation of synthesizers that utilize probabilistic models.

\subsection{How Can a Computer Evaluate Sounds?}
Automatic evaluation of sounds is an essential component of our work: A thorough manual evaluation of outputs is not possible when hundreds can be created in a second. In our work, we find simple features such as frequency content (high pitch vs low pitch), length, and envelope (change in loudness, how fast the sounds reaches its maximum loudness and fades away) to be powerful for the categorization of drum sounds. Later on we will discuss our algorithms for extraction of these and other features in~\ref{implementation}. We will also discuss how these extracted features were used to train models that can automatically categorize new sounds.

\section{What Is Our Methodology?}
\label{sec_methodology}
We conceptualized a general pipeline for approximation of sounds: A synthesizer creates random noise while a virtual ear rapidly evaluates the outputs and outputs a score which is used for the separation of undesired outputs from desired ones. This approach assumes that a fraction of the randomly generated sounds can be substituted for percussion and that the synthetic ear will assign higher evaluation scores to this subset. Our implementation allows for the improvement of heuristic search algorithms such that the parameters of the synthesizer can be selected based on the previously observed evaluations. Following this idea, we found the proper implementation of 2 major components to be crucial:

\begin{itemize}
    \item \textit{Virtual Synthesizer}: A flexible, deter\-min\-istic, and tract\-able gener\-ator which can create audio. 
    \item \textit{Virtual Ear}: An ear that returns an evaluation of an audio sample; estimating the effectiveness of an audio sample's fulfillment of a producers requirements. The ear's evaluation guides the generation process towards a desired path, making it a crucial component of our pipeline. 
\end{itemize}

Our components are designed with modularity and parallelizability in mind. This allows each component to be debugged, modified, and improved without requiring modifications in other components while additionally increasing the scalability and speed of experiments. 
Section~\ref{implementation} contains further discussion of the components as well as the code that glues the project together.

While the main focus of this project is the generation of novel percussive sounds, our methodology indicates promising results with regards to creation of new presets for any virtual synth without the need for a-priori knowledge of the functions or its parameters (i.e the effect of parameter modulation on the sonic output). We also demonstrate the viability of a virtual synthesizers based on Digital Signal Processing (DSP) methods for fast, unsupervised creation of novel audio.

% Instead of learning weights and parameters in an audio-generation neural network, we wish to generate, search, and tune synthesizers to produce percussion sounds. Discussed in more detail in section \ref{related}.

\section{Restating the Goal}
We wish to leverage AI technologies, heuristic search, and DSP methods for the synthesis of novel audio. The work here is motivated by the idea of finding new, convenient methods for the expansion of a music producer's library of sounds. We demonstrate our work in combining machine listening and automatic synthesizer programming to find pieces of audio which can be used as drums. Using the generation of short, percussive audio samples as a starting point, this project is a proof of concept for a modular, generative pipeline of novel, one-shot audio samples. Design decisions were made such that this approach can be modified for creation of other, non-percussive sound-types.

\chapter{Background and Related Work}
\label{section:background}
This chapter aims to provide a background for the subsequent chapters via a quick overview of four important topics:\\ 
\begin{enumerate}[label=(\roman*)]
\item Digital sound, its features and concepts that have been fundamental to our work.
\item A quick overview of common digital synthesis techniques.
\item Discussion on the applications of artificial neural networks (ANNs) for feature extraction and sound production. Although similar results can be yielded from either approach, we distinguish ANN based techniques from tradition digital signal processing (DSP).
\item Related works and their relative similarities and distinctions.
\end{enumerate}
\section{Digital Audio: Sound from Numbers}
Sound is the result of a series of physical events. Most of what we hear is the product of physical disturbances, causing vibrations in our mutually shared, immersive mediums (air, hopefully). Sound waves carry these vibrations through air as part of an expanding, spherical wave front; Exponentially losing intensity as they travel away from the source~\cite{cook1999chap4}. 
\\\\

[graph describing wave amplitude, phase and frequency here]
\\\\
A sound wave can be viewed as the result of a function which governs amplitude through time, where time and amplitude exist in continuous dimensions. Waves can be approximated via a series of samples, associating time steps to a discrete range of amplitude values. 
Given a wave generation method, computers can make sound by sending a series of discrete values to a digital-to-analogue chip, which in turn can
create vibrations within a speaker.  \textit{Digital synthesis} of audio is the process of creating these discrete values. 
\\

\subsection{Sampling Rates and Quality of Digital Audio}
\label{sec_sampling_rates}
In 1963, Mathews wrote on the potential and utility of computers as digital instruments; By presenting a snapshot of digital audio technology of his time and making predictions on what would be possible in the future~\cite{mathews1963digital}. This work by Mathews makes the robust foundations of digital signal processing apparent as many of the techniques described have remained popular and relatively unchanged, yet subjected to up-scaling alongside Moore's law~\cite{mack2011fifty,smith1991viewpoints}. For instance, Mathews described a general method for computers to capture and internally represent audio: By discretely sampling continuous pressure waves of sound and recreating the sound from numbers.

As briefly discussed in Section~\ref{sec:computer_make_sound}, sound can take on the physical characteristics of a waveform. Imagine the curve shown in figure~\ref{fig_sampling_rate} is representative of a sound wave we would like to digitally capture. As the sound travels through a microphone, sensors can capture small packets of information about it. Each packet would represent the amplitude of the wave at a time-step. The more packets of information we get, the better our digital recreation of the original sound.

In this context, \textit{sampling rate}, is an important feature of digital sound, referring to the number of samples per second of audio (measured in Hertz, or Hz). Sampling rate is not the only important factor when recording audio as it is important to record the samples with not just speed, but also precision. Assuming perfect sensors, precision is the range of possible values we can assign to each sample. It is determined by bit depth: the number of bits we have to represent the values of each sample.  Today, standard quality audio often refers to sampling rates of 44.1 kHz and 48 kHz and bit depth of 16 (that's $2^{16}$ values), while \enquote{high quality} audio indicates an increase in bit rate or bit depth~\cite{reiss2016meta}. Although subject to diminishing returns, high quality audio may be preferable to most musicians and audio-engineers; In a meta-analysis of digital sound perception, Reiss found a small but statistically significant portion of people are able to discriminate the effect of standard and high quality audio with no prior training, and a dramatically higher detection rate after extensive training~\cite{reiss2016meta}.

\begin{figure}[h]

\centering
\includegraphics[width=1\linewidth,angle =-90 ]{images/periodic_function_decimation.png}
\caption{Reconstruction of a periodic, continuous wave at three different sampling levels. Higher sampling rates result in higher reconstruction accuracy. } % AH: this is linear interpolation many sound cards will convert the last signal back into the original wave just fine
\label{fig_sampling_rate}
\end{figure}

\subsection{Loudness, Amplitudes and Envelopes}
Loudness is a subjective description of a sound's intensity or energy levels. It varies based on the complexity of sounds, the frequencies present, and hearing ability of the listener~\cite{fletcher1933loudness,cook1999chap6}. It can only be measured relatively, by establishing a benchmark sound and surveying populations on the relative intensities~\cite{cook1999chap6}. Since loudness and intensity of sound correlate with the amplitude of digital waveforms (the values assigned to the samples), an imperfect but convenient alternative method for inferring the the loudness of digital sounds is to compare relative amplitudes.

The peak level of a digital sound corresponds to the sample with the highest value. This method has its benefits, but leaves out an important factor: the duration of intensity. A more commonly used method of level detection is the Root Mean Square (RMS) method, which averages the values of a short sequence of samples for its calculation of levels.

Sounds typically vary in intensity as they unfold. This change in intensity is often described by the \enquote{envelope} of the sound, particularly in shorter samples. For digital sounds, Mitchell describes the envelope as either (since samples typically take the range of -1 to 1) of the borders that are created by graphing a signal and connecting the local absolute peak values~\cite{mitchell2009basicsynthChap6}. The envelope is generally described via 4 features: Attack, Decay, Sustain and Release (ADSR). Attack describes how quickly the peak loudness is reached. Decay for how quickly the sound drops to sustain level. Sustain is the duration of sustaining intensity (e.g how long a finger is kept on a piano key). Release describes the speed of fading to silence (e.g once a piano key is released).

Envelopes can be mathematically described and used to shape signals. A common approach in digital sound synthesis is to output all samples at a consistent amplitude and apply an envelope later down the synthesis chain. Digital and analog synthesizers often have built-in ADSR modules to shape the volume of the output and other parameters.

[Graph of envelope shaping a signal]
% note: make sure you're using terms signal and waveform properly
\subsection{Frequency, Pitch and Spectrograms}
\textit{Frequency} is used to describe number of repetitions within a time-frame, or how frequently a cycle is repeated. The frequency of an audio signal is often measured in unit of hertz (cycles per second). Most sounds, particularly those from none virtual sources, are a combination of multiple different pressure waves with different frequencies and amplitudes. \textit{Pitch}, is a perceptual property of sound that is tied to the frequencies present in each sound. How we perceive and describe the pitch of a sound (e.g high-pitched vs low-pitched) is heavily dependent on the characteristics (frequency, amplitude, duration, etc) of the waveforms it contains. Some sounds such as piano chords or pure tones have easily discernable pitches. Others, such as \enquote{pink noise} or the sound of rain do not. Yet another factor to consider is the hearing ability of the subject, which varies between people based on factors such as age, environment, musical training, etc~\cite{reiss2016meta,alain2007age,newman2012grm7}.

Spectrograms are graphs used to showcase and analyze the duration and amplitude of frequencies present in a sound. Since we often do not have access to the time-variant systems behind sounds of interest, it is common to use function decomposition methods to break sounds down to a combination of simpler functions. A commonly used method for the breakdown of complex, time-variant functions is the fourier transformation and its variations. One such method is the discrete fourier transformation (DFT) and its inverse, often used to convert digital sound from its time domain representation (sequence of samples) to its frequency domain representation (sets of frequency ranges and their amplitude) and vice versa.\\\\

[spectrogram figures]
[figure of this breakdown]

% https://en.wikipedia.org/wiki/Frequency_domain#/media/File:Fourier_transform_time_and_frequency_domains_(small).gif

\section{Digital Audio Synthesis}
\label{sec_digital_synthesis}
The phenomena of sound at intensities we commonly encounter can be described as a product of a \textit{linear system} of functions~\cite{cook1999chap4}. A linear system is a system where the transformation of overlapping inputs is equal to the sum of the separately transformed inputs~\cite{lyons2004understandingChap1,cook1999chap4}. In a linear system $\mathcal{S}$ with valid inputs and outputs $x(i)$ and $y(i)$, if:

\begin{equation}
 \mathcal{S}(x(i_1)) \xrightarrow{generates} y(i_1)
\end{equation}
\begin{center}
    and
\end{center}
\begin{equation}
\mathcal{S}(x(i_2)) \xrightarrow{generates}y(i_2)
\end{equation}

The output of the system given both inputs is the sum of the individual outputs, or:
\begin{equation}
 \mathcal{S}(x(i_1)+x(i_2)) \xrightarrow{generates} y(i_1)+y(i_2) 
\end{equation}
\\
This concept has important implications digital audio creation and analysis. Simple tones can be combined to create complex sounds, and complex sounds can be broken down for easier analysis~\cite{lyons2004understandingChap1}. It also allows systems based on experiments with simple sine waves to remain relevant in complex sound domains~\cite{cook1999chap4}.  \\\\

[graph of addition of two sine waves making a complex sine wave ]
\\

Various sound synthesis techniques have been developed via treatment of sound as a sequence of values. Linear systems are commonly used in creation of musical tones, while non-linear systems are used for introduction of distortion and noise where needed. In their taxonomy of digital synthesis techniques, Smith defines four families of algorithms. Algorithms that process and modulate existing sounds (e.g granular synthesis, wavelets), Spectral models that aim to create a particular spectrum of sound (e.g additive, subtractive), physical models which emulate the physics of real instruments (discussed briefly in Section ~\ref{sec_tools_disposal}) and abstract models (e.g wave shaping, Karplus-Strong) often used for adding harmonics or distortion to simple sound signals~\cite{smith1991viewpoints}.

Synthesizers are engines of synthesis that make use of one or more of these techniques for sound generation. Selection of the appropriate synthesis methods depends not only on the expectations from a single end product, but also the features of the synthesizer itself. Whether in goal oriented tasks such as text-to-speech or in creative endeavors such as ambient-noise generation, it is often desirable to work with systems that are quick, adaptable and tractable. For example, one might desire a text-to-speech system where slight changes to input parameters can introduces slight changes to the speech patterns, utterances, voices etc. This ability to quickly modify and audition sounds becomes a necessity when the synthesizer is being used as a creative instrument of itself, rather than an emulator for existing instruments and sounds.

In our work, we require our synthesizer to be simple and efficient, as we would like to deploy as many instances as possible (e.g when searching for particular sounds). We also value replicability as we would like to save and re-use synthesizer programs which we found interesting. Another requirement is tractability as we would like modify parameters of a program with various levels of intensity and contrast the audition results.

Having considered our requirements, we opted to mainly utilize \enquote{additive} and \enquote{subtractive} synthesis, umbrella terms for some of the most simple and common methods of synthesis~\cite{mitchell2009basicsynthChap1}. 
In additive synthesis, sounds are built as a sum of signals; Where signals are outputs of periodic oscillators.  In subtractive synthesis, segments of a complex signal are removed until a desired sound is reached, often by a chain of one or more \textit{digital filters}. It is not uncommon for percussive sounds to have noisy, chaotic high frequency content during their short attack envelope followed by harmonic low/medium frequency content~\cite{lakatos2000common}. We hypothesize that additive synthesis will be an appropriate when precisely tuned oscillators are needed, and subtractive synthesis can be utilized for sculpting white noise to recreate chaotic, noisy segments of the spectrum.

\subsection{Filters, Oscillators ...}
[quick overview of filters and oscillators]
[will use spectrums to describe these]

\subsection{Analog Synthesizer}
Talk about analog synthesis briefly, so the word synthesizer feels less abstract...
\subsection{Virtual Synthesizers}
5 decades ago, Mathews claimed that any sound can be recreated via a computer by high frequency sampling of pressure waves. Additionally, he added that since \enquote{a very high sampling rate is required, and, if this process is to be useful musically, programs for generating samples from the parameters of notes must be written}~\cite{mathews1963digital}. The methods of synthesis we discussed in Section~\ref{sec_digital_synthesis} are a major component of such programs. With the exception of physical synthesis, modern chips are more than capable of simultaneously running many instances of these algorithms. To further assist with their musical utility, the majority of digital synthesis systems work in tandem with programs such as Musical Instrument Digital Interface (MIDI), which can  modulating the parameters of these synthesis methods by modulating information pretaining to ADSR and other note characteristics, often in real time~\cite{moog1986midi}.

 The rise of Digital Audio Workstations (DAW) ~\cite{leider2004digital} and Virtual Studio Technology (VST) based plug-ins~\cite{tanev2013virtual} have rapidly transformed the sonic and material landscape of music production in the recent years. Coupled with this rise in popularity is a vast array of commercial products and services dedicated to satiating the need of amateur and professional music producers for unique sounds; most commonly via audio samples: one-shot drum samples, long sustained notes (commonly referred to as pads or textures), and loops (percussive or melodic) are common deliverables. Two notable examples of these commercial services are \textit{loopmasters}\footnote{loopmasters.com} and \textit{splice.com}\footnote{splice.com}. Furthermore, VST plug-ins can emulate complex audio synthesizers and effects which some producers may find daunting or time consuming to work with from scratch. In many cases VST plug-in vendors or unaffiliated enthusiasts sell additional presets for these plugins, targeted towards producers who do not have the time or interest in creating their own. The flexibility of the VST technology allows producers to further modify these presets until their desired sound is reached.

\section{Neural Networks And Sound}
\label{bg:NN}
\subsection{Neural Networks For Sound Analysis}
\subsection{Neural Networks as Synthesizers}
We defined digital synthesis as the \enquote{process of generating discrete values which approximate sound waves}. We also established that manual generation of these values at high sampling rates is near impossible; A problem which has motivated a wide variety of synthesis techniques which aim to create signals within a linear (or mostly linear) system, in the simplest form possible (**look into simplest form proofs**). Recently, the exponential increase in computing power has motivated a wide range of research in probabilistic sound generation, mainly via generative neural networks. 
% deterministically, if the input parameters to the system do not change, the output of the system will remain the same \footnote{talk about noise generation methods and seeding}.

Artificial Neural networks(ANNs) map inputs to outputs via a large network of parameters. Given the right network shape and parameter weights, they can approximate a large set of functions~\cite{cybenko1989approximation,cardaliaguet1992approximation}. ANNs are often deployed when we do not have access to the system of functions which guide a process, but a mapped set of inputs and outputs of the process can be attained. Given this set, the parameters of a neural network can be tuned for approximating the effect of the system on new inputs. The shape of the neural network (e.g number of layers, connections, activation functions) is often selected via trial and error ~\cite{bergstra2012random,bergstra2011algorithms,ba2013adaptive}. By definition, these approximations will never be more accurate than the system that is being approximated.

Since their emergence in the 1950's, research on ANNs has gone through several eras of stunted growth~\cite{basheer2000artificial,anderson1988neurocomputing}. With the lack of computing power identified as a major contributor (**citations needed**). In the last decade, the increase in the affordability of high performance graphic cards has been coupled with a major resurgence of interest into ANNs. As a result, a number of domain specific variations of the traditional ANN architectures have also emerged.

Generative neural networks (GNNs) are utilized for the completion of a sequences of values; Often by taking an incomplete sequence as input and outputting the most likely value for the next step. Published in 2016 by Oord et al. WaveNet is considered a seminal breakthrough in the usage ANNs for sound synthesis~\cite{oord2016wavenet}. Surpassing state of the art concatenate and parametric speech synthesis techniques, which work by combining one or more previously recorded audio snippets~\cite{schwarz2007corpus}. When trained on a large corpus of audio samples, GNNs such WaveNet can learn the \enquote{predictive distribution for each
audio sample conditioned on all previous ones}~\cite{oord2016wavenet}. Once this distribution is learned, it can be used to create sounds 1 sample at a time, a slow process, as Mathews predicted. \\
% Parallel WaveGAN has only 1.44 M parameters and can generate 24 kHz speech waveform 28.68 times faster than real-time on a single GPU environment. Perceptual listening test results verify that our proposed method achieves 4.16 mean opinion score within a Transformer-based text-to-speech framework, which is comparative to the best distillation-based Parallel WaveNet system.
Oord et al. later proposed a parallel implementation of the WaveNet architecutre, accelerating generation by (**extract benchmarks**)~\cite{oord2017parallel}. Highly optimized GNNs such as WaveGan by Yamamoto et al.~\cite{yamamoto2020parallel} have matched WaveNet's perception performance while significantly reducing the number of parameters and speeding up synthesis (**some benchmarks in comments have to organize them**). Despite its state of the art performance, domain specific optimizations and and relatively small foot-print, WaveGAN requires the tuning of 1.44 million parameters and \enquote{generates 24 kHz speech waveform 28.68 times faster than real-time on a single GPU environment}~\cite{yamamoto2020parallel}. It should be noted that 24 kHz is half the standard quality for audio, and far lower than what is perceived as \enquote{high quality}, as previously discussed in Section~\ref{sec_sampling_rates}. We found 24 kHz and lower sampling rates to be common place in audio generation work utilizing neural networks~\cite{oord2017parallel,yamamoto2019parallel,aouameur2019neural,ramires2020neural}, likely for reducing training and generation time.

% Yet another caveat of such models is the large amount of data that is required for training as well as the hardware, energy and time to carry out the training step.

% We can create a tone via a deterministic system of equations.  Where every sample is the result of a sine function (**can i show that a sine function is the simplest possible function to create a tone?**) 
% Mathews said that we can create sound by coding in the samples one at a time ~\cite{mathews1963digital}, but this process is too slow to do by hand, which is why he advocated for digital synthesis.
% These include (i) ANNs’ success de-
% pends on both the quality and quantity of the data,
% (ii) a lack of clear rules or fixed guidelines for
% optimal ANN architecture design, (iii) a lack of
% physical concepts and relations, and (iv) the inability
% to explain in a comprehensible form the process
% through which a given decision (answer) was made
% by the ANN (i.e., ANNs criticized for being black
% boxes) ~\cite{basheer}.

% 
\section{Goal Oriented Novel Sound Generation}

\label{related}
\subsection{Tool Selection}
We define \enquote{goal oriented novel sound generation} as any work that seeks to implement a system that is capable of generating novel sounds with a desired characteristic. Based on our review of relevant works, we believe that \enquote{goal oriented audio generation} necessitates two essential components: A tool-set for the analysis of sound and a tool-set for creation of sound. As a result, we base our work around learning of the distinguishing features of various sound groups (i.e different types of drums) and using the learned features for generation of sound. In Section~\ref{sec_methodology} we introduced these components as the virtual ear and virtual synthesizer.

 Thus far we have discussed various techniques at our disposal for the implementation of a virtual ear and synthesizers, all with their contextual strengths and weaknesses. In the upcoming Sections, we will thoroughly discuss our implementations and the subsequent results. Here, we will review a variety of works which fall under our definition of \enquote{goal oriented novel sound generation}. Particularly, we are interested in a discussion of goals, chosen methods for the feature extraction, and chosen methods of sound synthesis. 
%  We will highlight the contradistinctions with our work where appropriate

\subsection{Related Work}
ANN or DSP approaches can be taken to the implementation of a virtual ear and a virtual synthesizer. The development of ANN frameworks has led to works which have utilized ANNs for both components. Also common are works have leveraged a mixture of both approaches, commonly by utilization of ANNs for the virtual ear and DSP methods for synthesis.

\begin{center}
\begin{table}[h*]
 \resizebox{\linewidth}{!}{\begin{tabular}{||c c c c||} 
work & feature extraction & synthesis & specilization & \hline
Oord et al & CNN & CNN &Speech& \hline
Yamamoto et al & GAN & GAN&Speech & \hline
Aouameur et al & Latent layer& Decoding of Latent Layers & Percussion & \hline
Ramires et al & Latent layer & Decoding of Latent Layers & Percussion & \hline
Yee-King et al & LSTM on Paremters & DSP & Synth Pads & \hline
\end{tabular}}
\caption{for reference, will delete} % AH: Fix the table up and keep it.
\end{table}
\end{center}
Numerous deep, neural network models have been proposed and utilized for the purpose of signal generation in recent years. WaveGans and WaveNet have been subject to significant improvements and experiments since their proposal~\cite{nsynth2017,yamamoto2020parallel,oord2017parallel}. Most relevant to us are recent works by Aoumaeur et al. in which variational AutoEncoders (VAE's) have been utilized for generation of percussive samples~\cite{aouameur2019neural}; As well as Ramires et al's work in generation of percussive sounds by guiding the output of a feedforward neural network via simple and explainable desired features. 
Automatic programming of virtual synthesizers has also been a topic of interest. In early 2000s, Interactive Genetic Algorithms (IGA's) were utilized for the generation of new sounds with various sound-engines~\cite{johnson1999exploring,dahlstedt2001creating}. More recent work by Yee-King et al.~\cite{yee2018automatic} used Long short-Term Memory (LSTM) models and genetic algorithms to find the exact parameters used to create a group of sounds. The sounds approximated were made by the same virtual synthesizer, not an external source; making the eventual replication certain even with random search. Since this work appears more focused on pads and textures rather than drums, feature matching appears to not be concerned with the envelope of the sounds but rather the frequency content within arbitrary time windows. Yet another recent work by Esling et al. used a large dataset of over 10,000 presets for a commercial VST synthesizer to learn a latent parameter space which can be sampled for creation of new audio~\cite{esling2019universal}. As stated before, our work explores the rapid approximation of percussion sounds with no previous knowledge about the sonic capabilities of our virtual synthesizer, exploring the actual parameter space rather than its latent representation.

\bibliographystyle{apacite}
% Place your own .bib file here:
\bibliography{CSMC_MUME_LaTeX_Template.bib}

\end{document}

### 2020-08-16 templates_aimusic2020/paper.tex
Updates from Overleaf

@@
 
-\begin{figure}[h]
-
-\centering
-\includegraphics[width=1\linewidth,angle =-90 ]{images/periodic_function_decimation.png}
-\caption{Reconstruction of a periodic, continuous wave at three different sampling levels.
-Higher sampling rates result in higher reconstruction accuracy.
-} % AH: this is linear interpolation many sound cards will convert the last signal back into the original wave just fine
-\label{fig_sampling_rate}
-\end{figure}
-
 \subsection{Loudness, Amplitudes and Envelopes}
@@
 
-% https://en.wikipedia.org/wiki/Frequency_domain#/media/File:Fourier_transform_time_and_frequency_domains_(small).gif
-
-\section{Digital Audio Synthesis}
-\label{sec_digital_synthesis}
-The phenomena of sound at intensities we commonly encounter can be described as a product of a \textit{linear system} of functions~\cite{cook1999chap4}.
-A linear system is a system where the transformation of overlapping inputs is equal to the sum of the separately transformed inputs~\cite{lyons2004understandingChap1,cook1999chap4}.
-In a linear system $\mathcal{S}$ with valid inputs and outputs $x(i)$ and $y(i)$, if:
-
-\begin{equation}
- \mathcal{S}(x(i_1)) \xrightarrow{generates} y(i_1)
-\end{equation}
-\begin{center}
-    and
-\end{center}
-\begin{equation}
-\mathcal{S}(x(i_2)) \xrightarrow{generates}y(i_2)
-\end{equation}
-
-The output of the system given both inputs is the sum of the individual outputs, or:
-\begin{equation}
- \mathcal{S}(x(i_1)+x(i_2)) \xrightarrow{generates} y(i_1)+y(i_2) 
-\end{equation}
-\\
-This concept has important implications digital audio creation and analysis.
-Simple tones can be combined to create complex sounds, and complex sounds can be broken down for easier analysis~\cite{lyons2004understandingChap1}.
-It also allows systems based on experiments with simple sine waves to remain relevant in complex sound domains~\cite{cook1999chap4}.
-\\\\
-
-[graph of addition of two sine waves making a complex sine wave ]
-\\
-
-Various sound synthesis techniques have been developed via treatment of sound as a sequence of values.
-Linear systems are commonly used in creation of musical tones, while non-linear systems are used for introduction of distortion and noise where needed.
-In their taxonomy of digital synthesis techniques, Smith defines four families of algorithms.
-Algorithms that process and modulate existing sounds (e.g granular synthesis, wavelets), Spectral models that aim to create a particular spectrum of sound (e.g additive, subtractive), physical models which emulate the physics of real instruments (discussed briefly in Section ~\ref{sec_tools_disposal}) and abstract models (e.g wave shaping, Karplus-Strong) often used for adding harmonics or distortion to simple sound signals~\cite{smith1991viewpoints}.
-
-Synthesizers are engines of synthesis that make use of one or more of these techniques for sound generation.
-Selection of the appropriate synthesis methods depends not only on the expectations from a single end product, but also the features of the synthesizer itself.
-Whether in goal oriented tasks such as text-to-speech or in creative endeavors such as ambient-noise generation, it is often desirable to work with systems that are quick, adaptable and tractable.
-For example, one might desire a text-to-speech system where slight changes to input parameters can introduces slight changes to the speech patterns, utterances, voices etc.
-This ability to quickly modify and audition sounds becomes a necessity when the synthesizer is being used as a creative instrument of itself, rather than an emulator for existing instruments and sounds.
-
-In our work, we require our synthesizer to be simple and efficient, as we would like to deploy as many instances as possible (e.g when searching for particular sounds).
-We also value replicability as we would like to save and re-use synthesizer programs which we found interesting.
-Another requirement is tractability as we would like modify parameters of a program with various levels of intensity and contrast the audition results.
-
-Having considered our requirements, we opted to mainly utilize \enquote{additive} and \enquote{subtractive} synthesis, umbrella terms for some of the most simple and common methods of synthesis~\cite{mitchell2009basicsynthChap1}.
-In additive synthesis, sounds are built as a sum of signals; Where signals are outputs of periodic oscillators.
-In subtractive synthesis, segments of a complex signal are removed until a desired sound is reached, often by a chain of one or more \textit{digital filters}.
-It is not uncommon for percussive sounds to have noisy, chaotic high frequency content during their short attack envelope followed by harmonic low/medium frequency content~\cite{lakatos2000common}.
-We hypothesize that additive synthesis will be an appropriate when precisely tuned oscillators are needed, and subtractive synthesis can be utilized for sculpting white noise to recreate chaotic, noisy segments of the spectrum.
-
-\subsection{Filters, Oscillators ...}
-[quick overview of filters and oscillators]
-[will use spectrums to describe these]
-
-\subsection{Analog Synthesizer}
-Talk about analog synthesis briefly, so the word synthesizer feels less abstract...
-\subsection{Virtual Synthesizers}
-5 decades ago, Mathews claimed that any sound can be recreated via a computer by high frequency sampling of pressure waves.
-Additionally, he added that since \enquote{a very high sampling rate is required, and, if this process is to be useful musically, programs for generating samples from the parameters of notes must be written}~\cite{mathews1963digital}.
-The methods of synthesis we discussed in Section~\ref{sec_digital_synthesis} are a major component of such programs.
-With the exception of physical synthesis, modern chips are more than capable of simultaneously running many instances of these algorithms.
-To further assist with their musical utility, the majority of digital synthesis systems work in tandem with programs such as Musical Instrument Digital Interface (MIDI), which can  modulating the parameters of these synthesis methods by modulating information pretaining to ADSR and other note characteristics, often in real time~\cite{moog1986midi}.
-
- The rise of Digital Audio Workstations (DAW) ~\cite{leider2004digital} and Virtual Studio Technology (VST) based plug-ins~\cite{tanev2013virtual} have rapidly transformed the sonic and material landscape of music production in the recent years.
-Coupled with this rise in popularity is a vast array of commercial products and services dedicated to satiating the need of amateur and professional music producers for unique sounds; most commonly via audio samples: one-shot drum samples, long sustained notes (commonly referred to as pads or textures), and loops (percussive or melodic) are common deliverables.
-Two notable examples of these commercial services are \textit{loopmasters}\footnote{loopmasters.com} and \textit{splice.com}\footnote{splice.com}.
-Furthermore, VST plug-ins can emulate complex audio synthesizers and effects which some producers may find daunting or time consuming to work with from scratch.
-In many cases VST plug-in vendors or unaffiliated enthusiasts sell additional presets for these plugins, targeted towards producers who do not have the time or interest in creating their own.
-The flexibility of the VST technology allows producers to further modify these presets until their desired sound is reached.
-
-\section{Neural Networks And Sound}
-\label{bg:NN}
-\subsection{Neural Networks For Sound Analysis}
-\subsection{Neural Networks as Synthesizers}
-We defined digital synthesis as the \enquote{process of generating discrete values which approximate sound waves}.
-We also established that manual generation of these values at high sampling rates is near impossible; A problem which has motivated a wide variety of synthesis techniques which aim to create signals within a linear (or mostly linear) system, in the simplest form possible (**look into simplest form proofs**).
-Recently, the exponential increase in computing power has motivated a wide range of research in probabilistic sound generation, mainly via generative neural networks.
-% deterministically, if the input parameters to the system do not change, the output of the system will remain the same \footnote{talk about noise generation methods and seeding}.
-
-Artificial Neural networks(ANNs) map inputs to outputs via a large network of parameters.
-Given the right network shape and parameter weights, they can approximate a large set of functions~\cite{cybenko1989approximation,cardaliaguet1992approximation}.
-ANNs are often deployed when we do not have access to the system of functions which guide a process, but a mapped set of inputs and outputs of the process can be attained.
-Given this set, the parameters of a neural network can be tuned for approximating the effect of the system on new inputs.
-The shape of the neural network (e.g number of layers, connections, activation functions) is often selected via trial and error ~\cite{bergstra2012random,bergstra2011algorithms,ba2013adaptive}.
-By definition, these approximations will never be more accurate than the system that is being approximated.
-
-Since their emergence in the 1950's, research on ANNs has gone through several eras of stunted growth~\cite{basheer2000artificial,anderson1988neurocomputing}.
-With the lack of computing power identified as a major contributor (**citations needed**).
-In the last decade, the increase in the affordability of high performance graphic cards has been coupled with a major resurgence of interest into ANNs.
-As a result, a number of domain specific variations of the traditional ANN architectures have also emerged.
-
-Generative neural networks (GNNs) are utilized for the completion of a sequences of values; Often by taking an incomplete sequence as input and outputting the most likely value for the next step.
-Published in 2016 by Oord et al.
-WaveNet is considered a seminal breakthrough in the usage ANNs for sound synthesis~\cite{oord2016wavenet}.
-Surpassing state of the art concatenate and parametric speech synthesis techniques, which work by combining one or more previously recorded audio snippets~\cite{schwarz2007corpus}.
-When trained on a large corpus of audio samples, GNNs such WaveNet can learn the \enquote{predictive distribution for each
-audio sample conditioned on all previous ones}~\cite{oord2016wavenet}. Once this distribution is learned, it can be used to create sounds 1 sample at a time, a slow process, as Mathews predicted. \\
-% Parallel WaveGAN has only 1.44 M parameters and can generate 24 kHz speech waveform 28.68 times faster than real-time on a single GPU environment.
-Perceptual listening test results verify that our proposed method achieves 4.16 mean opinion score within a Transformer-based text-to-speech framework, which is comparative to the best distillation-based Parallel WaveNet system.
-Oord et al.
-later proposed a parallel implementation of the WaveNet architecutre, accelerating generation by (**extract benchmarks**)~\cite{oord2017parallel}.
-Highly optimized GNNs such as WaveGan by Yamamoto et al.~\cite{yamamoto2020parallel} have matched WaveNet's perception performance while significantly reducing the number of parameters and speeding up synthesis (**some benchmarks in comments have to organize them**).
-Despite its state of the art performance, domain specific optimizations and and relatively small foot-print, WaveGAN requires the tuning of 1.44 million parameters and \enquote{generates 24 kHz speech waveform 28.68 times faster than real-time on a single GPU environment}~\cite{yamamoto2020parallel}.
-It should be noted that 24 kHz is half the standard quality for audio, and far lower than what is perceived as \enquote{high quality}, as previously discussed in Section~\ref{sec_sampling_rates}.
-We found 24 kHz and lower sampling rates to be common place in audio generation work utilizing neural networks~\cite{oord2017parallel,yamamoto2019parallel,aouameur2019neural,ramires2020neural}, likely for reducing training and generation time.
-
-% Yet another caveat of such models is the large amount of data that is required for training as well as the hardware, energy and time to carry out the training step.
-
-% We can create a tone via a deterministic system of equations.
-Where every sample is the result of a sine function (**can i show that a sine function is the simplest possible function to create a tone?**)
-% Mathews said that we can create sound by coding in the samples one at a time ~\cite{mathews1963digital}, but this process is too slow to do by hand, which is why he advocated for digital synthesis.
-% These include (i) ANNs’ success de-
-% pends on both the quality and quantity of the data,
-% (ii) a lack of clear rules or fixed guidelines for
-% optimal ANN architecture design, (iii) a lack of
-% physical concepts and relations, and (iv) the inability
-% to explain in a comprehensible form the process
-% through which a given decision (answer) was made
-% by the ANN (i.e., ANNs criticized for being black
-% boxes) ~\cite{basheer}.
-
-% 
 \section{Goal Oriented Novel Sound Generation}

### 2020-08-17 templates_aimusic2020/paper.tex
Updates from Overleaf

@@
 
-In this context, \textit{sampling rate}, is an important feature of digital sound, referring to the number of samples per second of audio (measured in Hertz, or Hz).
-Sampling rate is not the only important factor when recording audio as it is important to record the samples with not just speed, but also precision.
-Assuming perfect sensors, precision is the range of possible values we can assign to each sample.
-It is determined by bit depth: the number of bits we have to represent the values of each sample.
-Today, standard quality audio often refers to sampling rates of 44.1 kHz and 48 kHz and bit depth of 16 (that's $2^{16}$ values), while \enquote{high quality} audio indicates an increase in bit rate or bit depth~\cite{reiss2016meta}.
-Although subject to diminishing returns, high quality audio may be preferable to most musicians and audio-engineers; In a meta-analysis of digital sound perception, Reiss found a small but statistically significant portion of people are able to discriminate the effect of standard and high quality audio with no prior training, and a dramatically higher detection rate after extensive training~\cite{reiss2016meta}.
-
-\subsection{Loudness, Amplitudes and Envelopes}
-Loudness is a subjective description of a sound's intensity or energy levels.
-It varies based on the complexity of sounds, the frequencies present, and hearing ability of the listener~\cite{fletcher1933loudness,cook1999chap6}.
-It can only be measured relatively, by establishing a benchmark sound and surveying populations on the relative intensities~\cite{cook1999chap6}.
-Since loudness and intensity of sound correlate with the amplitude of digital waveforms (the values assigned to the samples), an imperfect but convenient alternative method for inferring the the loudness of digital sounds is to compare relative amplitudes.
-
-The peak level of a digital sound corresponds to the sample with the highest value.
-This method has its benefits, but leaves out an important factor: the duration of intensity.
-A more commonly used method of level detection is the Root Mean Square (RMS) method, which averages the values of a short sequence of samples for its calculation of levels.
-
-Sounds typically vary in intensity as they unfold.
-This change in intensity is often described by the \enquote{envelope} of the sound, particularly in shorter samples.
-For digital sounds, Mitchell describes the envelope as either (since samples typically take the range of -1 to 1) of the borders that are created by graphing a signal and connecting the local absolute peak values~\cite{mitchell2009basicsynthChap6}.
-The envelope is generally described via 4 features: Attack, Decay, Sustain and Release (ADSR).
-Attack describes how quickly the peak loudness is reached.
-Decay for how quickly the sound drops to sustain level.
-Sustain is the duration of sustaining intensity (e.g how long a finger is kept on a piano key).
-Release describes the speed of fading to silence (e.g once a piano key is released).
-
-Envelopes can be mathematically described and used to shape signals.
-A common approach in digital sound synthesis is to output all samples at a consistent amplitude and apply an envelope later down the synthesis chain.
-Digital and analog synthesizers often have built-in ADSR modules to shape the volume of the output and other parameters.
-
-[Graph of envelope shaping a signal]
-% note: make sure you're using terms signal and waveform properly
 \subsection{Frequency, Pitch and Spectrograms}
@@
 Yet another factor to consider is the hearing ability of the subject, which varies between people based on factors such as age, environment, musical training, etc~\cite{reiss2016meta,alain2007age,newman2012grm7}.
-
-Spectrograms are graphs used to showcase and analyze the duration and amplitude of frequencies present in a sound.
-Since we often do not have access to the time-variant systems behind sounds of interest, it is common to use function decomposition methods to break sounds down to a combination of simpler functions.
-A commonly used method for the breakdown of complex, time-variant functions is the fourier transformation and its variations.
-One such method is the discrete fourier transformation (DFT) and its inverse, often used to convert digital sound from its time domain representation (sequence of samples) to its frequency domain representation (sets of frequency ranges and their amplitude) and vice versa.\\\\
-
-[spectrogram figures]
-[figure of this breakdown]
 

### 2020-08-17 templates_aimusic2020/paper.tex
Updates from Overleaf

@@
 
-\mainmatter  % start of an individual contribution
+\mainmatter
 
-% first the title is needed
 \title{Percussive Sound Generation with Virtual Listeners and Modular Synthesizers}
@@
 % the name(s) of the author(s) follow(s) next
-%
-% NB: Chinese authors should write their first names(s) in front of
-% their surnames. This ensures that the names appear correctly in
-% the running heads and the author index.
-%
 \author{Amir Salimi \and Abram Hindle}
-%
-% if the names of the authors are too long for the running head, please use the format: AuthorA et al.
+
 \authorrunning{Amir Salimi and Abram Hindle }
@@
 
-%
-% NB: a more complex sample for affiliations and the mapping to the
-% corresponding authors can be found in the file "llncs.dem"
-% (search for the string "\mainmatter" where a contribution starts).
-% "llncs.dem" accompanies the document class "llncs.cls".
-%
-
+% intro, 1 page
+% background and methodology 2 pages
+% implementation 
+% results 2.5
 \maketitle
@@
 
-\subsection{What Solution Do We Propose?}
-To virtually create novel drum sounds, we need a generative source; One that produces audio based on some instructions.
-We also need a method of evaluation to help us determine which sounds resemble drums and are worth keeping.
-We also would like to know what instructions caused our audio source to make the sounds we liked.
-In short, our approach requires effective \textit{generation} and \textit{evaluation} of sounds.
-\subsection{How Can a Computer Make Sounds?}
-Sounds are transmitted via waveforms.
-Your computer can emulate the physical characteristics of basic waveforms by evaluating the output of periodic functions such as sines and cosines.
-Evaluation of basic periodic functions is the simplest form of software audio generation~\cite{mitchell2009basicsynthChap5}.
-This generative system is called an \textit{oscillator} and its output is a waveform which can be sent to your computer's digital-to-analog conversion system to create an audible signal.
-The combination and modification of these pure tones are the building blocks of digital signal processing (DSP).
+ \begin{figure}[t!]
+    \begin{center}
+    \textbf{Pipeline Design}
+    \makebox[\textwidth]{
+    \fbox{\includegraphics[width=1.1\linewidth]{images/pipeline.pdf}}}
+    \end{center}
+    \caption{A blueprint of our desired pipeline which allows each component to be implemented in a number of ways. Our implementations of this pipeline allow for easy parallelization when needed. 
+    }
+\label{fig:pipeline_outline}
+\end{figure}
 
-\begin{figure*}[h]
+\subsection{Our Approach}
+To virtually create novel drum sounds, we need a tractable, generative source of audio; One that deterministically produces audio based on a set of instructions.
+Additionally, we need a method of evaluation to help us determine which sounds resemble drums and are worth keeping.
+To enable heuristic search, we would like to know what instructions caused our audio source to make the sounds we liked.
+Given these two components capable of \textit{generation} and \textit{evaluation} of sounds, we build a generative pipeline of audio as depicted in figure~\ref{fig:pipeline_outline}.
+The success of this pipeline is dependent on the characteristics of the components responsible for the generation and evaluation of the sounds.
+We call these two components the \emph{virtual synthesizer} and \emph{virtual ear} respectively.
+
+\subsection{Virtual Synthesizer Design}
+Sound is product of physical disturbances, causing vibrations in our mediums.
+Vibrations are perpetuated through air as part of an expanding, spherical front ~\cite{cook1999chap4}.
+A sound wave can be viewed as the result of a function which governs amplitude through time, where time and amplitude exist in continuous dimensions.
+Waves can be approximated via a series of samples, associating time steps to a discrete range of amplitude values.~\textit{Digital synthesis} of audio is the process of creating these discrete values.
+
+\begin{figure*}[htbp]
 \label{fig_example_sine}
@@
 
- Most organic sounds---sounds from the natural environment, and its flora and fauna---are much more complex than the output of a single oscillator.
-However, with careful programming, DSP techniques can be used to replicate almost any sound, which is why they have powered commercial digital synthesizers for over half a century \cite{jenkins2019analog}.
+Evaluation of a periodic function such as sine or cosine is the simplest form of software audio generation~\cite{mitchell2009basicsynthChap5}.
+This generative system is called an \textit{oscillator}.
+The combination and modification of oscillators are the building blocks of digital signal processing (DSP).
+Most sounds from the natural environment, and its flora and fauna are more complex than the output of a single oscillator.
+However, with careful programming, DSP techniques can be used to replicate almost any sound, which is why they have powered commercial digital synthesizers for over half a century ~\cite{jenkins2019analog}.
 Another advantage to using DSP for sound generation is that the synthesizers we build using these functions are tractable: the output is determined by the input and reproducible.
@@
 
-\section{What Is Our Methodology?}
-\label{sec_methodology}
+\subsection{Neural Networks and Sound}
+
+\begin{center}
+\begin{table}[h*]
+\hline
+ \resizebox{\linewidth}{!}{\begin{tabular}{||c c c c||} 
+work & feature extraction & synthesis & specilization & \hline
+Oord et al & CNN & CNN &Speech& \hline
+Yamamoto et al & GAN & GAN&Speech & \hline
+Aouameur et al & Latent layer& Decoding of Latent Layers & Percussion & \hline
+Ramires et al & Latent layer & FeedForward Network & Percussion & \hline
+Yee-King et al & LSTM on Paremters & DSP & Synth Pads & \hline
+\end{tabular}}
+\caption{Quick reference for related works}
+\end{table}
+\end{center}
+
+\section{Implementation}
 We conceptualized a general pipeline for approximation of sounds: A synthesizer creates random noise while a virtual ear rapidly evaluates the outputs and outputs a score which is used for the separation of undesired outputs from desired ones.
 This approach assumes that a fraction of the randomly generated sounds can be substituted for percussion and that the synthetic ear will assign higher evaluation scores to this subset.
-Our implementation allows for the improvement of heuristic search algorithms such that the parameters of the synthesizer can be selected based on the previously observed evaluations.
-Following this idea, we found the proper implementation of 2 major components to be crucial:
-
 \begin{itemize}
@@
 \end{itemize}
-
-Our components are designed with modularity and parallelizability in mind.
-This allows each component to be debugged, modified, and improved without requiring modifications in other components while additionally increasing the scalability and speed of experiments.
-Section~\ref{implementation} contains further discussion of the components as well as the code that glues the project together.
-
-While the main focus of this project is the generation of novel percussive sounds, our methodology indicates promising results with regards to creation of new presets for any virtual synth without the need for a-priori knowledge of the functions or its parameters (i.e the effect of parameter modulation on the sonic output).
-We also demonstrate the viability of a virtual synthesizers based on Digital Signal Processing (DSP) methods for fast, unsupervised creation of novel audio.
-
-% Instead of learning weights and parameters in an audio-generation neural network, we wish to generate, search, and tune synthesizers to produce percussion sounds.
-Discussed in more detail in section \ref{related}.
-
-\section{Restating the Goal}
 We wish to leverage AI technologies, heuristic search, and DSP methods for the synthesis of novel audio.
@@
 Design decisions were made such that this approach can be modified for creation of other, non-percussive sound-types.
-
-\chapter{Background and Related Work}
-\label{section:background}
-This chapter aims to provide a background for the subsequent chapters via a quick overview of four important topics:\\ 
-\begin{enumerate}[label=(\roman*)]
-\item Digital sound, its features and concepts that have been fundamental to our work.
-\item A quick overview of common digital synthesis techniques.
-\item Discussion on the applications of artificial neural networks (ANNs) for feature extraction and sound production.
-Although similar results can be yielded from either approach, we distinguish ANN based techniques from tradition digital signal processing (DSP).
-\item Related works and their relative similarities and distinctions.
-\end{enumerate}
-\section{Digital Audio: Sound from Numbers}
-Sound is the result of a series of physical events.
-Most of what we hear is the product of physical disturbances, causing vibrations in our mutually shared, immersive mediums (air, hopefully).
-Sound waves carry these vibrations through air as part of an expanding, spherical wave front; Exponentially losing intensity as they travel away from the source~\cite{cook1999chap4}.
-\\\\
-
-[graph describing wave amplitude, phase and frequency here]
-\\\\
-A sound wave can be viewed as the result of a function which governs amplitude through time, where time and amplitude exist in continuous dimensions.
-Waves can be approximated via a series of samples, associating time steps to a discrete range of amplitude values.
-Given a wave generation method, computers can make sound by sending a series of discrete values to a digital-to-analogue chip, which in turn can
-create vibrations within a speaker.  \textit{Digital synthesis} of audio is the process of creating these discrete values. 
-\\
-
-\subsection{Sampling Rates and Quality of Digital Audio}
-\label{sec_sampling_rates}
-In 1963, Mathews wrote on the potential and utility of computers as digital instruments; By presenting a snapshot of digital audio technology of his time and making predictions on what would be possible in the future~\cite{mathews1963digital}.
-This work by Mathews makes the robust foundations of digital signal processing apparent as many of the techniques described have remained popular and relatively unchanged, yet subjected to up-scaling alongside Moore's law~\cite{mack2011fifty,smith1991viewpoints}.
-For instance, Mathews described a general method for computers to capture and internally represent audio: By discretely sampling continuous pressure waves of sound and recreating the sound from numbers.
-
-As briefly discussed in Section~\ref{sec:computer_make_sound}, sound can take on the physical characteristics of a waveform.
-Imagine the curve shown in figure~\ref{fig_sampling_rate} is representative of a sound wave we would like to digitally capture.
-As the sound travels through a microphone, sensors can capture small packets of information about it.
-Each packet would represent the amplitude of the wave at a time-step.
-The more packets of information we get, the better our digital recreation of the original sound.
-
-\subsection{Frequency, Pitch and Spectrograms}
-\textit{Frequency} is used to describe number of repetitions within a time-frame, or how frequently a cycle is repeated.
-The frequency of an audio signal is often measured in unit of hertz (cycles per second).
-Most sounds, particularly those from none virtual sources, are a combination of multiple different pressure waves with different frequencies and amplitudes.
-\textit{Pitch}, is a perceptual property of sound that is tied to the frequencies present in each sound.
-How we perceive and describe the pitch of a sound (e.g high-pitched vs low-pitched) is heavily dependent on the characteristics (frequency, amplitude, duration, etc) of the waveforms it contains.
-Some sounds such as piano chords or pure tones have easily discernable pitches.
-Others, such as \enquote{pink noise} or the sound of rain do not.
-Yet another factor to consider is the hearing ability of the subject, which varies between people based on factors such as age, environment, musical training, etc~\cite{reiss2016meta,alain2007age,newman2012grm7}.
-
-\section{Goal Oriented Novel Sound Generation}
-
-\label{related}
-\subsection{Tool Selection}
-We define \enquote{goal oriented novel sound generation} as any work that seeks to implement a system that is capable of generating novel sounds with a desired characteristic.
-Based on our review of relevant works, we believe that \enquote{goal oriented audio generation} necessitates two essential components: A tool-set for the analysis of sound and a tool-set for creation of sound.
-As a result, we base our work around learning of the distinguishing features of various sound groups (i.e different types of drums) and using the learned features for generation of sound.
-In Section~\ref{sec_methodology} we introduced these components as the virtual ear and virtual synthesizer.
-
- Thus far we have discussed various techniques at our disposal for the implementation of a virtual ear and synthesizers, all with their contextual strengths and weaknesses.
-In the upcoming Sections, we will thoroughly discuss our implementations and the subsequent results.
-Here, we will review a variety of works which fall under our definition of \enquote{goal oriented novel sound generation}.
-Particularly, we are interested in a discussion of goals, chosen methods for the feature extraction, and chosen methods of sound synthesis.
-%  We will highlight the contradistinctions with our work where appropriate
-
-\subsection{Related Work}
-ANN or DSP approaches can be taken to the implementation of a virtual ear and a virtual synthesizer.
-The development of ANN frameworks has led to works which have utilized ANNs for both components.
-Also common are works have leveraged a mixture of both approaches, commonly by utilization of ANNs for the virtual ear and DSP methods for synthesis.
-
-\begin{center}
-\begin{table}[h*]
- \resizebox{\linewidth}{!}{\begin{tabular}{||c c c c||} 
-work & feature extraction & synthesis & specilization & \hline
-Oord et al & CNN & CNN &Speech& \hline
-Yamamoto et al & GAN & GAN&Speech & \hline
-Aouameur et al & Latent layer& Decoding of Latent Layers & Percussion & \hline
-Ramires et al & Latent layer & Decoding of Latent Layers & Percussion & \hline
-Yee-King et al & LSTM on Paremters & DSP & Synth Pads & \hline
-\end{tabular}}
-\caption{for reference, will delete} % AH: Fix the table up and keep it.
-\end{table}
-\end{center}
-Numerous deep, neural network models have been proposed and utilized for the purpose of signal generation in recent years.
-WaveGans and WaveNet have been subject to significant improvements and experiments since their proposal~\cite{nsynth2017,yamamoto2020parallel,oord2017parallel}.
-Most relevant to us are recent works by Aoumaeur et al.
-in which variational AutoEncoders (VAE's) have been utilized for generation of percussive samples~\cite{aouameur2019neural}; As well as Ramires et al's work in generation of percussive sounds by guiding the output of a feedforward neural network via simple and explainable desired features.
-Automatic programming of virtual synthesizers has also been a topic of interest.
-In early 2000s, Interactive Genetic Algorithms (IGA's) were utilized for the generation of new sounds with various sound-engines~\cite{johnson1999exploring,dahlstedt2001creating}.
-More recent work by Yee-King et al.~\cite{yee2018automatic} used Long short-Term Memory (LSTM) models and genetic algorithms to find the exact parameters used to create a group of sounds.
-The sounds approximated were made by the same virtual synthesizer, not an external source; making the eventual replication certain even with random search.
-Since this work appears more focused on pads and textures rather than drums, feature matching appears to not be concerned with the envelope of the sounds but rather the frequency content within arbitrary time windows.
-Yet another recent work by Esling et al.
-used a large dataset of over 10,000 presets for a commercial VST synthesizer to learn a latent parameter space which can be sampled for creation of new audio~\cite{esling2019universal}.
-As stated before, our work explores the rapid approximation of percussion sounds with no previous knowledge about the sonic capabilities of our virtual synthesizer, exploring the actual parameter space rather than its latent representation.
+Instead of learning weights and parameters in an audio-generation neural network, we wish to generate, search, and tune synthesizers to produce percussion sounds.
 
 \bibliographystyle{apacite}
-% Place your own .bib file here:
 \bibliography{CSMC_MUME_LaTeX_Template.bib}

### 2020-08-18 templates_aimusic2020/paper.tex
Updates from Overleaf

@@
 
+\subsection{Related Works}
+\label{related_works}
+\begin{center}
+\begin{table}[h]
+\resizebox{\linewidth}{!}{\begin{tabular}{|c c c c|} 
+\hline
+Work & Feature extraction & Synthesis & Specilization & \hline
+Oord 2017 & CNN & CNN &Speech& \hline
+Yee-King 2018 & LSTM on Paremters & DSP & Synth Pads & \hline
+Aouameur 2019 & Latent layer& Decoding of Latent Layers & Percussion & \hline
+Ramires 2020 & Latent layer & FeedForward Network & Percussion & \hline
+Yamamoto 2020 & GAN & GAN & Speech & \hline
+\end{tabular}}
+\caption{Quick reference of recent related works}
+\end{table}
+\label{table:recent_works}
+\end{center}
+Numerous deep, neural network models have been proposed and utilized for the purpose of signal generation in recent years.
+WaveGans and WaveNet have been subject to significant improvements and experiments since their proposal~\cite{nsynth2017,yamamoto2020parallel,oord2017parallel}.
+Most relevant to us are recent works by Aoumaeur et al.
+in which variational AutoEncoders (VAE's) have been utilized for generation of percussive samples~\cite{aouameur2019neural}; As well as Ramires et al's work in generation of percussive sounds by guiding the output of a feedforward neural network via a small set of latent features~\cite{ramires2020neural}.
+Automatic programming of virtual synthesizers has long been a topic of interest.
+In early 2000s, Interactive Genetic Algorithms (IGA's) were utilized for the generation of new sounds with various sound-engines~\cite{johnson1999exploring,dahlstedt2001creating}.
+More recent work by Yee-King et al.~\cite{yee2018automatic} used Long short-Term Memory (LSTM) models and genetic algorithms to find the exact parameters used to create a group of sounds.
+The sounds approximated were made by the same virtual synthesizer, not an external source; making the eventual replication certain even with random search.
+Since this work appears more focused on pads and textures rather than drums, feature matching appears to not be concerned with the envelope of the sounds but rather the frequency content within arbitrary time windows.
+Yet another recent work by Esling et al.
+used a large dataset of over 10,000 presets for a commercial VST synthesizer to learn a latent parameter space which can be sampled for creation of new audio~\cite{esling2019universal}.
+As stated before, our work explores the rapid approximation of percussion sounds with no previous knowledge about the sonic capabilities of our virtual synthesizer, exploring the actual parameter space rather than its latent representation.
+
 \subsection{Our Approach}
@@
 We call these two components the \emph{virtual synthesizer} and \emph{virtual ear} respectively.
+\begin{figure}[t!]
+    \begin{center}
+    \textbf{Data Overview}
+    \makebox[\textwidth]{
+    \includegraphics[width=1.1\linewidth]{images/venn_data.pdf}}
+    \end{center}
+    \caption{ 
+    Scales are symbolic (True scales are not measurable and/or subjective).
+Our positive samples, $\mathcal{T^{+}}$, is a small fraction of a wide variety of percussive sounds that are conceivable.
+The size of $\mathcal{T^{-}}$ can be set to any number(we can generate any number of random samples), but we prefer to keep it no larger than  $\mathcal{T^{+}}$.
+$\mathcal{H}$ is a series of sounds sent to the ear for classification.
+The ideal ear will detect  $\mathcal{H^{+}}$, the overlap of $\mathcal{H}$ and $\mathcal{N}$, with high precision and recall.
+    }
+\label{fig:ven_data}
+\end{figure}
 
@@
 Waves can be approximated via a series of samples, associating time steps to a discrete range of amplitude values.~\textit{Digital synthesis} of audio is the process of creating these discrete values.
+Unlike the majority of the works mentioned in Section~\ref{related_works}, we do not employ probabilistic models for the synthesizer component. Our decision is based on the following factors:
+\begin{itemize}
+    \item \textit{Interpretability and Expansion}:
+    \item \textit{Novelty and Creativity}: Given large sets of examples, generative models such as VAEs and GANS have proven capable of generating samples similar to the exemplars.
+we are not aiming for perfect imitations, rather, we want to work with the limitations of any tractable sound source to create its novel approximations of a given sound category.
+    \item \textit{Efficiency}:
+
+\end{itemize}
 
@@
 
-\subsection{Neural Networks and Sound}
-
-\begin{center}
-\begin{table}[h*]
-\hline
- \resizebox{\linewidth}{!}{\begin{tabular}{||c c c c||} 
-work & feature extraction & synthesis & specilization & \hline
-Oord et al & CNN & CNN &Speech& \hline
-Yamamoto et al & GAN & GAN&Speech & \hline
-Aouameur et al & Latent layer& Decoding of Latent Layers & Percussion & \hline
-Ramires et al & Latent layer & FeedForward Network & Percussion & \hline
-Yee-King et al & LSTM on Paremters & DSP & Synth Pads & \hline
-\end{tabular}}
-\caption{Quick reference for related works}
-\end{table}
-\end{center}
-
 \section{Implementation}

### 2020-08-18 templates_aimusic2020/paper.tex
Updates from Overleaf

@@
 \usepackage{csquotes}
+\usepackage{appendix}
 
@@
 Drums are a subcategory of percussive instruments.
-Drum sounds such as kick and snare are two of the most universally recognized examples of percussion~\cite{barry2005drum}.
 Almost any object which is struck to produce noise can be referred to as a drum~\cite{latham2002oxford}.
+Kicks and snares are two of the most universally recognized examples of percussion~\cite{barry2005drum}.
 The term \enquote{Percussion} often encompasses all drums and may include the additional instruments which may be rubbed, plucked, blown, etc; A more strict definition of percussion can be used interchangeably with drums~\cite{latham2002oxford}.
@@
 Our goal here is to create a new, virtual source of novel drum sounds, which could then be used in electronic music compositions.
-
 By relying on recordings of \textit{real life} drum sounds, we are limited by what instruments exist in the real world and whether or not we have access to clean, one-shot recordings.
@@
 We call these two components the \emph{virtual synthesizer} and \emph{virtual ear} respectively.
-\begin{figure}[t!]
-    \begin{center}
-    \textbf{Data Overview}
-    \makebox[\textwidth]{
-    \includegraphics[width=1.1\linewidth]{images/venn_data.pdf}}
-    \end{center}
-    \caption{ 
-    Scales are symbolic (True scales are not measurable and/or subjective).
-Our positive samples, $\mathcal{T^{+}}$, is a small fraction of a wide variety of percussive sounds that are conceivable.
-The size of $\mathcal{T^{-}}$ can be set to any number(we can generate any number of random samples), but we prefer to keep it no larger than  $\mathcal{T^{+}}$.
-$\mathcal{H}$ is a series of sounds sent to the ear for classification.
-The ideal ear will detect  $\mathcal{H^{+}}$, the overlap of $\mathcal{H}$ and $\mathcal{N}$, with high precision and recall.
-    }
-\label{fig:ven_data}
-\end{figure}
 
-\subsection{Virtual Synthesizer Design}
+\section{Virtual Synthesizer Design}
+
+\begin{table}[htbp]
+\centering
+\resizebox{\columnwidth}{!}{\begin{tabular}{ |c|c|c| } 
+\hline
+Parameters & Value Range & notes and constraints\\
+\hline \hline
+Attack & 0-3 & A-D-S-R values relative\\
+Decay & 0-3 & relative to A-S-R\\
+Sustain & 0-3 & relative to A-D-R\\
+Release & 0-3 & relative to A-D-S\\
+OSC type & sine,square,saw & tone type\\
+IsNoise & boolean & whether to \newline use OSC type to generate noise\\
+Length & 0-1 second & - \\
+StartTime & 0-1 second & Length+Start$<$1\\
+Amplitude & 0.1-1 & 1 = max amplitude\\
+Pitches(notes) & list of pitches &  range of C0(16.35hz) to B9 \\
+HP filter Cuttoff & 0-20000hz & -\\
+LP filter Cuttoff & 20000-HP & never lower than HP cutoff\\
+Filter Order & 4,8,16 & butterworth filter order \\
+\hline
+\end{tabular}}
+\caption{Synthesizer submodule Parameters.
+Despite the simplicity of the parameters and our efforts at constraining the ranges, the number of parameters that can be randomly chosen for each submodule is in the order of $10^{15}$ }
+\label{table:submodule_params}
+\end{table}
+
 Sound is product of physical disturbances, causing vibrations in our mediums.
@@
 \begin{itemize}
-    \item \textit{Interpretability and Expansion}:
     \item \textit{Novelty and Creativity}: Given large sets of examples, generative models such as VAEs and GANS have proven capable of generating samples similar to the exemplars.
-we are not aiming for perfect imitations, rather, we want to work with the limitations of any tractable sound source to create its novel approximations of a given sound category.
-    \item \textit{Efficiency}:
-
+In this work, we are not aiming for perfect imitations; Following Boden's definition of exploratory creativity as an emergent property of generative work within confined rule sets~\cite{boden2009computer}, we work within the limitations of any tractable sound source to create its  approximations of a given sound category.
+Within the music realm, prominent instance of exploratory creativity is the persistent aesthetics of 8-bit soundtracks, remaining popular long after the original constraints are lifted~\cite{collins2007loop}.
+    \item \textit{Interpretability}: Neural networks are often described as black boxes~\cite{basheer2000artificial}.
+Their highly recursive structure makes modern explanation methods such as saliency maps unreliable~\cite{rudin2019stop}.
+    \item \textit{Speed of Rendering at high sampling rates}: Despite the utilization of powerful GPUs, the standard sampling rate in most audio generation work utilizing neural is under 24 khz \cite{yamamoto2020parallel,oord2017parallel,aouameur2019neural,ramires2020neural}.
+However, a significant number of untrained human ears can detect a change in quality of audio between sampling rates of 192 khz and the industry standard of 44.1 khz \cite{reiss2016meta}.
+In this work, we fix our sampling rate to the 48 khz standard.
 \end{itemize}
@@
 \includegraphics[width=0.45\linewidth,angle =-90 ]{images/periodic_function.png}
-\caption{A computer can simulate waveforms by utilizing periodic functions. Digital waveforms are discrete approximations of analogue waves. \cite{mitchell2009basicsynthChap5} }
+\caption{A computer can simulate waveforms by utilizing periodic functions. Digital waveforms are discrete approximations of analogue waves. ~\cite{mitchell2009basicsynthChap5} }
 \end{figure*}
@@
 
-\subsection{How Can a Computer Evaluate Sounds?}
-Automatic evaluation of sounds is an essential component of our work: A thorough manual evaluation of outputs is not possible when hundreds can be created in a second.
-In our work, we find simple features such as frequency content (high pitch vs low pitch), length, and envelope (change in loudness, how fast the sounds reaches its maximum loudness and fades away) to be powerful for the categorization of drum sounds.
-Later on we will discuss our algorithms for extraction of these and other features in~\ref{implementation}.
-We will also discuss how these extracted features were used to train models that can automatically categorize new sounds.
+We opted for a set of classical DSP methods to build our synthesizer.
+For our project, we used the python based Pippi library for sound generation\footnote{https://github.com/luvsound/pippi}.
+This library uses a C back-end\footnote{https://github.com/PaulBatchelor/Soundpipe} and focuses on fast offline generation of audio signals.
+Our virtual synthesizer contains a set of one or more submodules.
+Each submodule is a self-contained noise making unit.
+Submodules have identical sets of parameters, but widely different outputs can be achieved depending on the values assigned.
+The set of parameters available to each submodule is highlighted in Table~\ref{table:submodule_params}.
+The sonic output of the virtual synthesizer is the normalized addition of the sonic output of its submodules.
+Our implementation of a synthesizer can have any number of submodules.
+The parameters that dictate the output signal of each submodule as well as the range of values each parameter can take are shown in table~\ref{table:submodule_params}.
+We call the number of submodules in each virtual synthesizer the \textit{stack size}.
+We call the sets of parameter values that characterize a synthesizer's submodules a \textit{program} (analogous to a preset for a VST).
 
-\section{Implementation}
-We conceptualized a general pipeline for approximation of sounds: A synthesizer creates random noise while a virtual ear rapidly evaluates the outputs and outputs a score which is used for the separation of undesired outputs from desired ones.
+\section{Virtual Ear Design}
+\subsection{Feature Extraction}
+To train our virtual ear, we require the generalizable, domain agnostic features.
+In this work we rely entirely on Fast Fourier Transform (FFT) and by extension Short-time Fourier Transforms (STFT) for feature extraction.
+Using FFT, a signal can be represented by a vector with each index corresponding to a frequency-bin (a range of frequencies too close to be distinguishable) and the value at each index corresponding to the combined-magnitude of the frequencies within the bin.
+STFT can be employed when variations in frequency-bin intensities are of interest, often by the application of the FFT to a sliding time-window to create an estimation of frequencies present within each time-frame.
+
+\begin{figure}[htbp]
+\centering
+\textbf{Visual Representation of Raw Features}\par\medskip
+    \subcaptionbox{Randomly generated audio with percussive qualities, resembling a tight snare}{\includegraphics[width=1\columnwidth]{images/ff2.pdf}}
+    \subcaptionbox{A randomly generated noise with a percussive envelop but non-percussive frequency features (modulated pitch)}
+    { \includegraphics[width=1\columnwidth]{images/ff3.pdf}}
+\caption{Graphed representation of features extracted for 2 different randomly generated samples.
+Sample $b$ is an example of randomly generated noise that we found suitably similar to a snare sound.
+Sample $c$ is an example of a randomly generated noise where the spectrum features are necessary for proper classification.}
+\label{fig:stackspectrums}
+\end{figure}
+Various works have demonstrated effective reconstruction of signals given their STFT~\cite{nawab1983signal,griffin1984signal}.
+If a signal can be faithfully reconstructed from its STFT, the STFT may be relied on as source of fundamental features necessary for audible signal categorization.
+
+Using only the STFT of signals as source of feature extraction we defined 3 transformation functions which we believe to capture important, unique attributes of percussive sounds.
+These functions were applied at training time to 1 second audio samples before being sent to a classifier.
+
+\subsection{The Models}
+\label{TPE_models}
+Using the described features, we trained several neural network models for Phase 1 and 2 in the Pytorch environment.
+The task of Phase 1 is to separate drums from not-drums (DrumVsNotDrum, or DVN).
+The task of Phase 2 is to categorize drums and percussion (DrumVsDrum, or DVD).
+We kept our feature space small, making it viable for feature selection and model design to be done on a trial and error basis.
+For all models, accuracy is calculated by prediction of all test dataset labels and the loss function and optimizer are Categorical-CrossEntropy and Adam respectively.
+Training continues until no reduction in loss and accuracy is observed in 10 epochs.
+All activation functions are PReLU:
+\begin {enumerate}
+\item FC-DVN: Fully connected network trained on Envelope features, reaching 97\% accuracy on our test data for Phase 1. With size of 10x5x10.
+\item CNNLSTM-DVN: A combination of CNN and LSTM models, where the CNN model extracts higher level features that are fed temporally to an LSTM cell.
+This model is trained on spectrum data and reaches 98\% accuracy on our test set.
+Its structure is the combination of a CNN with 2 output channels and kernel size $(7,3)$; Followed by an LSTM model of hidden size 800 and a fully connected layer of size 20x2.
+\item E+F-DVD: A fully connected model trained on a concatenation of envelope and frequency features. Reaching 80\% accuracy for 6-way drum categorization in Phase 2. Size of 50x10x2x6.
+\item CNN-DVD: A CNN model trained on Spectrum features.
+Reaching 82\% accuracy in a 6-way drum categorization in Phase 2.
+A combination of a CNN model with output channel size of 4, kernel of size of 5, another CNN model with output channel size of 8 and kernel of size 3.
+Followed by a fully connected network of shape 100x20x6.
+\item FC-DVD: Fully connected 3 layer neural net with 78\% accuracy for 6-way drum categorization in Phase 2. Size of 400x200x50.
+\end{enumerate}
+The parameters are hand-picked and un-tuned.
+As discussed in Section~\ref{surveys}, higher accuracy rates in these models do not translate to higher agreeableness with humans.
+leading us to believe that model accuracy on test data alone cannot be relied upon when the domain of sounds
+being categorized is switched from original percussion samples to virtual synth sounds.
+
+With our models showing high accuracy on testing data, we combine models in order to increase the efficacy of each phase and address the \enquote{open set problem} for our task.
+For Phase 1 we only determine sounds as percussive if both FC-DVN and CNN-LSTM have determined it as such with over 90\% confidence.
+For the majority of our random generations that is not the case, but if a randomly generated sound has passed this phase, our three categorizers assign their categorizations to this sound.
+These categorizers have a moderate degree of agree-ability as seen in~\ref{surveys}, but often the decision is not unanimous.
+The fourth method of categorization, \enquote{averaged-cat}, is implemented by taking the sum of the softmax outputs of all three categorizers, using it to determine the category.
+
+These models can be combined and weighted in various ways and the confidence thresholds can be modified in order to implement \enquote{virtual ears} with different properties.
+A glaring issue in the current implementation is the treatment of softmax outputs as a reasonable measure of a model's confidence.
+As a result, some models may have unwarranted higher confidence in their scores, skewing attempts at finding a consensus.
+
+\begin{enumerate}
+\item Envelope Transformation: The goal of this feature is to capture the changes in loudness for the duration of the signal.
+Using STFT we generate a matrix $M_{i \times j}$ with rows $i$ and columns $j$ corresponding to time steps and frequency bins respectively, and with values $v_{i \times j}$ indicating the magnitude of the frequency bin $j$ at each time-step $i$.
+Information about the envelope of the signal can be extracted by summing the values of $M$ for each time-step (or row $i$), giving us a feature vector $v_i$.
+This vector is then normalized to the range of 0 to 1.
+The information contained in this vector is similar to that of a Root-Mean-Square measurement.
+\item Frequency Transformation: A static, normalized snap-shot of the the frequencies present within the audio.
+The calculation of this feature vector is similar to the envelope, but the summation is done along the frequency axis.
+Another important distinction is that since capturing an adequate frequency resolution is important for this transformation, we utilized shorter hop-sizes and wider windows.
+A Mel Scale transformation was also applied in hopes that the captured features better represent human perception of frequencies.
+\item Spectrum Transformation: This function is simply a Mel Scaled STFT with its values normalized from 0-1.
+Since this features is a 2D matrix rather than a vector it captures more information about our signal but requires heavier, more complex computational methods to be utilized.
+\end{enumerate}
+
+% \section{Implementation}
+% We conceptualized a general pipeline for approximation of sounds: A synthesizer creates random noise while a virtual ear rapidly evaluates the outputs and outputs a score which is used for the separation of undesired outputs from desired ones.
 This approach assumes that a fraction of the randomly generated sounds can be substituted for percussion and that the synthetic ear will assign higher evaluation scores to this subset.
+% \begin{itemize}
+%     \item \textit{Virtual Synthesizer}: A flexible, deter\-min\-istic, and tract\-able gener\-ator which can create audio. 
+%     \item \textit{Virtual Ear}: An ear that returns an evaluation of an audio sample; estimating the effectiveness of an audio sample's fulfillment of a producers requirements.
+The ear's evaluation guides the generation process towards a desired path, making it a crucial component of our pipeline.
+% \end{itemize}
+
+\label{gens}
+\label{surveys}
+\section{Results}
+ In the previous chapter, we discussed our implementation of a \emph{virtual synthesizer}, which generates 1 second long sounds (or sonic noise) based on its parameters.
+We also discussed our expectations of an ideal \emph{virtual ear} along with multiple implementation attempts and measurements for accuracy.
+Putting these components together, we conceptualized a generative pipeline for creation of novel drum sounds, shown in figure~\ref{fig:pipeline_outline}.
+
+ We expect the virtual synthesizer to make sounds, which we call \enquote{synthetic noise}.
+We also expect the ideal virtual synthesizer to create identical sounds, given the same program.
+We verified These claims in Section~\ref{chap3:synth_deterministic}.
+Much harder to verify are our expectations of the virtual ear.
+If a small subset of synthetic noise can stand in for percussive sounds, then the ideal synthetic ear will be able to the desired sounds from noise with high recall and precision.
+Low recall will cause a slow-down of the pipeline and loss of novel sounds.
+Low precision will make manual cleanup of generated samples a requirement.
+Critically, manual over-sight is necessary to assess the performance of the ear.
+
+To assess the performance of each pipeline, we randomly create drum programs and generate and the corresponding signal.
+This signal is then fed through the ear model to determine if the signal is percussive.
+If so, a category is assigned to the sound.
+This sound and the corresponding synthesizer program are saved to hard-disk.
+Here we assess the success rate of two different pipelines by manual inspection and categorization of a randomly selected subset of its results.
+We cross reference the manual categorizations with the categories assigned by the virtual ear: Do we agree that the sounds are percussive?
+Do we agree with the drum group assigned to the percussive sounds?
+
+ \section{Survey of Two-Phased Ear Performance}
+
+\begin{table}[htbp]
+ \resizebox{\linewidth}{!}{\begin{tabular}{||c c c c c c c||} 
+ \hline
+ Drop Rule & Size & HvH & H+FC & H+CNN & H+ALL & 3 models \\ [0.5ex] 
+ \hline
+ No Drops & 257 &0.37 & 0.35 & 0.36 & 0.36 & 0.28\\ 
+ \hline
+ Assigned \enquote{Bad} By Both & 236 & 0.31 & 0.37 & 0.37 & 0.38 & 0.30 \\
+ \hline
+ Assigned \enquote{Bad} By Either & 180 & 0.47 & 0.50 & 0.48 & 0.48 &  0.34 \\
+ \hline
+ Assigned \enquote{Bad} or \enquote{Other} By Either & 154 & 0.47 & 0.59 & 0.54 & 0.50 &  0.35 \\
+ \hline
+\end{tabular}}
+\caption{\label{kappa_table_TPE}Table of Fleiss' kappa coefficient to measure the degree of agreement between persons (HvH), persons with FC model (H+FC), persons with CNNLSTM model, persons with all models (H+ALL), and between the 3 models.
+\enquote{Drop Rule} column indicates if any samples were dropped.
+We show the measurements after dropping samples if they are deemed bad by either or both responders.
+We also show measurements after dropping the \enquote{other} category along with samples deemed bad by either responder.
+}
+\end{table}
+To measure the quality of the samples produced by our pipeline combined with the TP ear models, we run the model until an adequate number of samples in each category are saved to disk.
+Next, we randomly generated around 50 samples in the following categories: \enquote{snare}, \enquote{kick}, \enquote{hat}, \enquote{clap} and \enquote{other} (combination of rims,
+shakers and unusual percussive sounds).
+This gave us a total of 257 samples.
+These samples were determined to be percussive and then categorized by 4 different models (FC, CNNLSTM, E+F and AVG).
+We ensured a balanced division between samples of stack size 1, 2 and 4 (each stack is responsible for a third of the samples under each category).
+Both reviewers then categorized these samples without knowledge of other categorizations (person or computation models).
+It's important to note:
 \begin{itemize}
-    \item \textit{Virtual Synthesizer}: A flexible, deter\-min\-istic, and tract\-able gener\-ator which can create audio. 
-    \item \textit{Virtual Ear}: An ear that returns an evaluation of an audio sample; estimating the effectiveness of an audio sample's fulfillment of a producers requirements.
-The ear's evaluation guides the generation process towards a desired path, making it a crucial component of our pipeline.
+    \item Each responder had an additional category of bad for samples that they deemed not percussive. The \enquote{bad} category indicates that the sample should have been skipped in Phase 1. 
+    \item With 6 categorization groups, responders had the same categorization in 47\% of cases.
+    \item The agreement between the responders and AVG was 44\% and 47\%.
+    \item Of 257 samples, the responders agreed with FC, CNNLSTM, AVG and E+F respectively in 78, 76, 76 and 46 of cases.
+This indicates no major difference in model types and agree-ability, with E+F being the worst performer.
 \end{itemize}
-We wish to leverage AI technologies, heuristic search, and DSP methods for the synthesis of novel audio.
-The work here is motivated by the idea of finding new, convenient methods for the expansion of a music producer's library of sounds.
-We demonstrate our work in combining machine listening and automatic synthesizer programming to find pieces of audio which can be used as drums.
-Using the generation of short, percussive audio samples as a starting point, this project is a proof of concept for a modular, generative pipeline of novel, one-shot audio samples.
-Design decisions were made such that this approach can be modified for creation of other, non-percussive sound-types.
-Instead of learning weights and parameters in an audio-generation neural network, we wish to generate, search, and tune synthesizers to produce percussion sounds.
 
+\begin{figure}[h!]
+    \begin{center}
+    \textbf{Label Assignment Frequency}
+    \makebox[\textwidth]{
+    \includegraphics[width=1.1\linewidth]{images/cat_2p.pdf}}
+    \end{center}
+    \caption{Frequency of assigned labels by persons vs the true number of labels}
+\label{fig:freq-survey-2p}
+\end{figure}
+We assess the reliability of agreement between persons and categorization models via the Fleiss' kappa coefficient \cite{fleiss1971measuring}.
+The value of 0 or less for this coefficient indicates no agreement beyond random chance, and the value of 1 indicating perfect agreement.
+Our kappa measurements shocased in~\ref{kappa_table_TPE} lie within the 0.35-0.45 range, indicating mild to moderate agreement between persons and machines.
+We again measure this coefficient after dropping samples that were categorized as \enquote{bad} by the authors, as samples that persons deem to be \enquote{bad} indicate a failure in Phase 1 and should not have been categorized by the models at all.
+Dropping of samples that both authors deemed \enquote{bad} causes an 8\% reduction of our data (21 samples) and a small increase in kappa score.
+Dropping samples deemed bad by either reviewer resulted in a 30\% reduction of samples and relatively large increase in kappa scores.
+
+\subsection{Takeaways Of The Two Phased Pipeline Survey}
+\label{survey1_takeaway}
+\begin{itemize}
+    \item The survey brings into question the reliability of our phase 1 models, as 30\% of the generated samples were deemed not percussive by at least 1 reviewer and 8\% by both reviewers
+    \item The task of categorizing synthetic drums is difficult.
+Survey shows that the scale of agreement within persons as well as between persons and various model combinations is moderate at best, even after removal of \enquote{bad} samples.
+While the same models can easily achieve 98+ percent accuracy when tested on recorded drum samples.
+This may be a manifestation of the \enquote{open set recognition} problem.
+    \item While there is much room for improvement, our pipeline can generate and categorize drums and percussive sounds with a promising degree of success. 
+\end{itemize}
+
+ \section{Survey of Mixed-Models Ear Performance}
+ Keeping the other components of the pipeline the same, we replace the two-phased ear in the previous pipeline with the MME.
+Our survey differs from the previous survey in that the pipeline only creates the four drum categories.
+The \enquote{other} category is only assigned by survey responders.
+This means that two out of six possible categories are only available to responders, therefore there is an inherent bias towards worse agreeably scores compared to last survey.
+Our main concern here is changes in the amount of \enquote{bad} samples.
+We show measurments before and after dropping all \enquote{bad} and \enquote{other} samples for a fairer comparison with the TPE pipeline.
+
+ \begin{table}[t]
+ \resizebox{\linewidth}{!}{\begin{tabular}{||c c c c||} 
+ \hline
+ Drop Rule & Size & HvH & H+MME \\
+ \hline
+ No Drop & 300 & 0.336 & 0.250\\ 
+ \hline
+ Assigned Bad By Both & 249 & 0.200 & 0.260 \\
+ \hline
+ Assigned Bad By Either & 151 & 0.460 &  0.473 \\
+ \hline
+Assigned \enquote{Bad} or \enquote{Other} By Either  & 120 & 0.620   &  0.587 \\
+ \hline
+\end{tabular}}
+\caption{\label{kappa_table_MME}Table of Fleiss' kappa coefficient to measure the degree of agreement between persons (HvH) and persons and MME.
+We also measure the agreeability scores after dropping bad samples if both or either persons assigned the sample as such.
+We also measure agree-ability when all samples deemed \enquote{bad} or \enquote{other} by either person are removed.}
+\end{table}
+
+\begin{figure}[htpb]
+    \begin{center}
+    \textbf{Category Assignment Frequency For MME Survey}
+    \makebox[\textwidth]{
+    \includegraphics[width=1.1\linewidth]{images/cat_mme.pdf}}
+    \end{center}
+    \caption{Frequency of assigned labels by persons vs the true number of labels}
+\label{fig:freq-survey-2p}
+\end{figure} 
+\subsection{Takeaways Of The MME Pipeline Survey}
+\label{survey2_takeaway}
+The results from the two surveys are not easily comparable.
+However, no major improvements in agree-ability or a decrease in the number of bad samples can be seen, in fact, the opposite is more likely to be true.
+However, we are yielding comparable results to the TPE pipeline despite having a fraction of the features to learn from (latent layer + 10 envelope features).
+This shows that latent layers of an autoencoder network can be used as a low-dimensional proxy for representation of more complex inputs, despite the autoencoder not being trained for such a task.
+
+Agree-ability scores for MME pipeline are often lower, but we reiterate that this can be caused by having two out of six (rather than one out of six in the TPE pipeline) categories which are exclusive to survey responders.
+Supporting this hypothesis is the notable improvement in agree-ability observed after dropping all \enquote{bad} and \enquote{other} samples.
+Here, both persons agree with each other and with the MME at a stronger rate than in the TPE pipeline, despite having similar number of samples (120 for MME and 154 for TPE) and equal number of categories to choose from.
+This values are observed in the last rows of tables~\ref{kappa_table_TPE} and ~\ref{kappa_table_MME}.
+The higher DVD categorization accuracy achieved by the mixed-model ear compared to the best two-phaased ear is consistent with this observation: Given that the sound being categorized is a drum, the MME will yield better results that the TPE.
+However, the MME pipeline does not yield better results in the DVN task.
 \bibliographystyle{apacite}
@@
 
+\begin{appendices}
+\chapter{Datasets}
+\begin{table}[h!]
+\centering
+\begin{tabular}[width=\paperwidth]{|l|l|l|l|l|l|l|l|l|l|}
+\hline
+DB Name & kick & snare & clap & tom\_high & tom\_mid & tom\_low & hihat\_closed &  hihat\_open & rim \\ \hline
+MixedDB & 648 & 732 & 118 & 179 & 139 &  188 & 187 & 280 & 105 \\\hline
+\end{tabular}
+\caption{Database 1: Mixed sources}
+\label{db:self}
+\end{table}
+
+\begin{table}[h!]
+\centering
+\begin{tabular}{|l|l|l|l|l|l|l|l|l|}
+\hline
+DB Name & kick & snare & clap & tom & clap & hat & rim & shaker  \\ \hline
+RadarDB & 1054 & 842   & 353 & 349 &  353 & 1561& 131 & 121 \\ \hline
+\end{tabular}
+\caption{Database 2: Royalty free sounds sourced from \enquote{Music Radar}}
+\label{db:radar}
+\end{table}
+
+\begin{table}[h!]
+\centering
+\begin{tabular}{|l|l|l|l|l|l|}
+\hline
+ DB Name & kick & snare & clap & hat & other \\\hline
+ FreeDB & 533 & 372 & 230 & 105 & 281 \\ \hline
+\end{tabular}
+\caption{Database 3: Free sounds sourced from the \enquote{Sample Swap} project.
+Simplified for our purposes.
+The version available for download contains more sample groups.
+The \enquote{other} category contains a variety of percussive sounds.}
+\label{db:sampleswap}
+\end{table}
+
+\begin{table}[h!]
+\centering
+\begin{tabular}{|l|l|l|l|}
+\hline
+ Synth Noise Type & 1 Stack & 3 Stacks  & 5 Stacks \\ \hline
+ Number of Examples & 2000 & 2000 & 2000 \\ \hline
+\end{tabular}
+\caption{Database of random noise examples from our virtual synthesizers}
+\label{db:noise}
+\end{table}
+
+\chapter{Virtual Ear Models}
+% \begin{table}[htbp]
+% \centering
+% \begin{tabular}{|p{3cm}|p{8cm}|}
+% \hline
+%  Merged Name & Possible Merged Groups \\ \hline
+%  Kicks & low toms and kicks \\
+%  Toms & toms and mid toms \\
+%  Snares & snares and high toms  \\
+%  Hats & high hats and low hats \\ 
+%  Other & rims, shakers and other percussive sounds with few representative samples \\ \hline
+% \end{tabular}
+% \caption{These mappings may be used to simplify databases. }
+% \label{db:merge-map}
+% \end{table}
+\end{appendices}
+
 \end{document}

### 2020-08-19 templates_aimusic2020/paper.tex
Updates from Overleaf

--- 2020-08-18 templates_aimusic2020/paper.tex
@@
 For more than two decades research involving digital synthesis, heuristic search, and neural networks has been used for the generation of novel sounds.
-Our goal is to generate one-shot percussive samples by leveraging modern AI technologies alongside scalable signal generation methods.
+This work is a proof of concept in automatic programming of synthesizers towards their best approximation of drum sounds.
 We centered our approach around the combination of two central components: \begin {enumerate*} [label=(\roman*)] \item a \emph{virtual ear} capable of evaluating the proximity of unheard sounds to  and \item a dynamic \emph{virtual synthesizer} with a rich set of tractable parameters\end{enumerate*}.
-We present a generative pipeline that utilizes robust digital signal processing methods guided by supervised learning towards the generation of one-shot percussive sounds.
-We present our findings and measurements of the various approaches taken.
+We present a generative pipeline that utilizes classical digital signal processing functions guided by supervised learning towards the generation of one-shot percussive sounds.
+We present our findings and measurements of a number of approaches taken.
 Advantages, shortcomings and practicality of the employed methodologies are demonstrated.
@@
     \makebox[\textwidth]{
-    \fbox{\includegraphics[width=1.1\linewidth]{images/pipeline.pdf}}}
+    \fbox{\includegraphics[width=1\linewidth]{images/pipeline.pdf}}}
     \end{center}
@@
 WaveGans and WaveNet have been subject to significant improvements and experiments since their proposal~\cite{nsynth2017,yamamoto2020parallel,oord2017parallel}.
-Most relevant to us are recent works by Aoumaeur et al.
-in which variational AutoEncoders (VAE's) have been utilized for generation of percussive samples~\cite{aouameur2019neural}; As well as Ramires et al's work in generation of percussive sounds by guiding the output of a feedforward neural network via a small set of latent features~\cite{ramires2020neural}.
+Particularly relevant are the utilization of variational autoencoders (VAE's) for generation of percussive samples~\cite{aouameur2019neural} and generation of percussive sounds by decoding a small set of latent features~\cite{ramires2020neural}.
 Automatic programming of virtual synthesizers has long been a topic of interest.
@@
 We call these two components the \emph{virtual synthesizer} and \emph{virtual ear} respectively.
-\begin{figure}[t!]
-    \begin{center}
-    \textbf{Data Overview}
-    \makebox[\textwidth]{
-    \includegraphics[width=1.1\linewidth]{images/venn_data.pdf}}
-    \end{center}
-    \caption{ 
-    Scales are symbolic (True scales are not measurable and/or subjective).
-Our positive samples, $\mathcal{T^{+}}$, is a small fraction of a wide variety of percussive sounds that are conceivable.
-The size of $\mathcal{T^{-}}$ can be set to any number(we can generate any number of random samples), but we prefer to keep it no larger than  $\mathcal{T^{+}}$.
-$\mathcal{H}$ is a series of sounds sent to the ear for classification.
-The ideal ear will detect  $\mathcal{H^{+}}$, the overlap of $\mathcal{H}$ and $\mathcal{N}$, with high precision and recall.
-    }
-\label{fig:ven_data}
-\end{figure}
 
-\subsection{Virtual Synthesizer Design}
+\section{Virtual Synthesizer Design}
+\begin{table}[htbp]
+\centering
+\resizebox{\columnwidth}{!}{\begin{tabular}{ |c|c|c| } 
+\hline
+Parameters & Value Range & notes and constraints\\
+\hline \hline
+Attack & 0-3 & A-D-S-R values relative\\
+Decay & 0-3 & relative to A-S-R\\
+Sustain & 0-3 & relative to A-D-R\\
+Release & 0-3 & relative to A-D-S\\
+OSC type & sine,square,saw & tone type\\
+IsNoise & boolean & whether to \newline use OSC type to generate noise\\
+Length & 0-1 second & - \\
+StartTime & 0-1 second & Length+Start$<$1\\
+Amplitude & 0.1-1 & 1 = max amplitude\\
+Pitches(notes) & list of pitches &  range of C0(16.35hz) to B9 \\
+HP filter Cuttoff & 0-20000hz & -\\
+LP filter Cuttoff & 20000-HP & never lower than HP cutoff\\
+Filter Order & 4,8,16 & butterworth filter order \\
+\hline
+\end{tabular}}
+\caption{Synthesizer submodule Parameters.
+Despite the simplicity of the parameters and our efforts at constraining the ranges, the number of parameters that can be randomly chosen for each submodule is in the order of $10^{15}$ }
+\label{table:submodule_params}
+\end{table}
+
 Sound is product of physical disturbances, causing vibrations in our mediums.
@@
 \includegraphics[width=0.45\linewidth,angle =-90 ]{images/periodic_function.png}
-\caption{A computer can simulate waveforms by utilizing periodic functions. Digital waveforms are discrete approximations of analogue waves. \cite{mitchell2009basicsynthChap5} }
+\caption{A computer can simulate waveforms by utilizing periodic functions. Digital waveforms are discrete approximations of analogue waves~\cite{mitchell2009basicsynthChap5} }
 \end{figure*}
@@
 
-\subsection{How Can a Computer Evaluate Sounds?}
-Automatic evaluation of sounds is an essential component of our work: A thorough manual evaluation of outputs is not possible when hundreds can be created in a second.
-In our work, we find simple features such as frequency content (high pitch vs low pitch), length, and envelope (change in loudness, how fast the sounds reaches its maximum loudness and fades away) to be powerful for the categorization of drum sounds.
-Later on we will discuss our algorithms for extraction of these and other features in~\ref{implementation}.
-We will also discuss how these extracted features were used to train models that can automatically categorize new sounds.
+We opted for a set of classical DSP methods to build our synthesizer.
+For our project, we used the python based Pippi library for sound generation\footnote{https://github.com/luvsound/pippi}.
+This library uses a C back-end\footnote{https://github.com/PaulBatchelor/Soundpipe} and focuses on fast offline generation of audio signals.
+Our virtual synthesizer contains a set of one or more submodules.
+Each submodule is a self-contained noise making unit.
+Submodules have identical sets of parameters, but widely different outputs can be achieved depending on the values assigned.
+The set of parameters available to each submodule is highlighted in Table~\ref{table:submodule_params}.
+The sonic output of the virtual synthesizer is the normalized addition of the sonic output of its submodules.
+Our implementation of a synthesizer can have any number of submodules.
+The parameters that dictate the output signal of each submodule as well as the range of values each parameter can take are shown in table~\ref{table:submodule_params}.
+We call the number of submodules in each virtual synthesizer the \textit{stack size}.
+We call the sets of parameter values that characterize a synthesizer's submodules a \textit{program} (analogous to a preset for a VST).
 
-\section{Implementation}
-We conceptualized a general pipeline for approximation of sounds: A synthesizer creates random noise while a virtual ear rapidly evaluates the outputs and outputs a score which is used for the separation of undesired outputs from desired ones.
-This approach assumes that a fraction of the randomly generated sounds can be substituted for percussion and that the synthetic ear will assign higher evaluation scores to this subset.
-\begin{itemize}
-    \item \textit{Virtual Synthesizer}: A flexible, deter\-min\-istic, and tract\-able gener\-ator which can create audio. 
-    \item \textit{Virtual Ear}: An ear that returns an evaluation of an audio sample; estimating the effectiveness of an audio sample's fulfillment of a producers requirements.
-The ear's evaluation guides the generation process towards a desired path, making it a crucial component of our pipeline.
-\end{itemize}
-We wish to leverage AI technologies, heuristic search, and DSP methods for the synthesis of novel audio.
-The work here is motivated by the idea of finding new, convenient methods for the expansion of a music producer's library of sounds.
-We demonstrate our work in combining machine listening and automatic synthesizer programming to find pieces of audio which can be used as drums.
-Using the generation of short, percussive audio samples as a starting point, this project is a proof of concept for a modular, generative pipeline of novel, one-shot audio samples.
-Design decisions were made such that this approach can be modified for creation of other, non-percussive sound-types.
-Instead of learning weights and parameters in an audio-generation neural network, we wish to generate, search, and tune synthesizers to produce percussion sounds.
+\section{Virtual Ear}
+
+We are not looking for the perfect imitation of organic drums using a synthesizer.
+We seek to imitate drums using a synthesizer and even \textbf{prefer} for its generations to retain novel, unusual characteristics.
+The task assigned to the virtual ear is the rare acceptance of drum-like sounds and the inevitable rejection of most \enquote{noise} outputs from the virtual synthesizer.
+By definition, we cannot anticipate what these novel drums will sound like.
+Without manual inspection, all we know is that the accepted sounds are synthesizer noises which the synthetic ear has determined to be similar to drum-sounds.
+The virtual ear makes two critical decisions:
+\emph{
+\begin{quote}
+\text{Decision.1 Could the sound be used as a drum?}\label{Decision.1}
+\\
+\text{Decision.2 If it does sound like a drum, what type of drum should it be?}\label{Decision.2}
+\end{quote}
+ }
+
+\begin{figure}[htbp!]
+    \begin{center}
+    \textbf{Data Overview}
+    \makebox[\textwidth]{
+    \includegraphics[width=0.95\linewidth]{images/venn_data.pdf}}
+    \end{center}
+    \caption{ 
+    Scales are symbolic (true scales are not measurable and/or subjective).
+$\mathcal{N}$ is the set of percussive sounds a synthesizer is capable of making.
+Our positive samples, $\mathcal{T^{+}}$, is a small fraction of a wide variety of percussive sounds that are conceivable.
+The size of $\mathcal{T^{-}}$ can be set to any number(we can generate as any number of random samples), but we prefer to keep it no larger than  $\mathcal{T^{+}}$.
+$\mathcal{H}$ is a series of sounds sent to the ear for classification.
+The ideal ear will detect  $\mathcal{H^{+}}$, the overlap of $\mathcal{H}$ and $\mathcal{N}$, with high precision and recall.
+    }
+\label{fig:ven_data}
+\end{figure}
+\hypref{Decision.1} requires knowledge of what drums \textbf{do not} sound like, or knowledge of an infinitely large set, which cannot be fully represented via examples.
+An important consideration is that the source of sounds used in training the model (organic drum sounds) will be fundamentally different from the source of unlabeled sounds we wish to categorize (noise from a synthesizer).
+This issue is reflective of the OSR problem~\cite{geng2020recent,mundt2019open}.
+Figure~\ref{fig:ven_data} highlights a number of caveats with this approach.
+we denote $\mathcal{N}$ as the set of percussive sounds a synthesizer is capable of making.
+$\mathcal{T^{+}}$, our positive examples, is a set of sound extracted from material drums.
+$\mathcal{T^{-}}$, is a small subset of an infinite set which is meant to represent all noises which the synthesizer is capable of making.
+It likely includes sounds in $\mathcal{N}$.
+could be used as drums.
+During the hearing test, the virtual ear continually receives synthesizer noises ($\mathcal{H}$) for classification.
+The performance of the ear is measured by its precision and recall in finding the overlap between $\mathcal{H}$ and $\mathcal{N}$.
+It is important to ensure that the change in learning domains---particularly with the case of positive examples of percussive instruments---does not interfere with transformation of knowledge from the training of the ear to the hearing test.
+To maximize the transference of knowledge from one domain to another, we seek to learn from agnostic feature sets that capture fundamental characteristics of the data points.
+\subsection{Feature Extraction}
+To train our virtual ear, we require generalizable, domain agnostic features.
+Various works have demonstrated effective reconstruction of signals given their Short-time Fourier Transforms (STFT) ~\cite{nawab1983signal,griffin1984signal}.
+If the STFT of a signal can be used its reconstruction, perhaps it can be utilized as a source of fundamental features necessary for audible signal categorization.
+We defined 3 STFT transformation functions which we believe to capture important, unique attributes of percussive sounds (figure ~\ref{fig:stackspectrums}).
+Our transformations are GPU based, allowing their application in tandem to the training of the classifier or tuning of STFT transformation during hyper-paramter optimization (see Section~\ref{---}).
+
+\subsection{Classifiers}
+\label{classifiers}
+Two groups of classifiers are implemented: \emph{two phased ears} (TPEs) and \emph{embedding ears} (EEs).
+TPEs are a combination different models specializing in ~\hypref{Decision.2} or ~\hypref{Decision.1} and trained only with our transformation functions.
+EEs are trained on a highly compressed, automatically encoded representation of sounds and can give simultaneous answers to both questions.
+These encodings are extracted from the latent layer of a percussion autoencoder.
 
@@
 
+\begin{appendices}
+\chapter{Datasets}
+\label{appendix:A}
+\begin{table}[h!]
+\centering
+\begin{tabular}[width=\paperwidth]{|l|l|l|l|l|l|l|l|l|l|}
+\hline
+DB Name & kick & snare & clap & tom\_high & tom\_mid & tom\_low & hihat\_closed &  hihat\_open & rim \\ \hline
+MixedDB & 648 & 732 & 118 & 179 & 139 &  188 & 187 & 280 & 105 \\\hline
+\end{tabular}
+\caption{Database 1: Mixed sources}
+\label{db:self}
+\end{table}
+
+\begin{table}[h!]
+\centering
+\begin{tabular}{|l|l|l|l|l|l|l|l|l|}
+\hline
+DB Name & kick & snare & clap & tom & clap & hat & rim & shaker  \\ \hline
+RadarDB & 1054 & 842   & 353 & 349 &  353 & 1561& 131 & 121 \\ \hline
+\end{tabular}
+\caption{Database 2: Royalty free sounds sourced from \enquote{Music Radar}}
+\label{db:radar}
+\end{table}
+
+\begin{table}[h!]
+\centering
+\begin{tabular}{|l|l|l|l|l|l|}
+\hline
+ DB Name & kick & snare & clap & hat & other \\\hline
+ FreeDB & 533 & 372 & 230 & 105 & 281 \\ \hline
+\end{tabular}
+\caption{Database 3: Free sounds sourced from the \enquote{Sample Swap} project.
+Simplified for our purposes.
+The version available for download contains more sample groups.
+The \enquote{other} category contains a variety of percussive sounds.}
+\label{db:sampleswap}
+\end{table}
+
+\begin{table}[h!]
+\centering
+\begin{tabular}{|l|l|l|l|}
+\hline
+ Synth Noise Type & 1 Stack & 3 Stacks  & 5 Stacks \\ \hline
+ Number of Examples & 2000 & 2000 & 2000 \\ \hline
+\end{tabular}
+\caption{Database of random noise examples from our virtual synthesizers}
+\label{db:noise}
+\end{table}
+
+%=============
+\chapter{Audio Transformation functions}
+\label{appendix:B}
+\begin{figure}
+\centering
+\textbf{Visual Representation of Raw Features}\par\medskip
+    \subcaptionbox{Recorded hat sample}{    \includegraphics[width=1\columnwidth]{images/ff1.pdf}
+    }
+    \subcaptionbox{Randomly generated audio with percussive qualities, resembling a tight snare}{\includegraphics[width=1\columnwidth]{images/ff2.pdf}}
+    \subcaptionbox{A randomly generated noise with a percussive envelop but non-percussive frequency features (modulated pitch)}
+    { \includegraphics[width=1\columnwidth]{images/ff3.pdf}}
+\caption{Graphed representation of features extracted for 3 different samples.
+Sample $a$ is a recorded hat from our database.
+sample $b$ is an example of randomly generated noise with percussive qualities that we found suitably similar to a snare sound.
+Sample $c$ is an example of a randomly generated noise where the spectrum features are necessary for proper classification.}
+\label{fig:stackspectrums}
+\end{figure}
+\begin{enumerate}
+\item Envelope Transformation: Represents changes in loudness for the duration of the signal.
+Using STFT we generate a matrix $M_{i \times j}$ with rows $i$ and columns $j$ corresponding to time steps and frequency bins respectively.
+Values $v_{i \times j}$ indicating the magnitude of the frequency bin $j$ at each time-step $i$.
+Information about the envelope of the signal can be extracted by summing the values of $M$ for each time-step (or row $i$), giving us a feature vector that is normalized to the range of 0 to 1.
+The information contained in this vector is an alternative to Root-Mean-Square measurements of a sliding window over the signal.
+\item Frequency Transformation: A static, normalized snap-shot of the the frequencies present within the audio.
+The calculation of this feature vector is similar to the envelope, but the summation is done along the frequency axis.
+Another important distinction is that since capturing an adequate frequency resolution is important for this transformation, we utilized shorter hop-sizes and wider windows.
+A Mel Scale transformation was also applied in hopes that the captured features better represent human perception of frequencies.
+\item Spectrum Transformation: This function is simply a Mel Scaled STFT with its values normalized from 0-1.
+Spectrograms contain more information about the original signal but their analysis requires more complex computational methods.
+\end{enumerate}
+
+%================
+\chapter{Virtual Ear Classifier Definitions}
+\label{appendix:C}
+\section{Two Phased models}
+Using the described features, we trained several neural network models for Phase 1 and 2 in the Pytorch environment.
+The task of Phase 1 is to separate drums from not-drums (DrumVsNotDrum, or DVN).
+The task of Phase 2 is to categorize drums and percussion (DrumVsDrum, or DVD).
+We kept our feature space small, making it viable for feature selection and model design to be done on a trial and error basis.
+For all models, accuracy is calculated by prediction of all test dataset labels and the loss function and optimizer are Categorical-CrossEntropy and Adam respectively.
+Training continues until no reduction in loss and accuracy is observed in 10 epochs.
+All activation functions are PReLU:
+\begin {enumerate}
+\item FC-DVN: Fully connected network trained on Envelope features, reaching 97\% accuracy on our test data for Phase 1. With size of 10x5x10.
+\item CNNLSTM-DVN: A combination of CNN and LSTM models, where the CNN model extracts higher level features that are fed temporally to an LSTM cell.
+This model is trained on spectrum data and reaches 98\% accuracy on our test set.
+Its structure is the combination of a CNN with 2 output channels and kernel size $(7,3)$; Followed by an LSTM model of hidden size 800 and a fully connected layer of size 20x2.
+\item E+F-DVD: A fully connected model trained on a concatenation of envelope and frequency features. Reaching 80\% accuracy for 6-way drum categorization in Phase 2. Size of 50x10x2x6.
+\item CNN-DVD: A CNN model trained on Spectrum features.
+Reaching 82\% accuracy in a 6-way drum categorization in Phase 2.
+A combination of a CNN model with output channel size of 4, kernel of size of 5, another CNN model with output channel size of 8 and kernel of size 3.
+Followed by a fully connected network of shape 100x20x6.
+\item FC-DVD: Fully connected 3 layer neural net with 78\% accuracy for 6-way drum categorization in Phase 2. Size of 400x200x50.
+\end{enumerate}
+Unlike EE models, parameters are hand-picked and un-tuned.
+Higher accuracy rates in these models do not necessarily translate to higher agreeableness with surveyors.
+Since the positive sounds in the hearing test are sourced from a synthesizer, model accuracy on test data alone cannot be relied upon when the domain of sounds
+being categorized is switched.
+\section{Embedding Models}
+
+\begin{table}[[h]
+\begin{tabular}{|p{28mm}|p{25mm}|p{23mm}|p{50mm}|}
+\hline
+Layer-\# & Out Shape & Param Num & Details  \\ \hline
+Conv2d-1 & [-1, 8, 30, 20] &   208 & Encoder's input \newline
+Num. Channels:8\newline
+kernel:5x5\newline                  
+stride:1\newline    
+padding:2 \\ \hline
+ReLU-2 & [-1, 8, 30, 20] &   0 & \\  \hline
+MaxPool2d-3 & [-1, 8, 15, 10] & 0 &  kernel:5x5 \newline
+stride:2 \\ \hline
+Dropout-4 & [-1, 8, 15, 10] & 0 &  \\ \hline
+Linear-5 & [-1, 8] & 9,608 & Encoder's output \\ \hline
+Linear-6 & [-1, 256] & 2,304 & Decoder's Input \\ \hline
+Dropout-7 & [-1, 256] & 0 &  \\ \hline
+Linear-8 & [-1, 600 ] &  154,200& Decoder's output\\ \hline
+\end{tabular}
+\caption{CNN model design with latent size of 8. 30 and 20 are the assumed frequency bins and step size. Total number of parameters is 166,320. }
+\label{table:CNNAUTOENCODER}
+\end{table}
+
+\begin{table}[[h]
+\begin{tabular}{|p{28mm}|p{25mm}|p{23mm}|p{50mm}|}
+\hline
+Layer-\# & Out Shape & Param Num & Details  \\ \hline
+Linear-1 & [-1, 128]  & 76,928 & Encoder's input \\ \hline
+Dropout-2 & [-1, 128] & 0 &  \\ \hline
+Linear-3 & [-1, 8] & 9,608 & Encoder's output \\ \hline
+Linear-4 & [-1, 128] & 2,304 & Decoder's Input \\ \hline
+Dropout-5 & [-1, 128]  & 0 &  \\ \hline
+Linear-6  & [-1, 600 ] &  77,400 &Decoder's output\\ \hline
+\end{tabular}
+\caption{Fully connected model with only 1 hidden dimension for encoder and decoder.
+Designed assumes latent size of 8.
+30 and 20 are the assumed frequency-bins and step-size values.
+Total number of parameters is 156,512.}
+\label{table:FC1_AUTOENCODER}
+\end{table}
+
+\begin{table}[[h]
+
+\begin{tabular}{|p{28mm}|p{25mm}|p{23mm}|p{50mm}|}
+\hline
+Layer-\# & Out Shape & Param Num & Details  \\ \hline
+Linear-1 & [-1, 128]  & 76,928 & Encoder's input \\ \hline
+Dropout-2 & [-1, 128] & 0 &  \\ \hline
+Linear-3 & [-1, 32]  & 4,128 & \\ \hline
+Dropout-4 & [-1, 128] & 0 &  \\ \hline
+Linear-5 & [-1, 8] & 9,608 & Encoder's output \\ \hline
+Linear-4 & [-1, 32] & 2,304 & Decoder's Input \\ \hline
+Dropout-5 & [-1, 32]  & 0 &  \\ \hline
+Linear-4 & [-1, 128] & 2,304 & \\ \hline
+Dropout-5 & [-1, 128]  & 0 &  \\ \hline
+Linear-6  & [-1, 600 ] &  77,400 &Decoder's output\\ \hline
+\end{tabular}
+\caption{Fully connected model with 2 hidden dimensions for encoder and decoder.
+Designed assumes latent size of 8.
+30 and 20 are the assumed frequency-bins and step-size values.
+Total number of parameters is 163,232.}
+\label{table:FC2_AUTOENCODER}
+\end{table}
+
+\end{appendices}
 \end{document}

### 2020-08-19 templates_aimusic2020/paper.tex
bloated version. needs reduction

@@
 This work is a proof of concept in automatic programming of synthesizers towards their best approximation of drum sounds.
-We centered our approach around the combination of two central components: \begin {enumerate*} [label=(\roman*)] \item a \emph{virtual ear} capable of evaluating the proximity of unheard sounds to  and \item a dynamic \emph{virtual synthesizer} with a rich set of tractable parameters\end{enumerate*}.
+We centered our approach around the combination of two central components: \begin {enumerate*} [label=(\roman*)] \item a \emph{virtual ear} capable of evaluating the proximity of \enquote{unusual} sounds to drum sounds and \item a dynamic \emph{virtual synthesizer} with a rich set of tractable parameters\end{enumerate*}.
 We present a generative pipeline that utilizes classical digital signal processing functions guided by supervised learning towards the generation of one-shot percussive sounds.
@@
 Most sounds from the natural environment, and its flora and fauna are more complex than the output of a single oscillator.
-However, with careful programming, DSP techniques can be used to replicate almost any sound, which is why they have powered commercial digital synthesizers for over half a century ~\cite{jenkins2019analog}.
+However, with careful programming, DSP techniques can be used to replicate almost any sound, which is why they have powered coMEMrcial digital synthesizers for over half a century ~\cite{jenkins2019analog}.
 Another advantage to using DSP for sound generation is that the synthesizers we build using these functions are tractable: the output is determined by the input and reproducible.
@@
 
-\subsection{Classifiers}
+\subsection{Ear Types}
 \label{classifiers}
-Two groups of classifiers are implemented: \emph{two phased ears} (TPEs) and \emph{embedding ears} (EEs).
-TPEs are a combination different models specializing in ~\hypref{Decision.2} or ~\hypref{Decision.1} and trained only with our transformation functions.
-EEs are trained on a highly compressed, automatically encoded representation of sounds and can give simultaneous answers to both questions.
-These encodings are extracted from the latent layer of a percussion autoencoder.
+Two groups of classifiers are implemented: \emph{two phased ears} (TPEs) and \emph{Mixed Ear Models} (MEMs).
+TPEs combine different models specializing in ~\hypref{Decision.2} or ~\hypref{Decision.1} and trained only with our transformation functions.
+MEMs are a proof of concept attempt at addressing the OSR problem by usage of autoencoded representation of sounds as features.
+MEMs are trained using highly compressed, automatically encoded representation of sounds and can give simultaneous answers to both questions.
+Model specifications for TPE and MEMs can be found in Appendix~\ref{appendix:C}.
+We speculate that the features used to represent sounds plays a much more important role in determining outcomes, particularly when working with relatively small datasets.
 
+The features used by MEMs are encodings extracted from the latent layer of an autoencoder trained with MixedDB.
+To better understand the delineation potential of the encoded features, 64-dimensional latent representation of 20\% of MixedDB and 1000 Noise sounds were projected onto a 2 or 3-dimensional planes using t-SNE.
+Referring to~\hypref{Decision.1} and~\hypref{Decision.2}, we expect the drum sounds to be clustered together, with the majority of the synthetic noise sounds appearing away from these clusters.
+The projections confirmed that this is the case(see Appendix~\ref{appendix:E}).
+We are most interested in synthetic noise sounds which appear within or near these clusters.
+Do these synthetic noise sounds have drum like characteristics?\\
+To test this, we implemented interactive projection graphs.
+These graphs allow interactions such as playing the samples(by hovering the cursor on-top) and movement of the scene camera.
+Manual inspections revealed a noticeable, positive correlation between distance and similarity of a synthetic sound to drum clusters.
+
+\section{Pipelines and Surveys}
+\label{gens}
+\label{surveys}
+With our virtual synthesizer and virtual ears in place, we build two pipelines, one using all TPE models and the other using our best MEM model.
+To assess the performance of each pipeline, we randomly create drum programs and generate and the corresponding signal.
+This signal is then fed through the ear model to determine if the signal is percussive.
+If so, a category is assigned to the sound.
+This sound and the corresponding synthesizer program are saved to hard-disk.
+Here we assess the success rate of two different pipelines by manual inspection of sounds it has categorized as drums, as well as the category of those drums.
+The authors of this work attempt their own categorization of a randomly selected subset of each pipeline's results.
+We cross reference the manual categorizations with the categories assigned by the virtual ear: Do we agree that the sounds are percussive?
+Do we agree with the drum group assigned to the percussive sounds?
+
+ \section{Survey of Two-Phased Ear Performance}
+
+\begin{table}[htbp]
+ \resizebox{\linewidth}{!}{\begin{tabular}{||c c c c c c c||} 
+ \hline
+ Drop Rule & Size & HvH & H+FC & H+CNN & H+ALL & 3 models \\ [0.5ex] 
+ \hline
+ No Drops & 257 &0.37 & 0.35 & 0.36 & 0.36 & 0.28\\ 
+ \hline
+ Assigned \enquote{Bad} By Both & 236 & 0.31 & 0.37 & 0.37 & 0.38 & 0.30 \\
+ \hline
+ Assigned \enquote{Bad} By Either & 180 & 0.47 & 0.50 & 0.48 & 0.48 &  0.34 \\
+ \hline
+ Assigned \enquote{Bad} or \enquote{Other} By Either & 154 & 0.47 & 0.59 & 0.54 & 0.50 &  0.35 \\
+ \hline
+\end{tabular}}
+\caption{\label{kappa_table_TPE}Table of Fleiss' kappa coefficient to measure the degree of agreement between persons (HvH), persons with FC model (H+FC), persons with CNNLSTM model, persons with all models (H+ALL), and between the 3 models.
+\enquote{Drop Rule} column indicates if any samples were dropped.
+We show the measurements after dropping samples if they are deemed bad by either or both responders.
+We also show measurements after dropping the \enquote{other} category along with samples deemed bad by either responder.
+}
+\end{table}
+To measure the quality of the samples produced by our pipeline combined with the TP ear models, we run the model until an adequate number of samples in each category are saved to disk.
+Next, we randomly generated around 50 samples in the following categories: \enquote{snare}, \enquote{kick}, \enquote{hat}, \enquote{clap} and \enquote{other} (combination of rims,
+shakers and unusual percussive sounds).
+This gave us a total of 257 samples.
+These samples were determined to be percussive and then categorized by 4 different models (FC, CNNLSTM, E+F and AVG).
+We ensured a balanced division between samples of stack size 1, 2 and 4 (each stack is responsible for a third of the samples under each category).
+Both reviewers then categorized these samples without knowledge of other categorizations (person or computation models).
+Additionally, each responder had the option of labeling samples as \enquote{bad} for samples that they deemed not percussive.
+
+We assess the reliability of agreement between persons and categorization models via the Fleiss' kappa coefficient \cite{fleiss1971measuring}.
+The value of 0 or less for this coefficient indicates no agreement beyond random chance, and the value of 1 indicating perfect agreement.
+Our kappa measurements showcased in~\ref{kappa_table_TPE} lie within the 0.35-0.45 range, indicating mild to moderate agreement between persons and machines.
+We again measure this coefficient after dropping samples that were categorized as \enquote{bad} by the authors, as samples that persons deem to be \enquote{bad} indicate a failure in Phase 1 and should not have been categorized by the models at all.
+
+\section{Survey of Mixed-Models Ear Performance}
+ Keeping the other components of the pipeline the same, we replace the two-phased ear in the previous pipeline with the MME.
+Our survey differs from the previous survey in that the pipeline only creates the four drum categories.
+Our main concern here is changes in the amount of \enquote{bad} samples.
+We show measurements before and after dropping all \enquote{bad} and \enquote{other} samples for a fairer comparison with the TPE pipeline.
+
+ \begin{table}[t]
+ \resizebox{\linewidth}{!}{\begin{tabular}{||c c c c||} 
+ \hline
+ Drop Rule & Size & HvH & H+MME \\
+ \hline
+ No Drop & 300 & 0.336 & 0.250\\ 
+ \hline
+ Assigned Bad By Both & 249 & 0.200 & 0.260 \\
+ \hline
+ Assigned Bad By Either & 151 & 0.460 &  0.473 \\
+ \hline
+Assigned \enquote{Bad} or \enquote{Other} By Either  & 120 & 0.620   &  0.587 \\
+ \hline
+\end{tabular}}
+\caption{\label{kappa_table_MME}Table of Fleiss' kappa coefficient to measure the degree of agreement between persons (HvH) and persons and MME.
+We also measure the agreeability scores after dropping bad samples if both or either persons assigned the sample as such.
+We also measure agree-ability when all samples deemed \enquote{bad} or \enquote{other} by either person are removed.}
+\end{table}
+
+\subsection{Takeaways from These Surveys}
+\label{survey2_takeaway}
+The results from the two surveys are not easily comparable.
+However, no major improvements in agree-ability or a decrease in the number of bad samples can be seen, in fact, the opposite is more likely to be true.
+However, we are yielding comparable results to the TPE pipeline despite having a fraction of the features to learn from (latent layer + 10 envelope features).
+This shows that latent layers of an autoencoder network can be used as a low-dimensional proxy for representation of more complex inputs, despite the autoencoder not being trained for such a task.
+Agree-ability scores for MME pipeline are often lower, but we reiterate that this can be caused by having two out of six (rather than one out of six in the TPE pipeline) categories which are exclusive to survey responders.
+Supporting this hypothesis is the notable improvement in agree-ability observed after dropping all \enquote{bad} and \enquote{other} samples.
+Here, both persons agree with each other and with the MME at a stronger rate than in the TPE pipeline, despite having similar number of samples (120 for MME and 154 for TPE) and equal number of categories to choose from.
+This values are observed in the last rows of tables~\ref{kappa_table_TPE} and ~\ref{kappa_table_MME}.
+The higher DVD categorization accuracy achieved by the mixed-model ear compared to the best two-phaased ear is consistent with this observation: Given that the sound being categorized is a drum, the MME will yield better results that the TPE.
+However, the MME pipeline does not yield better results in the DVN task.
+\begin{itemize}
+    \item The survey brings into question the reliability of our phase 1 models, as 30\% of the generated samples were deemed not percussive by at least 1 reviewer and 8\% by both reviewers
+    \item The task of categorizing synthetic drums is difficult.
+Survey shows that the scale of agreement within persons as well as between persons and various model combinations is moderate at best, even after removal of \enquote{bad} samples.
+While the same models can easily achieve 98+ percent accuracy when tested on sounds from physical drum samples.
+    \item While there is much room for improvement, our pipelines can generate and categorize drums and percussive sounds with a promising degree of success. 
+\end{itemize}
 \bibliographystyle{apacite}
@@
 %=============
-\chapter{Audio Transformation functions}
+\chapter{Audio Transformation Functions}
 \label{appendix:B}
@@
 being categorized is switched.
-\section{Embedding Models}
 
+\chapter{AutoEncoder Structures and Hyper-Parameter Optimization}
+\label{appendix:D}
+\section{Possible Model Structures}
 \begin{table}[[h]
@@
 \end{table}
+\begin{table}[htbp!]
+\centering
+\begin{tabular}{|p{6cm}|p{6cm}|}
+\hline
+Hyper-Param. & Value  \\ \hline
+Model Type      &  CNN  \\ \hline
+Optimizer       & Adam  \\ \hline
+Hidden Layers   & -  \\\hline
+Learning Rate   &  0.001145\\ \hline
+Frequency Bins & 30 \\ \hline
+Time Steps & 20 \\ \hline
+Latent Size & 64 \\ \hline
+Regularization & 3.25^{-6}\\ \hline
+Dropout Rate & 0.5 \\ \hline
+\end{tabular}
+\caption{Top performing hyper-parameter set}
+\label{table:best_params}
+\end{table}
+\chapter{Embedded Feature Visualization}
+\label{appendix:E}
+\begin{figure}[]
+\centering
+\textbf{2 Dimensional Projection of Latent Variables}\par\medskip
+ \includegraphics[width=0.90\linewidth]{images/t-SNE_2d.pdf}
+\caption{Projection of an embedding model's low dimensional encoding on to a 2D plane. We implemented interactions for these graphs for manual inspection of samples. }
+\label{fig:2d_tsne}
+\end{figure}
+
+\begin{figure}[]
+\centering
+\textbf{3D t-SNE Projection}\par\medskip
+\mbox{\subfloat[]{\label{subfig:1} \fbox{\includegraphics[width=12cm,height=6.8cm]{images/3d_t-SNE_symdrum_type_cam0.pdf}}}}
+
+\mbox{\subfloat[]{\label{subfig:2} \fbox{\includegraphics[width=12cm,height=6.8cm]{images/3d_t-SNE_symdrum_type_cam3.pdf}}}}
+
+\fbox{\mbox{\subfloat[]{\label{subfig:2} \includegraphics[width=6cm,height=6cm]{images/3d_t-SNE_symdrum_type_cam1.pdf}}}
+\mbox{\subfloat[]{\label{subfig:2} \includegraphics[width=6cm,height=6cm]{images/3d_t-SNE_symdrum_type_cam2.pdf}}}}
+\caption{3D projections of the data used for Figure~\ref{fig:2d_tsne}. Interactive demos are also implemented for 3D projections.}
+\label{fig:3d_tsne}
+\end{figure}
 

### 2020-08-19 templates_aimusic2020/paper.tex
Updates from Overleaf

@@
 $\mathcal{T^{+}}$, our positive examples, is a set of sound extracted from material drums.
-$\mathcal{T^{-}}$, is a small subset of an infinite set which is meant to represent all noises which the synthesizer is capable of making.
-It likely includes sounds in $\mathcal{N}$.
-could be used as drums.
-During the hearing test, the virtual ear continually receives synthesizer noises ($\mathcal{H}$) for classification.
+$\mathcal{T^{-}}$, is a small subset of an infinite set which is meant to represent all noises which the synthesizer is capable of making and likely includes sounds in $\mathcal{N}$.
+During the hearing test, the virtual ear continually receives synthesizer noises for classification.
+The set of received noises is denoted as $\mathcal{H}$.
 The performance of the ear is measured by its precision and recall in finding the overlap between $\mathcal{H}$ and $\mathcal{N}$.
-It is important to ensure that the change in learning domains---particularly with the case of positive examples of percussive instruments---does not interfere with transformation of knowledge from the training of the ear to the hearing test.
+It is important to ensure that the change in learning domains ---particularly with the case of positive examples of percussive sounds--- does not interfere with transformation of knowledge from the training of the ear to the hearing test.
 To maximize the transference of knowledge from one domain to another, we seek to learn from agnostic feature sets that capture fundamental characteristics of the data points.
@@
 We defined 3 STFT transformation functions which we believe to capture important, unique attributes of percussive sounds (figure ~\ref{fig:stackspectrums}).
-Our transformations are GPU based, allowing their application in tandem to the training of the classifier or tuning of STFT transformation during hyper-paramter optimization (see Section~\ref{---}).
+Our transformations are GPU based, allowing their application in tandem to the training of the classifier or tuning of STFT transformation during hyper-paramter optimization (see Appendix~\ref{appendix:F}).
 
@@
 
+%========
+
+%==============
 \chapter{AutoEncoder Structures and Hyper-Parameter Optimization}
-\label{appendix:D}
-\section{Possible Model Structures}
-\begin{table}[[h]
-\begin{tabular}{|p{28mm}|p{25mm}|p{23mm}|p{50mm}|}
+% could do multi-objective pareto front stuff too
+Within the context of machine learning, a model's \emph{hyper-parameters} are fixed parameters which are set before the training begins (e.g number of layers, size of layers, loss function) and are not learned during the minimization procedure~\cite{bengio2000gradient}.
+To assist us with the construction of our model, we defined a number of possible choices for the architecture of our model and audio-transformers and used hyper-parameter optimization to extract promising sets of values~\ref{table:hyper_params}.
+
+The list of possible choices for the selected hyper-parameters can be found in table~\ref{table:hyper_params}.
+We included not only model parameters but also spectrogram transformation parameters within this search space, as GPU accelerated FFT calculations allows ad hoc audio transformations to take place parallel to the training process.
+We implemented 3 base models which are affected by these hyper-parameters.
+The \enquote{Model Type} parameter dictates whether CNN or fully connected models are selected; If a \enquote{fully connected} model is selected, the \enquote{hidden layers} parameter selects between the two implementations.
+The specifications for these models can be found in tables~\ref{table:FC1_AUTOENCODER},~\ref{table:FC2_AUTOENCODER} and~\ref{table:CNNAUTOENCODER}.
+
+Using the optuna optimization tools \cite{akiba2019optuna}, we conducted 500 search trials.
+The trial's success is measured in their final loss value, calculated by applying the model to test data-set.
+Each trials consisted of 20 epoch of training using a selected set of hyper-parameters.
+An additional 100 trials with 40 epochs of training were conducted following the initial 500 to test the effect of longer epochs.
+Each trial's intermediate results (loss at every n epoch,s where $0<n<20$) were reported to a multi-armed bandit based pruner for early stoppage of unpromising trials~\cite{li2017hyperband}.
+We employed a tree-structured parzen estimator for better navigation of the search space~\cite{bergstra2011algorithms,akiba2019optuna} but found short reversions to a random sampling coupled with a decrease in the frequency of pruning helpful in exiting local minima.
+\\
+
+\begin{table}
+\begin{tabular}{|p{3cm}|p{3cm}|p{3cm}|p{3cm}|}
 \hline
@@
 
-\begin{table}[[h]
-\begin{tabular}{|p{28mm}|p{25mm}|p{23mm}|p{50mm}|}
+\begin{table}
+\begin{tabular}{|p{3cm}|p{3cm}|p{3cm}|p{3cm}|}
 \hline
@@
 
-\begin{table}[[h]
+\begin{table}
 
-\begin{tabular}{|p{28mm}|p{25mm}|p{23mm}|p{50mm}|}
+\begin{tabular}{|p{3cm}|p{3cm}|p{3cm}|p{3cm}|}
 \hline
@@
 \end{table}
+
+\begin{figure}[htbp]
+\centering
+\textbf{Tracing the Best Loss Values}
+\includegraphics[width=12cm,height=7cm]{images/Optimization_History.pdf}
+\caption{Best loss values found during hyper-parameter optimization. The effect of a switch to random sampling and an increase of the pruning threshold can be observed during trials 270 and 310.}
+\label{chap3:bestvalues}
+\end{figure}
+
+\begin{figure}[htbp]
+\centering
+\textbf{Loss Value per Epoch for Top 10 Trials}
+\includegraphics[width=12cm,height=6.5cm]{images/loss_per_training.pdf}
+\caption{Loss value per epoch for top 10 trials.
+Some of the initial 500 trials appear in this list, despite having half the number of epoch steps.
+The learning curves tend to flatten quickly.
+Therefore, 20 epoch steps may be a reasonable number for measuring hyper-parameter viability.
+}
+\label{chap3:top10}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+    \textbf{Hyper-Parameters' Loss Correlation}
+    \makebox[\textwidth]{\includegraphics[width=0.95\paperwidth]{images/slice_plot.pdf}}
+      \caption{Sliced plot depicting the correlation between hyper-parameters and loss values.
+The color-scale shows the number of times each parameters has been used in a trial.
+Our sampling algorithm aims to utilize spaces with higher potential more often.
+}
+    \label{fig:slicegraph}
+    \end{center}
+
+\end{figure}
+
 \begin{table}[htbp!]
@@
 \end{table}
+
+%==============
 \chapter{Embedded Feature Visualization}

### 2020-08-20 templates_aimusic2020/paper.tex
Updates from Overleaf

@@
 \maketitle
+% For more than two decades research involving digital synthesis, heuristic search, and neural networks has been used for the generation of novel sounds.
+\begin{abstract}
+This work is a proof of concept in automatic programming of synthesizers towards their best approximation of drum sounds.
+Our approach is based on the combination of two central components: \begin {enumerate*} [label=(\roman*)] \item a \emph{virtual ear} capable of evaluating the proximity of \enquote{unusual} sounds to drum sounds and \item a dynamic \emph{virtual synthesizer} with a rich set of tractable parameters\end{enumerate*}.
+We present a modular design of a generative pipeline which utilizes (semi-)supervised learning and classical digital signal processing for the generation of one-shot percussive sounds.
+We present our findings and measurements of a number of approaches taken, particularly in regard to the implementation of an effective virtual ear.
+Advantages, shortcomings and practicality of the employed methodologies are demonstrated and discussed.
+We share a number of datasets, notably our curated dataset of free percussive sounds.
 
-\begin{abstract}
-Digital sound artists often require a variety of percussive samples for their music.
-For more than two decades research involving digital synthesis, heuristic search, and neural networks has been used for the generation of novel sounds.
-This work is a proof of concept in automatic programming of synthesizers towards their best approximation of drum sounds.
-We centered our approach around the combination of two central components: \begin {enumerate*} [label=(\roman*)] \item a \emph{virtual ear} capable of evaluating the proximity of \enquote{unusual} sounds to drum sounds and \item a dynamic \emph{virtual synthesizer} with a rich set of tractable parameters\end{enumerate*}.
-We present a generative pipeline that utilizes classical digital signal processing functions guided by supervised learning towards the generation of one-shot percussive sounds.
-We present our findings and measurements of a number of approaches taken.
-Advantages, shortcomings and practicality of the employed methodologies are demonstrated.
-We share our curated dataset of sounds and codebase\footnote{\url{https://github.com/imilas/Synths_Stacks_Search}} which can be used for its further expansion.
 \keywords{Automatic Synthesizer design. Machine Listening. Sound Analysis. Novelty and Originality}
@@
 Yet another recent work by Esling et al.
-used a large dataset of over 10,000 presets for a commercial VST synthesizer to learn a latent parameter space which can be sampled for creation of new audio~\cite{esling2019universal}.
+used a large dataset of over 10,000 presets for a coMEMrcial VST synthesizer to learn a latent parameter space which can be sampled for creation of new audio~\cite{esling2019universal}.
 As stated before, our work explores the rapid approximation of percussion sounds with no previous knowledge about the sonic capabilities of our virtual synthesizer, exploring the actual parameter space rather than its latent representation.
@@
 
-\begin{figure*}[htbp]
-\label{fig_example_sine}
-\centering
-\includegraphics[width=0.45\linewidth,angle =-90 ]{images/periodic_function.png}
-\caption{A computer can simulate waveforms by utilizing periodic functions. Digital waveforms are discrete approximations of analogue waves~\cite{mitchell2009basicsynthChap5} }
-\end{figure*}
+% \begin{figure*}[htbp]
+% \label{fig_example_sine}
+% \centering
+% \includegraphics[width=0.3\linewidth,angle =-90 ]{images/periodic_function.png}
+% \caption{A computer can simulate waveforms by utilizing periodic functions. Digital waveforms are discrete approximations of analogue waves~\cite{mitchell2009basicsynthChap5} }
+% \end{figure*}
 
@@
 We defined 3 STFT transformation functions which we believe to capture important, unique attributes of percussive sounds (figure ~\ref{fig:stackspectrums}).
-Our transformations are GPU based, allowing their application in tandem to the training of the classifier or tuning of STFT transformation during hyper-paramter optimization (see Appendix~\ref{appendix:F}).
-
+Our transformations are GPU based, allowing their application in tandem to the training of the classifier or tuning of STFT transformation during hyper-paramter optimization (see Appendix~\ref{appendix:hyperparam}).
 \subsection{Ear Types}
 \label{classifiers}
+
 Two groups of classifiers are implemented: \emph{two phased ears} (TPEs) and \emph{Mixed Ear Models} (MEMs).
-TPEs combine different models specializing in ~\hypref{Decision.2} or ~\hypref{Decision.1} and trained only with our transformation functions.
+TPEs combine different models specializing in~\hypref{Decision.2} or~\hypref{Decision.1} and trained only with our transformation functions.
 MEMs are a proof of concept attempt at addressing the OSR problem by usage of autoencoded representation of sounds as features.
 MEMs are trained using highly compressed, automatically encoded representation of sounds and can give simultaneous answers to both questions.
-Model specifications for TPE and MEMs can be found in Appendix~\ref{appendix:C}.
+Model specifications and measurments for TPE and MEMs can be found in Appendix~\ref{appendix:C}.
 We speculate that the features used to represent sounds plays a much more important role in determining outcomes, particularly when working with relatively small datasets.
 
-The features used by MEMs are encodings extracted from the latent layer of an autoencoder trained with MixedDB.
+The features used by MEMs are encodings extracted from the latent layer of an autoencoder trained to encode and decode spectrogram representations of sound in MixedDB.
 To better understand the delineation potential of the encoded features, 64-dimensional latent representation of 20\% of MixedDB and 1000 Noise sounds were projected onto a 2 or 3-dimensional planes using t-SNE.
 Referring to~\hypref{Decision.1} and~\hypref{Decision.2}, we expect the drum sounds to be clustered together, with the majority of the synthetic noise sounds appearing away from these clusters.
-The projections confirmed that this is the case(see Appendix~\ref{appendix:E}).
+The projections confirmed that this is the case (see Appendix~\ref{appendix:E}).
 We are most interested in synthetic noise sounds which appear within or near these clusters.
@@
 These graphs allow interactions such as playing the samples(by hovering the cursor on-top) and movement of the scene camera.
-Manual inspections revealed a noticeable, positive correlation between distance and similarity of a synthetic sound to drum clusters.
+Manual inspections revealed a noticeable, positive correlation between a synthetic sound's distance and similarity of a synthetic sound to drum clusters.
 
 \section{Pipelines and Surveys}
-\label{gens}
 \label{surveys}
-With our virtual synthesizer and virtual ears in place, we build two pipelines, one using all TPE models and the other using our best MEM model.
-To assess the performance of each pipeline, we randomly create drum programs and generate and the corresponding signal.
-This signal is then fed through the ear model to determine if the signal is percussive.
-If so, a category is assigned to the sound.
-This sound and the corresponding synthesizer program are saved to hard-disk.
-Here we assess the success rate of two different pipelines by manual inspection of sounds it has categorized as drums, as well as the category of those drums.
-The authors of this work attempt their own categorization of a randomly selected subset of each pipeline's results.
-We cross reference the manual categorizations with the categories assigned by the virtual ear: Do we agree that the sounds are percussive?
-Do we agree with the drum group assigned to the percussive sounds?
-
- \section{Survey of Two-Phased Ear Performance}
-
+With our virtual synthesizer and virtual ears in place, we build two pipelines.
+We chose CNNLSTM-DVN for \hypref{Decision.1}, and FC-DVD,CNNLSTM-DVD and E/F for \hypref{Decision.2} to build the TPE pipeline.
+The MEM pipeline uses our best MEM, which simultaneously classifies sounds as drums and categorizes them.
+The TPE pipeline produces samples in the following categories: \enquote{snare}, \enquote{kick}, \enquote{hat}, \enquote{clap} and \enquote{other} (combination of rims, shakers and unusual percussive sounds).
+The MEM pipeline does not output the \enquote{other} category, yet the option is available to surveyors when categorizing sounds manually.
+The sounds and the corresponding synthesizer programs are saved to hard-disk.
+Here we assess the success rate of two different pipelines---and by extension, the virtual ears---by manual inspection of sounds categorized as drums, as well as the category of those drums.
+Both authors categorized a subset of the results without knowledge of the drum categorization outcomes.
+Additionally, each responder had the option of labeling samples as \enquote{bad} for samples that they deemed not percussive.
+The percentage of sounds labeled as \enquote{bad} by the authors is a measurement of success with regards to \hypref{Decision.1}.
+We measure success with regards to \hypref{Decision.2}---the reliability of agreement between persons and drum categorization models--- via the Fleiss' kappa coefficient \cite{fleiss1971measuring}.
+The value of 0 or less for this coefficient indicates no agreement beyond random chance, and the values of 1 indicates perfect agreement.
+We again measure this coefficient after dropping samples that were categorized as \enquote{bad} by one or both authors.
+We also show measurements after dropping all \enquote{bad} and \enquote{other} samples.
 \begin{table}[htbp]
- \resizebox{\linewidth}{!}{\begin{tabular}{||c c c c c c c||} 
+ \resizebox{\linewidth}{!}{\begin{tabular}{|c c c c c c c|} 
  \hline
- Drop Rule & Size & HvH & H+FC & H+CNN & H+ALL & 3 models \\ [0.5ex] 
+ Drop Rule & Size & H+H & H+FC & H+CNN & H+E/F & 3 models \\ [0.5ex] 
  \hline
@@
 \end{tabular}}
-\caption{\label{kappa_table_TPE}Table of Fleiss' kappa coefficient to measure the degree of agreement between persons (HvH), persons with FC model (H+FC), persons with CNNLSTM model, persons with all models (H+ALL), and between the 3 models.
+\caption{\label{kappa_table_TPE}Table of Fleiss' kappa coefficient to measure the degree of agreement between persons (H+H), persons with FC model (H+FC), persons with CNNLSTM model, persons with all models (H+E/F), and between the 3 models.
 \enquote{Drop Rule} column indicates if any samples were dropped.
@@
 \end{table}
-To measure the quality of the samples produced by our pipeline combined with the TP ear models, we run the model until an adequate number of samples in each category are saved to disk.
-Next, we randomly generated around 50 samples in the following categories: \enquote{snare}, \enquote{kick}, \enquote{hat}, \enquote{clap} and \enquote{other} (combination of rims,
-shakers and unusual percussive sounds).
-This gave us a total of 257 samples.
-These samples were determined to be percussive and then categorized by 4 different models (FC, CNNLSTM, E+F and AVG).
-We ensured a balanced division between samples of stack size 1, 2 and 4 (each stack is responsible for a third of the samples under each category).
-Both reviewers then categorized these samples without knowledge of other categorizations (person or computation models).
-Additionally, each responder had the option of labeling samples as \enquote{bad} for samples that they deemed not percussive.
-
-We assess the reliability of agreement between persons and categorization models via the Fleiss' kappa coefficient \cite{fleiss1971measuring}.
-The value of 0 or less for this coefficient indicates no agreement beyond random chance, and the value of 1 indicating perfect agreement.
-Our kappa measurements showcased in~\ref{kappa_table_TPE} lie within the 0.35-0.45 range, indicating mild to moderate agreement between persons and machines.
-We again measure this coefficient after dropping samples that were categorized as \enquote{bad} by the authors, as samples that persons deem to be \enquote{bad} indicate a failure in Phase 1 and should not have been categorized by the models at all.
-
-\section{Survey of Mixed-Models Ear Performance}
- Keeping the other components of the pipeline the same, we replace the two-phased ear in the previous pipeline with the MME.
-Our survey differs from the previous survey in that the pipeline only creates the four drum categories.
-Our main concern here is changes in the amount of \enquote{bad} samples.
-We show measurements before and after dropping all \enquote{bad} and \enquote{other} samples for a fairer comparison with the TPE pipeline.
 
@@
  \hline
- Drop Rule & Size & HvH & H+MME \\
+ Drop Rule & Size & H+H & H+H+MEM \\
  \hline
- No Drop & 300 & 0.336 & 0.250\\ 
+ No Drop & 300 & 0.34 & 0.25\\ 
  \hline
- Assigned Bad By Both & 249 & 0.200 & 0.260 \\
+ Assigned Bad By Both & 249 & 0.20 & 0.26 \\
  \hline
- Assigned Bad By Either & 151 & 0.460 &  0.473 \\
+ Assigned Bad By Either & 151 & 0.46 &  0.47 \\
  \hline
-Assigned \enquote{Bad} or \enquote{Other} By Either  & 120 & 0.620   &  0.587 \\
+Assigned \enquote{Bad} or \enquote{Other} By Either  & 120 & 0.62   &  0.59 \\
  \hline
 \end{tabular}}
-\caption{\label{kappa_table_MME}Table of Fleiss' kappa coefficient to measure the degree of agreement between persons (HvH) and persons and MME.
-We also measure the agreeability scores after dropping bad samples if both or either persons assigned the sample as such.
+\caption{\label{kappa_table_MEM}Table of Fleiss' kappa coefficient to measure the degree of agreement between persons (H+H) and persons with MEM (H+MEM).
+We also measure the agree-ability scores after dropping bad samples if both or either persons assigned the sample as such.
 We also measure agree-ability when all samples deemed \enquote{bad} or \enquote{other} by either person are removed.}
@@
 
-\subsection{Takeaways from These Surveys}
+\subsection{Survey Discussion}
 \label{survey2_takeaway}
-The results from the two surveys are not easily comparable.
-However, no major improvements in agree-ability or a decrease in the number of bad samples can be seen, in fact, the opposite is more likely to be true.
-However, we are yielding comparable results to the TPE pipeline despite having a fraction of the features to learn from (latent layer + 10 envelope features).
-This shows that latent layers of an autoencoder network can be used as a low-dimensional proxy for representation of more complex inputs, despite the autoencoder not being trained for such a task.
-Agree-ability scores for MME pipeline are often lower, but we reiterate that this can be caused by having two out of six (rather than one out of six in the TPE pipeline) categories which are exclusive to survey responders.
+Due to the discrepancy in categorization and output groups, results from the two surveys must be compared with caution.
+Agree-ability scores for MEM pipeline are often lower, but we reiterate that the MEM survey has two out of six (rather than one out of six in the TPE pipeline) categories which are exclusive to survey responders.
 Supporting this hypothesis is the notable improvement in agree-ability observed after dropping all \enquote{bad} and \enquote{other} samples.
-Here, both persons agree with each other and with the MME at a stronger rate than in the TPE pipeline, despite having similar number of samples (120 for MME and 154 for TPE) and equal number of categories to choose from.
-This values are observed in the last rows of tables~\ref{kappa_table_TPE} and ~\ref{kappa_table_MME}.
-The higher DVD categorization accuracy achieved by the mixed-model ear compared to the best two-phaased ear is consistent with this observation: Given that the sound being categorized is a drum, the MME will yield better results that the TPE.
-However, the MME pipeline does not yield better results in the DVN task.
-\begin{itemize}
-    \item The survey brings into question the reliability of our phase 1 models, as 30\% of the generated samples were deemed not percussive by at least 1 reviewer and 8\% by both reviewers
-    \item The task of categorizing synthetic drums is difficult.
-Survey shows that the scale of agreement within persons as well as between persons and various model combinations is moderate at best, even after removal of \enquote{bad} samples.
-While the same models can easily achieve 98+ percent accuracy when tested on sounds from physical drum samples.
-    \item While there is much room for improvement, our pipelines can generate and categorize drums and percussive sounds with a promising degree of success. 
-\end{itemize}
+Despite the drawbacks, the results here are encouraging as the MEM pipeline remains competitive despite working with a fraction of the features to learn from and simultaneously making both decisions.
+Suggesting that latent representations of autoencoder networks can be used as general, low-dimensional proxies for representation of complex inputs.
+
 \bibliographystyle{apacite}
 \bibliography{CSMC_MUME_LaTeX_Template.bib}
-
 \begin{appendices}
@@
 Its structure is the combination of a CNN with 2 output channels and kernel size $(7,3)$; Followed by an LSTM model of hidden size 800 and a fully connected layer of size 20x2.
-\item E+F-DVD: A fully connected model trained on a concatenation of envelope and frequency features. Reaching 80\% accuracy for 6-way drum categorization in Phase 2. Size of 50x10x2x6.
+\item E/F-DVD: A fully connected model trained on a concatenation of envelope and frequency features. Reaching 80\% accuracy for 6-way drum categorization in Phase 2. Size of 50x10x2x6.
 \item CNN-DVD: A CNN model trained on Spectrum features.
@@
 \chapter{AutoEncoder Structures and Hyper-Parameter Optimization}
+\label{appendix:hyperparam}
 % could do multi-objective pareto front stuff too
@@
 \\
+\begin{table}[htbp]
 
+\begin{tabular}{|p{28mm}|p{50mm}|p{21mm}|p{21mm}|}
+\hline
+Hyper-Param. & Description  & Values & Distribution\\ \hline
+Model Type      &   Affects encoder's first hidden layer & CNN,FC & Categorical \\  \hline
+Optimizer       & Updates network's weights based on loss & Adam,SGD & Categorical  \\  \hline
+Hidden Layers   & Extra hidden layer for the Encoder & True,False & Categorical \\  \hline
+Time Steps & Temporal granularity of the spectrogram. Affects FFT windowing. & 10,20 & Categorical  \\ \hline
+Learning Rate   &    Optimizer's learning rate  & $1^{-4}$ ... $1^{-1}$ & Uniform      \\ \hline
+Frequency Bins & Number of spectrogram frequency bins & 10, 30,60 & Categorical \\ \hline
+
+Regularization  &  L2 regularization parameter. Penalizes large weights to prevent overfitting & 1^{-6}~...~1^{-1} & Uniform\\ \hline
+Latent Size & Size of bottle neck layer or number encoded features & 8,16,64 & Categorical              \\ \hline
+Dropout Rate & Random zeroing of activations between layers to prevent over-fitting & 0,0.5,0.1 & Categorical\\  \hline
+\end{tabular}
+\caption{The Hyper-Paramter space in which the optimization was conducted.}
+\label{table:hyper_params}
+\end{table}
 \begin{table}
@@
 
-\begin{figure}[htbp]
-\centering
-\textbf{Loss Value per Epoch for Top 10 Trials}
-\includegraphics[width=12cm,height=6.5cm]{images/loss_per_training.pdf}
-\caption{Loss value per epoch for top 10 trials.
-Some of the initial 500 trials appear in this list, despite having half the number of epoch steps.
-The learning curves tend to flatten quickly.
-Therefore, 20 epoch steps may be a reasonable number for measuring hyper-parameter viability.
-}
-\label{chap3:top10}
-\end{figure}
-
 \begin{figure}
@@
 Optimizer       & Adam  \\ \hline
-Hidden Layers   & -  \\\hline
+Hidden Layers   & Not Applicable  \\\hline
 Learning Rate   &  0.001145\\ \hline
@@
 \chapter{Embedded Feature Visualization}
+Live demos provided in project source code.
 \label{appendix:E}
@@
 
+%==============
+\chapter{Survey Details}
+\label{appendix:surveys}
+\subsubsection{TPE Survey of 257 Samples:}
+\begin{itemize}
+    \item With 6 categorization groups, responders had the same categorization in 47\% of cases.
+    \item The agreement between the responders and AVG was 44\% and 47\%.
+    \item Of 257 samples, the responders agreed with FC, CNNLSTM and E/F respectively in 78, 76, and 46 of cases.
+The loss of spectrum data is likely the cause of E/F model's noticeably worse performance.
+    \item The survey brings into question the reliability of our phase 1 model, as 30\% of the generated samples were deemed not percussive by at least 1 reviewer and 8\% by both reviewers
+    \item The task of categorizing synthetic drums is difficult.
+Survey shows that the scale of agreement within persons as well as between persons and various model combinations is moderate at best, even after removal of \enquote{bad} samples.
+While the same models can easily achieve 98+ percent accuracy when tested on sounds from physical drum samples.
+    \item While there is much room for improvement, our pipelines can generate and categorize drums and percussive sounds with a promising degree of success. 
+\end{itemize}
+
+\begin{figure}[h!]
+    \begin{center}
+    \textbf{Category Assignment Frequency For TPE Survey}
+    \makebox[\textwidth]{
+    \includegraphics[width=1.1\linewidth]{images/cat_2p.pdf}}
+    \end{center}
+    \caption{Frequency of assigned labels by persons vs the true number of labels}
+\label{fig:freq-survey-2p}
+\end{figure}
+
+\subsubsection{MEM Survey of 300 Samples:}
+
+\begin{figure}[htpb]
+    \begin{center}
+    \textbf{Category Assignment Frequency For MEM Survey}
+    \makebox[\textwidth]{
+    \includegraphics[width=1.1\linewidth]{images/cat_MME.pdf}}
+    \end{center}
+    \caption{Frequency of assigned labels by persons vs the true number of labels}
+\label{fig:freq-survey-2p}
+\end{figure}
+
 \end{appendices}

### 2020-08-20 templates_aimusic2020/paper.tex
Updates from Overleaf

@@
 Almost any object which is struck to produce noise can be referred to as a drum~\cite{latham2002oxford}.
-Kicks and snares are two of the most universally recognized examples of percussion~\cite{barry2005drum}.
-The term \enquote{Percussion} often encompasses all drums and may include the additional instruments which may be rubbed, plucked, blown, etc; A more strict definition of percussion can be used interchangeably with drums~\cite{latham2002oxford}.
-We adapt this strict definition for this work as our concern is not the delineation between the two overlapping concepts, but with extraction and creation of novel sounds with characteristics shared between the two.
-As a result, we often use the terms \enquote{drum} and \enquote{percussion} interchangeably.
+Under strict definitions, the terms can be used interchangeably~\cite{latham2002oxford}.
+We adapt this strict definition as our work is not concerned the delineation between the two overlapping concepts, but with creation of synthetic sounds which can be used by digital sound artists as replacements for organic drums or percussion.
+In this work, the terms \enquote{drum} and \enquote{percussion} are often interchangeable.
 
 \subsection{Motivation and Goals}
-Digital recordings of novel, one-shot\footnote{A single hit on the drum that captures its capabilities} drum sounds are not easy or cheap to find.
-Our goal here is to create a new, virtual source of novel drum sounds, which could then be used in electronic music compositions.
-By relying on recordings of \textit{real life} drum sounds, we are limited by what instruments exist in the real world and whether or not we have access to clean, one-shot recordings.
-Our hypothesis is that the virtualization of sound generation can alleviate these material limitations.
+Digital recordings of novel, one-shot\footnote{A single hit on the drum that captures its capabilities} drum sounds are commonly used in  electronic music compositions.
+Yet unique drum sounds are not easy or cheap to find.
+By relying on recordings of \textit{real life} drum sounds, artitsts are limited by what instruments exist in the real world and whether or not high-quality, one-shot recordings can be accessed.
+Virtual sources of novel drum sounds can alleviate these material limitations.
 
- \begin{figure}[t!]
+ \begin{figure}
     \begin{center}
@@
     \end{center}
-    \caption{A blueprint of our desired pipeline which allows each component to be implemented in a number of ways. Our implementations of this pipeline allow for easy parallelization when needed. 
+    \caption{A blueprint of our desired pipeline which allows each component to be implemented in a number of ways.
+Our implementations of this pipeline allow for easy parallelization when needed.
+This implementation also allows for easy integration of heuristic search for future works.
     }
@@
 \subsection{Related Works}
+
+Numerous deep, neural network models have been proposed and utilized for the purpose of signal generation in recent years.
+WaveGans and WaveNet have been subject to significant improvements and experiments since their proposal~\cite{nsynth2017,yamamoto2020parallel,oord2017parallel}.
+Particularly relevant are the utilization of variational autoencoders (VAE's) for generation of percussive samples~\cite{aouameur2019neural} and generation of percussive sounds by decoding a small set of latent features~\cite{ramires2020neural}.
+Automatic programming of virtual synthesizers has long been a topic of interest.
+In early 2000s, Interactive Genetic Algorithms (IGA's) were utilized for the generation of new sounds with various sound-engines~\cite{johnson1999exploring,dahlstedt2001creating}.
+More recent work by Yee-King et al.~\cite{yee2018automatic} used Long short-Term Memory (LSTM) models and genetic algorithms to find the exact parameters used to create a group of sounds.
+The sounds approximated were made by the same virtual synthesizer, not an external source; making the eventual replication certain even with random search.
+Since this work appears more focused on pads and textures rather than drums, feature matching appears to not be concerned with the envelope of the sounds but rather the frequency content within arbitrary time windows.
+Yet another recent work by Esling et al.
+used a large dataset of over 10,000 presets for a coMEMrcial VST synthesizer to learn a latent parameter space which can be sampled for creation of new audio~\cite{esling2019universal}.
+As stated before, our work explores the rapid approximation of percussion sounds with no previous knowledge about the sonic capabilities of our virtual synthesizer, exploring the actual parameter space rather than its latent representation.
 \label{related_works}
 \begin{center}
-\begin{table}[h]
+\begin{table}
 \resizebox{\linewidth}{!}{\begin{tabular}{|c c c c|} 
@@
 \end{center}
-Numerous deep, neural network models have been proposed and utilized for the purpose of signal generation in recent years.
-WaveGans and WaveNet have been subject to significant improvements and experiments since their proposal~\cite{nsynth2017,yamamoto2020parallel,oord2017parallel}.
-Particularly relevant are the utilization of variational autoencoders (VAE's) for generation of percussive samples~\cite{aouameur2019neural} and generation of percussive sounds by decoding a small set of latent features~\cite{ramires2020neural}.
-Automatic programming of virtual synthesizers has long been a topic of interest.
-In early 2000s, Interactive Genetic Algorithms (IGA's) were utilized for the generation of new sounds with various sound-engines~\cite{johnson1999exploring,dahlstedt2001creating}.
-More recent work by Yee-King et al.~\cite{yee2018automatic} used Long short-Term Memory (LSTM) models and genetic algorithms to find the exact parameters used to create a group of sounds.
-The sounds approximated were made by the same virtual synthesizer, not an external source; making the eventual replication certain even with random search.
-Since this work appears more focused on pads and textures rather than drums, feature matching appears to not be concerned with the envelope of the sounds but rather the frequency content within arbitrary time windows.
-Yet another recent work by Esling et al.
-used a large dataset of over 10,000 presets for a coMEMrcial VST synthesizer to learn a latent parameter space which can be sampled for creation of new audio~\cite{esling2019universal}.
-As stated before, our work explores the rapid approximation of percussion sounds with no previous knowledge about the sonic capabilities of our virtual synthesizer, exploring the actual parameter space rather than its latent representation.
-
 \subsection{Our Approach}
@@
 \label{surveys}
+\begin{table}
+ \begin{tabular}{|c c c c c c c|} 
+ \hline
+ Drop Rule & Size & H+H & H+FC & H+CNN & H+E/F & 3 models \\ [0.5ex] 
+ \hline
+ No Drops & 257 &0.37 & 0.35 & 0.36 & 0.36 & 0.28\\ 
+ \hline
+ Assigned \enquote{Bad} By Both & 236 & 0.31 & 0.37 & 0.37 & 0.38 & 0.30 \\
+ \hline
+ Assigned \enquote{Bad} By Either & 180 & 0.47 & 0.50 & 0.48 & 0.48 &  0.34 \\
+ \hline
+ Assigned \enquote{Bad} or \enquote{Other} By Either & 154 & 0.47 & 0.59 & 0.54 & 0.50 &  0.35 \\
+ \hline
+\end{tabular}
+\caption{\label{kappa_table_TPE}Table of Fleiss' kappa coefficient to measure the degree of agreement between persons (H+H), persons with FC model (H+FC), persons with CNNLSTM model, persons with all models (H+E/F), and between the 3 models.
+}
+\end{table}
+
+ \begin{table}
+ \resizebox{\linewidth}{!}{\begin{tabular}{||c c c c||} 
+ \hline
+ Drop Rule & Size & H+H & H+H+MEM \\
+ \hline
+ No Drop & 300 & 0.34 & 0.25\\ 
+ \hline
+ Assigned Bad By Both & 249 & 0.20 & 0.26 \\
+ \hline
+ Assigned Bad By Either & 151 & 0.46 &  0.47 \\
+ \hline
+Assigned \enquote{Bad} or \enquote{Other} By Either  & 120 & 0.62   &  0.59 \\
+ \hline
+\end{tabular}}
+\caption{\label{kappa_table_MEM}Table of Fleiss' kappa coefficient to measure the degree of agreement between persons (H+H) and persons with MEM (H+MEM).}
+\end{table}
 With our virtual synthesizer and virtual ears in place, we build two pipelines.
@@
 We also show measurements after dropping all \enquote{bad} and \enquote{other} samples.
-\begin{table}[htbp]
- \resizebox{\linewidth}{!}{\begin{tabular}{|c c c c c c c|} 
- \hline
- Drop Rule & Size & H+H & H+FC & H+CNN & H+E/F & 3 models \\ [0.5ex] 
- \hline
- No Drops & 257 &0.37 & 0.35 & 0.36 & 0.36 & 0.28\\ 
- \hline
- Assigned \enquote{Bad} By Both & 236 & 0.31 & 0.37 & 0.37 & 0.38 & 0.30 \\
- \hline
- Assigned \enquote{Bad} By Either & 180 & 0.47 & 0.50 & 0.48 & 0.48 &  0.34 \\
- \hline
- Assigned \enquote{Bad} or \enquote{Other} By Either & 154 & 0.47 & 0.59 & 0.54 & 0.50 &  0.35 \\
- \hline
-\end{tabular}}
-\caption{\label{kappa_table_TPE}Table of Fleiss' kappa coefficient to measure the degree of agreement between persons (H+H), persons with FC model (H+FC), persons with CNNLSTM model, persons with all models (H+E/F), and between the 3 models.
-\enquote{Drop Rule} column indicates if any samples were dropped.
-We show the measurements after dropping samples if they are deemed bad by either or both responders.
-We also show measurements after dropping the \enquote{other} category along with samples deemed bad by either responder.
-}
-\end{table}
-
- \begin{table}[t]
- \resizebox{\linewidth}{!}{\begin{tabular}{||c c c c||} 
- \hline
- Drop Rule & Size & H+H & H+H+MEM \\
- \hline
- No Drop & 300 & 0.34 & 0.25\\ 
- \hline
- Assigned Bad By Both & 249 & 0.20 & 0.26 \\
- \hline
- Assigned Bad By Either & 151 & 0.46 &  0.47 \\
- \hline
-Assigned \enquote{Bad} or \enquote{Other} By Either  & 120 & 0.62   &  0.59 \\
- \hline
-\end{tabular}}
-\caption{\label{kappa_table_MEM}Table of Fleiss' kappa coefficient to measure the degree of agreement between persons (H+H) and persons with MEM (H+MEM).
-We also measure the agree-ability scores after dropping bad samples if both or either persons assigned the sample as such.
-We also measure agree-ability when all samples deemed \enquote{bad} or \enquote{other} by either person are removed.}
-\end{table}
 
@@
 \bibliography{CSMC_MUME_LaTeX_Template.bib}
+
 \begin{appendices}

### 2020-08-20 templates_aimusic2020/paper.tex
Updates from Overleaf

@@
 Yet unique drum sounds are not easy or cheap to find.
-By relying on recordings of \textit{real life} drum sounds, artitsts are limited by what instruments exist in the real world and whether or not high-quality, one-shot recordings can be accessed.
-Virtual sources of novel drum sounds can alleviate these material limitations.
+By relying on recordings of \textit{real life} drum sounds, artists are limited by what instruments exist in the real world and whether or not high-quality, one-shot recordings can be accessed.
+Virtual Studio Technology (VST)~\cite{tanev2013virtual} and other DSP based software have given artists unprecedented access to complex audio synthesizers.
+Utilization of virtual synthesizers for creation of novel drum sounds can alleviate these material limitations.
 
@@
 Yet another recent work by Esling et al.
-used a large dataset of over 10,000 presets for a coMEMrcial VST synthesizer to learn a latent parameter space which can be sampled for creation of new audio~\cite{esling2019universal}.
-As stated before, our work explores the rapid approximation of percussion sounds with no previous knowledge about the sonic capabilities of our virtual synthesizer, exploring the actual parameter space rather than its latent representation.
+used a large dataset of over 10,000 presets for a commercial VST synthesizer to learn a latent parameter space which can be sampled for creation of new audio~\cite{esling2019universal}.
+
 \label{related_works}
+\begin{table}[t!]
 \begin{center}
-\begin{table}
-\resizebox{\linewidth}{!}{\begin{tabular}{|c c c c|} 
+\begin{tabular}{|c c c c|} 
 \hline
-Work & Feature extraction & Synthesis & Specilization & \hline
-Oord 2017 & CNN & CNN &Speech& \hline
-Yee-King 2018 & LSTM on Paremters & DSP & Synth Pads & \hline
-Aouameur 2019 & Latent layer& Decoding of Latent Layers & Percussion & \hline
-Ramires 2020 & Latent layer & FeedForward Network & Percussion & \hline
-Yamamoto 2020 & GAN & GAN & Speech & \hline
-\end{tabular}}
+Work & Feature extraction & Synthesis & Specilization \\ \hline
+Oord 2017 & CNN & CNN & Speech \\  \hline
+Yee-King 2018 & LSTM on Paremters & DSP & Synth Pads \\  \hline
+Aouameur 2019 & Latent layer& Decoding of Latent Layers & Percussion \\  \hline
+Ramires 2020 & Latent layer & FeedForward Network & Percussion \\  \hline
+Yamamoto 2020 & GAN & GAN & Speech \\  \hline
+\end{tabular}
 \caption{Quick reference of recent related works}
-\end{table}
 \label{table:recent_works}
 \end{center}
+\end{table}
 \subsection{Our Approach}
+We explore the approximation of percussive sounds with no previous knowledge about the sonic capabilities of a virtual synthesizer.
 To virtually create novel drum sounds, we need a tractable, generative source of audio; One that deterministically produces audio based on a set of instructions.
 Additionally, we need a method of evaluation to help us determine which sounds resemble drums and are worth keeping.
-To enable heuristic search, we would like to know what instructions caused our audio source to make the sounds we liked.
-Given these two components capable of \textit{generation} and \textit{evaluation} of sounds, we build a generative pipeline of audio as depicted in figure~\ref{fig:pipeline_outline}.
+To enable heuristic search in future works, we would like to know what instructions caused our audio source to make the sounds we liked.
+Given components capable of \textit{generation} and \textit{evaluation} of sounds, we build a generative pipeline of audio as depicted in figure~\ref{fig:pipeline_outline}.
 The success of this pipeline is dependent on the characteristics of the components responsible for the generation and evaluation of the sounds.
@@
 
-Sound is product of physical disturbances, causing vibrations in our mediums.
-Vibrations are perpetuated through air as part of an expanding, spherical front ~\cite{cook1999chap4}.
+Sound is our experience of physical disturbances, causing vibrations in our mediums ~\cite{cook1999chap4}.
 A sound wave can be viewed as the result of a function which governs amplitude through time, where time and amplitude exist in continuous dimensions.
-Waves can be approximated via a series of samples, associating time steps to a discrete range of amplitude values.~\textit{Digital synthesis} of audio is the process of creating these discrete values.
-Unlike the majority of the works mentioned in Section~\ref{related_works}, we do not employ probabilistic models for the synthesizer component. Our decision is based on the following factors:
+Waves can be approximated via a series of samples, associating time steps to a discrete range of amplitude values.
+\textit{Digital synthesis} of audio is the process of creating these discrete values.
+Unlike the majority of the works mentioned in Section~\ref{related_works}, we do not employ probabilistic models for the synthesizer component.
+Our decision is based on the following factors:
 \begin{itemize}
     \item \textit{Novelty and Creativity}: Given large sets of examples, generative models such as VAEs and GANS have proven capable of generating samples similar to the exemplars.
-In this work, we are not aiming for perfect imitations; Following Boden's definition of exploratory creativity as an emergent property of generative work within confined rule sets~\cite{boden2009computer}, we work within the limitations of any tractable sound source to create its  approximations of a given sound category.
-Within the music realm, prominent instance of exploratory creativity is the persistent aesthetics of 8-bit soundtracks, remaining popular long after the original constraints are lifted~\cite{collins2007loop}.
+In this work, we are not aiming for perfect imitations.
+We seek to create \emph{novel sounds} by via artifical, exploratory creativity.
+Boden defines this concept as an emergent property of generative work within confined rule sets~\cite{boden2009computer}.
+Ultimately, we wish to work within the limitations of any tractable sound source to create its approximations of a given sound category.
+Within the music realm, a prominent instance of exploratory creativity is the persistent aesthetics of 8-bit soundtracks, remaining popular long after the original constraints are lifted~\cite{collins2007loop}.
     \item \textit{Interpretability}: Neural networks are often described as black boxes~\cite{basheer2000artificial}.
@@
 However, a significant number of untrained human ears can detect a change in quality of audio between sampling rates of 192 khz and the industry standard of 44.1 khz \cite{reiss2016meta}.
-In this work, we fix our sampling rate to the 48 khz standard.
+In this work, we fix our sampling rate 48 khz.
 \end{itemize}
-
-% \begin{figure*}[htbp]
-% \label{fig_example_sine}
-% \centering
-% \includegraphics[width=0.3\linewidth,angle =-90 ]{images/periodic_function.png}
-% \caption{A computer can simulate waveforms by utilizing periodic functions. Digital waveforms are discrete approximations of analogue waves~\cite{mitchell2009basicsynthChap5} }
-% \end{figure*}
 
@@
 This generative system is called an \textit{oscillator}.
-The combination and modification of oscillators are the building blocks of digital signal processing (DSP).
-Most sounds from the natural environment, and its flora and fauna are more complex than the output of a single oscillator.
-However, with careful programming, DSP techniques can be used to replicate almost any sound, which is why they have powered coMEMrcial digital synthesizers for over half a century ~\cite{jenkins2019analog}.
-Another advantage to using DSP for sound generation is that the synthesizers we build using these functions are tractable: the output is determined by the input and reproducible.
-This makes the evaluation of a set of inputs (or parameters) to our synthesizers  simpler compared to the evaluation of synthesizers that utilize probabilistic models.
+With careful programming, DSP techniques can be used to replicate almost any sound, which is why they have powered commercial digital synthesizers for over half a century ~\cite{jenkins2019analog}.
+Synthesizers we build using these functions are tractable and explainable: the output is determined by the input and reproducible.
+This makes the evaluation of a set of inputs (or parameters) to our synthesizers relatively simple.
 
-We opted for a set of classical DSP methods to build our synthesizer.
-For our project, we used the python based Pippi library for sound generation\footnote{https://github.com/luvsound/pippi}.
-This library uses a C back-end\footnote{https://github.com/PaulBatchelor/Soundpipe} and focuses on fast offline generation of audio signals.
+We opted for a set of classical DSP methods to build our synthesizer, which allow for fast offline generation of audio signals.
+We made extensive use of Pippi\footnote{https://github.com/luvsound/pippi} and SciPy~\cite{jones2001scipy} libraries.
 Our virtual synthesizer contains a set of one or more submodules.
@@
 
-\begin{figure}[htbp!]
+\begin{figure}[htbp]
     \begin{center}

### 2020-08-20 templates_aimusic2020/paper.tex
Updates from Overleaf

@@
 
-We opted for a set of classical DSP methods to build our synthesizer, which allow for fast offline generation of audio signals.
+We opted for a set of classical DSP methods to build our synthesizer, which allow for quick offline, and parallel generation of audio signals without the usage of GPUs.
 We made extensive use of Pippi\footnote{https://github.com/luvsound/pippi} and SciPy~\cite{jones2001scipy} libraries.
@@
 The task assigned to the virtual ear is the rare acceptance of drum-like sounds and the inevitable rejection of most \enquote{noise} outputs from the virtual synthesizer.
-By definition, we cannot anticipate what these novel drums will sound like.
-Without manual inspection, all we know is that the accepted sounds are synthesizer noises which the synthetic ear has determined to be similar to drum-sounds.
 The virtual ear makes two critical decisions:
@@
 The performance of the ear is measured by its precision and recall in finding the overlap between $\mathcal{H}$ and $\mathcal{N}$.
-It is important to ensure that the change in learning domains ---particularly with the case of positive examples of percussive sounds--- does not interfere with transformation of knowledge from the training of the ear to the hearing test.
+It is important to ensure that the change in learning domains---particularly with the case of positive examples of percussive sounds---does not interfere with transformation of knowledge from the training of the ear to the hearing test.
 To maximize the transference of knowledge from one domain to another, we seek to learn from agnostic feature sets that capture fundamental characteristics of the data points.
@@
 Supporting this hypothesis is the notable improvement in agree-ability observed after dropping all \enquote{bad} and \enquote{other} samples.
-Despite the drawbacks, the results here are encouraging as the MEM pipeline remains competitive despite working with a fraction of the features to learn from and simultaneously making both decisions.
+Despite the drawbacks, the MEM pipeline remains competitive while working with a fraction of the features to learn from and simultaneously making both decisions.
 Suggesting that latent representations of autoencoder networks can be used as general, low-dimensional proxies for representation of complex inputs.
-
 \bibliographystyle{apacite}

### 2020-08-21 templates_aimusic2020/paper.tex
Updates from Overleaf

@@
 % unless you accept that it will be published
-\institute{Department of Computing Science\\ University of Alberta \\ \email{asalimi@ualberta.ca}}
+\institute{Department of Computing Science\\ University of Alberta \\ \email{asalimi@ualberta.ca\\ }}
 
@@
 \maketitle
-% For more than two decades research involving digital synthesis, heuristic search, and neural networks has been used for the generation of novel sounds.
+
 \begin{abstract}
-This work is a proof of concept in automatic programming of synthesizers towards their best approximation of drum sounds.
-Our approach is based on the combination of two central components: \begin {enumerate*} [label=(\roman*)] \item a \emph{virtual ear} capable of evaluating the proximity of \enquote{unusual} sounds to drum sounds and \item a dynamic \emph{virtual synthesizer} with a rich set of tractable parameters\end{enumerate*}.
-We present a modular design of a generative pipeline which utilizes (semi-)supervised learning and classical digital signal processing for the generation of one-shot percussive sounds.
-We present our findings and measurements of a number of approaches taken, particularly in regard to the implementation of an effective virtual ear.
-Advantages, shortcomings and practicality of the employed methodologies are demonstrated and discussed.
-We share a number of datasets, notably our curated dataset of free percussive sounds.
-
+Can we generate drum synthesizers automatically?
+We present an approach for the automatic generation of synthesizer programs for one-shot percussive sounds. 
+Recent advancements in digital synthesis, heuristic search, and neural networks can be utilized for sound generation. 
+Yet the need for data, the problem of open set recognition, and high computational costs persist as barriers towards the expansion of sound libraries using these techniques. 
+We generate quick, scalable, percussion synthesizers using classical signal processing. 
+We train drum classifiers to find and classify synthesizer programs that mimic percussive sounds. 
+We use features from Fourier transformations and autoencoder embeddings to train machine learning classifiers.
+Manual listening tests of the generated sounds demonstrates the system can successfully generate drum synthesizers and categorize drum sounds.
+To facilitate future research, we share our curated dataset of free percussive sounds.
 \keywords{Automatic Synthesizer design. Machine Listening. Sound Analysis. Novelty and Originality}
@@
 
-\section{Preamble}
-\subsection{Drums and Percussion}
-Drums are a subcategory of percussive instruments.
-Almost any object which is struck to produce noise can be referred to as a drum~\cite{latham2002oxford}.
-Under strict definitions, the terms can be used interchangeably~\cite{latham2002oxford}.
-We adapt this strict definition as our work is not concerned the delineation between the two overlapping concepts, but with creation of synthetic sounds which can be used by digital sound artists as replacements for organic drums or percussion.
-In this work, the terms \enquote{drum} and \enquote{percussion} are often interchangeable.
+\section{Introduction} 
+Digital recordings of novel, one-shot\footnote{A single hit on the drum that captures its capabilities} drum sounds are commonly used in  electronic music compositions.
+Yet unique drum sounds can be difficult or expensive to find.
+By relying on recordings of \textit{real life} drum sounds, artists are limited by what instruments exist in the real world and whether or not high-quality, one-shot recordings can be accessed.
+We believe automatic programming of virtual synthesizers for the creation of novel drum sounds can alleviate these material limitations.
+To this end, we implement a programmable virtual synthesizer of audio, which we call the \emph{virtual synthesizer}.
+We also implement machine learning classifiers for automatic separation of percussive sounds from non-percussive sounds.
+To effectively train the classifiers with small datasets, we simplify the representation of audio data by experimenting with fast Fourier transform (FFT) features and autoencoder embeddings.
+We call our system of feature extraction and classification of sounds the \emph{virtual ear}.
+To create a dataset of synthetic drums, the virtual synthesizer produces random programs and generates the corresponding audio.
+This audio is then categorized by the virtual ear.
+We save not just the desirable sounds, but also the programs which generated these sounds.
+These programs can be modified and experimented on by sound designers, or used for an improved search algorithm in future works.
+We build generative systems using different implementations of the virtual ear, and conduct manual hearing tests of the generated sounds.
+Our results are promising as the majority of sounds generated from our systems are deemed percussive by human listeners.
+However, we cannot quantify the novelty of these sounds.
 
-\subsection{Motivation and Goals}
-Digital recordings of novel, one-shot\footnote{A single hit on the drum that captures its capabilities} drum sounds are commonly used in  electronic music compositions.
-Yet unique drum sounds are not easy or cheap to find.
-By relying on recordings of \textit{real life} drum sounds, artists are limited by what instruments exist in the real world and whether or not high-quality, one-shot recordings can be accessed.
-Virtual Studio Technology (VST)~\cite{tanev2013virtual} and other DSP based software have given artists unprecedented access to complex audio synthesizers.
-Utilization of virtual synthesizers for creation of novel drum sounds can alleviate these material limitations.
-
- \begin{figure}
+ \begin{figure}[t]
     \begin{center}
-    \textbf{Pipeline Design}
+    \textbf{Generative System}
     \makebox[\textwidth]{
@@
     \end{center}
-    \caption{A blueprint of our desired pipeline which allows each component to be implemented in a number of ways.
+    \caption{A blueprint of our system which allows each component to be implemented in a number of ways.
 Our implementations of this pipeline allow for easy parallelization when needed.
@@
 
-\subsection{Related Works}
-
-Numerous deep, neural network models have been proposed and utilized for the purpose of signal generation in recent years.
+\section{Related Works}
+Numerous deep neural network models have been proposed for the purpose of signal generation in recent years.
 WaveGans and WaveNet have been subject to significant improvements and experiments since their proposal~\cite{nsynth2017,yamamoto2020parallel,oord2017parallel}.
-Particularly relevant are the utilization of variational autoencoders (VAE's) for generation of percussive samples~\cite{aouameur2019neural} and generation of percussive sounds by decoding a small set of latent features~\cite{ramires2020neural}.
+Particularly relevant works are the utilization of variational autoencoders (VAE's) for generation of percussive samples~\cite{aouameur2019neural} and generation of percussive sounds by decoding a small set of latent features~\cite{ramires2020neural}.
 Automatic programming of virtual synthesizers has long been a topic of interest.
@@
 More recent work by Yee-King et al.~\cite{yee2018automatic} used Long short-Term Memory (LSTM) models and genetic algorithms to find the exact parameters used to create a group of sounds.
-The sounds approximated were made by the same virtual synthesizer, not an external source; making the eventual replication certain even with random search.
-Since this work appears more focused on pads and textures rather than drums, feature matching appears to not be concerned with the envelope of the sounds but rather the frequency content within arbitrary time windows.
+The sounds approximated were made by the same virtual synthesizer and not with an external source, making the eventual replication certain even with random search.
 Yet another recent work by Esling et al.
 used a large dataset of over 10,000 presets for a commercial VST synthesizer to learn a latent parameter space which can be sampled for creation of new audio~\cite{esling2019universal}.
-
-\label{related_works}
-\begin{table}[t!]
-\begin{center}
-\begin{tabular}{|c c c c|} 
-\hline
-Work & Feature extraction & Synthesis & Specilization \\ \hline
-Oord 2017 & CNN & CNN & Speech \\  \hline
-Yee-King 2018 & LSTM on Paremters & DSP & Synth Pads \\  \hline
-Aouameur 2019 & Latent layer& Decoding of Latent Layers & Percussion \\  \hline
-Ramires 2020 & Latent layer & FeedForward Network & Percussion \\  \hline
-Yamamoto 2020 & GAN & GAN & Speech \\  \hline
-\end{tabular}
-\caption{Quick reference of recent related works}
-\label{table:recent_works}
-\end{center}
-\end{table}
-\subsection{Our Approach}
-We explore the approximation of percussive sounds with no previous knowledge about the sonic capabilities of a virtual synthesizer.
-To virtually create novel drum sounds, we need a tractable, generative source of audio; One that deterministically produces audio based on a set of instructions.
-Additionally, we need a method of evaluation to help us determine which sounds resemble drums and are worth keeping.
-To enable heuristic search in future works, we would like to know what instructions caused our audio source to make the sounds we liked.
-Given components capable of \textit{generation} and \textit{evaluation} of sounds, we build a generative pipeline of audio as depicted in figure~\ref{fig:pipeline_outline}.
-The success of this pipeline is dependent on the characteristics of the components responsible for the generation and evaluation of the sounds.
-We call these two components the \emph{virtual synthesizer} and \emph{virtual ear} respectively.
+Here, we work towards the approximation of percussive sounds with no previous knowledge about the sonic capabilities of a virtual synthesizer.
 
@@
 \centering
-\resizebox{\columnwidth}{!}{\begin{tabular}{ |c|c|c| } 
+\resizebox{\columnwidth}{!}{\begin{tabular}{ |p{4cm}|p{4cm}|p{4cm}| } 
 \hline
@@
 Release & 0-3 & relative to A-D-S\\
-OSC type & sine,square,saw & tone type\\
-IsNoise & boolean & whether to \newline use OSC type to generate noise\\
+OSC type & sine,square,saw & -\\
+IsNoise & boolean & generate noise using \newline cloud of waveform\\
 Length & 0-1 second & - \\
@@
 \caption{Synthesizer submodule Parameters.
-Despite the simplicity of the parameters and our efforts at constraining the ranges, the number of parameters that can be randomly chosen for each submodule is in the order of $10^{15}$ }
+Despite the simplicity of the parameters and our efforts at constraining the ranges, the number of parameters that can be randomly chosen for each submodule is over $10^{15}$.
+Each synthesizer can contain any number of submodules }
 \label{table:submodule_params}
 \end{table}
-
-Sound is our experience of physical disturbances, causing vibrations in our mediums ~\cite{cook1999chap4}.
-A sound wave can be viewed as the result of a function which governs amplitude through time, where time and amplitude exist in continuous dimensions.
-Waves can be approximated via a series of samples, associating time steps to a discrete range of amplitude values.
-\textit{Digital synthesis} of audio is the process of creating these discrete values.
-Unlike the majority of the works mentioned in Section~\ref{related_works}, we do not employ probabilistic models for the synthesizer component.
+Digital sound is a series of discrete values.
+\textit{Digital synthesis} of audio is the process of creating these values.
+Here, we do not employ probabilistic models for the synthesizer component.
 Our decision is based on the following factors:
@@
 In this work, we are not aiming for perfect imitations.
-We seek to create \emph{novel sounds} by via artifical, exploratory creativity.
+We seek to create \emph{novel sounds} by via artificial, exploratory creativity.
 Boden defines this concept as an emergent property of generative work within confined rule sets~\cite{boden2009computer}.
@@
 Their highly recursive structure makes modern explanation methods such as saliency maps unreliable~\cite{rudin2019stop}.
-    \item \textit{Speed of Rendering at high sampling rates}: Despite the utilization of powerful GPUs, the standard sampling rate in most audio generation work utilizing neural is under 24 khz \cite{yamamoto2020parallel,oord2017parallel,aouameur2019neural,ramires2020neural}.
+    \item \textit{Speed of Rendering at high sampling rates}: Despite the utilization of powerful GPUs, the standard sampling rate in most audio generation work utilizing neural networks is under 24 khz ~\cite{yamamoto2020parallel,oord2017parallel,aouameur2019neural,ramires2020neural}.
 However, a significant number of untrained human ears can detect a change in quality of audio between sampling rates of 192 khz and the industry standard of 44.1 khz \cite{reiss2016meta}.
-In this work, we fix our sampling rate 48 khz.
+At our fixed sampling rate of 48 khz, synthesizers with stack sizes of 8 can create and save 1 sounds to hard-disk with an average rendering time of 50 milliseconds\footnote{Using a single process on a Macbook Air 2012 and Ubuntu 18.04}.
+    \item \textit{Flexibility and Scaling}: Probabilistic audio generation is often done sequentially.
+For example, state of the art, parallel wave generation with GANs requires a fixed amount for rendering time for each time-step~\cite{yamamoto2020parallel}.
+Our virtual synthesizer produces audio by solving a linear system of equations.
+The added footprint of increasing the length of rendered sounds or higher sampling rates is relatively minuscule.
 \end{itemize}
 
- Evaluation of a periodic function such as sine or cosine is the simplest form of software audio generation~\cite{mitchell2009basicsynthChap5}.
+%  Evaluation of a periodic function such as sine or cosine is the simplest form of software audio generation~\cite{mitchell2009basicsynthChap5}.
 This generative system is called an \textit{oscillator}.
-With careful programming, DSP techniques can be used to replicate almost any sound, which is why they have powered commercial digital synthesizers for over half a century ~\cite{jenkins2019analog}.
+With careful programming, DSP techniques can be used to replicate almost any sound~\cite{jenkins2019analog}.
 Synthesizers we build using these functions are tractable and explainable: the output is determined by the input and reproducible.
@@
 
-We opted for a set of classical DSP methods to build our synthesizer, which allow for quick offline, and parallel generation of audio signals without the usage of GPUs.
+We rely on a set of classical DSP methods to build our synthesizer, which allows for quick, offline, and parallel generation of audio signals without the usage of GPUs.
 We made extensive use of Pippi\footnote{https://github.com/luvsound/pippi} and SciPy~\cite{jones2001scipy} libraries.
@@
     \caption{ 
-    Scales are symbolic (true scales are not measurable and/or subjective).
+    Not to scale (true scales are not measurable and/or subjective).
 $\mathcal{N}$ is the set of percussive sounds a synthesizer is capable of making.
+The inclusion of sounds in this group may vary from person to person.
 Our positive samples, $\mathcal{T^{+}}$, is a small fraction of a wide variety of percussive sounds that are conceivable.
-The size of $\mathcal{T^{-}}$ can be set to any number(we can generate as any number of random samples), but we prefer to keep it no larger than  $\mathcal{T^{+}}$.
+For $\mathcal{T^{-}}$, we can generate any number of random samples.
 $\mathcal{H}$ is a series of sounds sent to the ear for classification.
@@
 An important consideration is that the source of sounds used in training the model (organic drum sounds) will be fundamentally different from the source of unlabeled sounds we wish to categorize (noise from a synthesizer).
-This issue is reflective of the OSR problem~\cite{geng2020recent,mundt2019open}.
-Figure~\ref{fig:ven_data} highlights a number of caveats with this approach.
-we denote $\mathcal{N}$ as the set of percussive sounds a synthesizer is capable of making.
-$\mathcal{T^{+}}$, our positive examples, is a set of sound extracted from material drums.
-$\mathcal{T^{-}}$, is a small subset of an infinite set which is meant to represent all noises which the synthesizer is capable of making and likely includes sounds in $\mathcal{N}$.
+This issue is reflective of the open set recognition (OSR) problem~\cite{geng2020recent,mundt2019open}.
+We use figure~\ref{fig:ven_data} to highlight a number of caveats with our training approach: We denote $\mathcal{N}$ as the set of percussive sounds a synthesizer is capable of making.
+$\mathcal{T^{+}}$, our positive examples, is a set of sound extracted from material drums (see Appendix~\ref{appendix:datasets} for details about our datasets).
+$\mathcal{T^{-}}$ is a small subset of an infinite set used to represent all noises which the synthesizer is capable of making.
+Moreover, $\mathcal{T^{-}}$ likely includes sounds in $\mathcal{N}$.
 During the hearing test, the virtual ear continually receives synthesizer noises for classification.
@@
 To train our virtual ear, we require generalizable, domain agnostic features.
-Various works have demonstrated effective reconstruction of signals given their Short-time Fourier Transforms (STFT) ~\cite{nawab1983signal,griffin1984signal}.
-If the STFT of a signal can be used its reconstruction, perhaps it can be utilized as a source of fundamental features necessary for audible signal categorization.
-We defined 3 STFT transformation functions which we believe to capture important, unique attributes of percussive sounds (figure ~\ref{fig:stackspectrums}).
+Various works have demonstrated effective reconstruction of signals given their Short-time Fourier Transforms (STFT)~\cite{nawab1983signal,griffin1984signal}.
+If the STFT of a signal can be used for its reconstruction, perhaps it can be utilized as a source of fundamental features.
+We defined 3 STFT transformation functions which we believe to capture important, unique attributes of percussive sounds (figure~\ref{fig:stackspectrums}).
 Our transformations are GPU based, allowing their application in tandem to the training of the classifier or tuning of STFT transformation during hyper-paramter optimization (see Appendix~\ref{appendix:hyperparam}).
@@
 MEMs are trained using highly compressed, automatically encoded representation of sounds and can give simultaneous answers to both questions.
-Model specifications and measurments for TPE and MEMs can be found in Appendix~\ref{appendix:C}.
+Model specifications and extended measurements for TPE and MEMs can be found in Appendix~\ref{appendix:classifier_definitions}.
 We speculate that the features used to represent sounds plays a much more important role in determining outcomes, particularly when working with relatively small datasets.
@@
 Referring to~\hypref{Decision.1} and~\hypref{Decision.2}, we expect the drum sounds to be clustered together, with the majority of the synthetic noise sounds appearing away from these clusters.
-The projections confirmed that this is the case (see Appendix~\ref{appendix:E}).
+The projections confirmed that this is the case ( see Appendix~\ref{appendix:E} for examples of these projections).
 We are most interested in synthetic noise sounds which appear within or near these clusters.
@@
  \begin{table}
- \resizebox{\linewidth}{!}{\begin{tabular}{||c c c c||} 
+ \resizebox{\linewidth}{!}{\begin{tabular}{|c c c c|} 
  \hline
- Drop Rule & Size & H+H & H+H+MEM \\
+ Drop Rule & Size & H+H & H+MEM \\
  \hline
@@
 \end{table}
-With our virtual synthesizer and virtual ears in place, we build two pipelines.
-We chose CNNLSTM-DVN for \hypref{Decision.1}, and FC-DVD,CNNLSTM-DVD and E/F for \hypref{Decision.2} to build the TPE pipeline.
+We built two pipelines and analyzed the results.
+We the TPE pipeline uses CNNLSTM-DVN for \hypref{Decision.1}, and FC-DVD, CNNLSTM-DVD and E/F for \hypref{Decision.2}.
 The MEM pipeline uses our best MEM, which simultaneously classifies sounds as drums and categorizes them.
@@
 The MEM pipeline does not output the \enquote{other} category, yet the option is available to surveyors when categorizing sounds manually.
-The sounds and the corresponding synthesizer programs are saved to hard-disk.
-Here we assess the success rate of two different pipelines---and by extension, the virtual ears---by manual inspection of sounds categorized as drums, as well as the category of those drums.
-Both authors categorized a subset of the results without knowledge of the drum categorization outcomes.
-Additionally, each responder had the option of labeling samples as \enquote{bad} for samples that they deemed not percussive.
+We assess the success rate of each pipeline---and by extension, the virtual ears---by manual inspection of sounds categorized as drums.
+Both authors categorized a subset of the results without knowledge of the assigned labels.
+Additionally, each responder has the option of labeling samples as \enquote{bad} for samples that they deemed not percussive.
 The percentage of sounds labeled as \enquote{bad} by the authors is a measurement of success with regards to \hypref{Decision.1}.
-We measure success with regards to \hypref{Decision.2}---the reliability of agreement between persons and drum categorization models--- via the Fleiss' kappa coefficient \cite{fleiss1971measuring}.
+We measure success with regards to \hypref{Decision.2}---the reliability of agreement between persons and drum categorization models---via the Fleiss' kappa coefficient \cite{fleiss1971measuring}.
 The value of 0 or less for this coefficient indicates no agreement beyond random chance, and the values of 1 indicates perfect agreement.
@@
 We also show measurements after dropping all \enquote{bad} and \enquote{other} samples.
-
 \subsection{Survey Discussion}
@@
 Suggesting that latent representations of autoencoder networks can be used as general, low-dimensional proxies for representation of complex inputs.
+
+\section{Conclusion and Future Work}
 \bibliographystyle{apacite}
@@
 \chapter{Datasets}
-\label{appendix:A}
-\begin{table}[h!]
+\label{appendix:datasets}
+Our data sources are a large set of 2 second or shorter drum samples aggregated from personal libraries, free drum kits from the sample-swap project \footnote{https://sampleswap.org/} which we organized into 5 groups, and a large set of drum sounds aggregated from royalty free sources such as musicradar \footnote{https://www.musicradar.com/}.
+We put together 3 databases of drums using these sources.
+We also created a database of synthetic noise from 1, 3, and 5 stacked virtual synthesizers.
+Specifications about our datasets can be found in tables~\ref{db:self},~\ref{db:radar},~\ref{db:sampleswap} and~\ref{db:noise}.
+We have made our dataset of free-drum sounds available for download.
+The scripts used to download and process royalty free samples are also made available.
+Further information about downloading our dataset can be found on the project's github page.
+
+We prioritize making generalizable tools which can learn from and produce a variety of different sounds.
+We utilize these databases depending on the task at hand.
+At times, we merged or purged drum groups to simplify tasks.
+\begin{table}[]
 \centering
@@
 
-\begin{table}[h!]
+\begin{table}[]
 \centering
@@
 \chapter{Audio Transformation Functions}
-\label{appendix:B}
+\label{appendix:trans_funcitons}
 \begin{figure}
@@
 \chapter{Virtual Ear Classifier Definitions}
-\label{appendix:C}
+\label{appendix:classifier_definitions}
 \section{Two Phased models}

### 2020-08-21 templates_aimusic2020/paper.tex
Updates from Overleaf

@@
     \begin{center}
-    \textbf{Generative System}
+    % \textbf{Generative System}
     \makebox[\textwidth]{
@@
 \end{tabular}}
-\caption{Synthesizer submodule Parameters.
+\caption{Synthesizer submodule parameters.
 Despite the simplicity of the parameters and our efforts at constraining the ranges, the number of parameters that can be randomly chosen for each submodule is over $10^{15}$.
-Each synthesizer can contain any number of submodules }
+Each synthesizer can contain any number of submodules}
 \label{table:submodule_params}
@@
 
+ \begin{figure}[t]
+    \begin{center}
+    % \textbf{Synthesizer SubModule }
+    \makebox[\textwidth]{
+    \fbox{\includegraphics[width=1\linewidth]{templates_aimusic2020/images/synthesizer_block.pdf}}}
+    \end{center}
+    \caption{High level representation of pre-rendering steps for each submodule.
+Each Synthesizer contains 1 or more these submodules.
+The output of a synthesizer is the normalized addition of all its submodule outputs.
+Each synthesizer program determines the number of these submodules and their parameters.
+    }
+\label{fig:pipeline_outline}
+\end{figure}
+
 We rely on a set of classical DSP methods to build our synthesizer, which allows for quick, offline, and parallel generation of audio signals without the usage of GPUs.
@@
 \section{Virtual Ear}
-
-We are not looking for the perfect imitation of organic drums using a synthesizer.
-We seek to imitate drums using a synthesizer and even \textbf{prefer} for its generations to retain novel, unusual characteristics.
 The task assigned to the virtual ear is the rare acceptance of drum-like sounds and the inevitable rejection of most \enquote{noise} outputs from the virtual synthesizer.
+Our goal is not realism; We want the virtual ear to accept novel and unusual drum sounds.
 The virtual ear makes two critical decisions:

### 2020-08-21 templates_aimusic2020/paper.tex
Updates from Overleaf

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newcommand{\descfirst}{\textit{Descision.1~}}
+\newcommand{\descsecond}{\textit{Descision.2}}
 
 \documentclass[runningheads,a4paper]{llncs}
-
 \usepackage{amssymb}
@@
 \end{figure}
-
 We rely on a set of classical DSP methods to build our synthesizer, which allows for quick, offline, and parallel generation of audio signals without the usage of GPUs.
@@
 \section{Virtual Ear}
-The task assigned to the virtual ear is the rare acceptance of drum-like sounds and the inevitable rejection of most \enquote{noise} outputs from the virtual synthesizer.
+\label{section:virtual_ear}
+The virtual ear receives sounds and discards those which do not resemble drums.
+Accepted sounds are assigned a drum category.
 Our goal is not realism; We want the virtual ear to accept novel and unusual drum sounds.
@@
 \begin{quote}
-\text{Decision.1 Could the sound be used as a drum?}\label{Decision.1}
+\text{Decision.1 Could the sound be used as a drum?}
 \\
-\text{Decision.2 If it does sound like a drum, what type of drum should it be?}\label{Decision.2}
+\text{Decision.2 If it does sound like a drum, what type of drum should it be?}
 \end{quote}
@@
     \begin{center}
-    \textbf{Data Overview}
-    \makebox[\textwidth]{
-    \includegraphics[width=0.95\linewidth]{images/venn_data.pdf}}
+    \makebox[\textwidth]{\includegraphics[width=0.95\linewidth]{images/venn_data.pdf}}
     \end{center}
-    \caption{ 
-    Not to scale (true scales are not measurable and/or subjective).
+    \caption{ An illustration of the discrepancy between the sounds we use to train our classifiers and the type of sounds the classifier is expected to classify.
 $\mathcal{N}$ is the set of percussive sounds a synthesizer is capable of making.
@@
 $\mathcal{H}$ is a series of sounds sent to the ear for classification.
-The ideal ear will detect  $\mathcal{H^{+}}$, the overlap of $\mathcal{H}$ and $\mathcal{N}$, with high precision and recall.
+Not to scale (true scales are not measurable and/or subjective).
     }
@@
 \end{figure}
-\hypref{Decision.1} requires knowledge of what drums \textbf{do not} sound like, or knowledge of an infinitely large set, which cannot be fully represented via examples.
+\descfirst requires knowledge of what drums \textbf{do not} sound like, or knowledge of an infinitely large set, which cannot be fully represented via examples.
 An important consideration is that the source of sounds used in training the model (organic drum sounds) will be fundamentally different from the source of unlabeled sounds we wish to categorize (noise from a synthesizer).
@@
 We use figure~\ref{fig:ven_data} to highlight a number of caveats with our training approach: We denote $\mathcal{N}$ as the set of percussive sounds a synthesizer is capable of making.
-$\mathcal{T^{+}}$, our positive examples, is a set of sound extracted from material drums (see Appendix~\ref{appendix:datasets} for details about our datasets).
-$\mathcal{T^{-}}$ is a small subset of an infinite set used to represent all noises which the synthesizer is capable of making.
-Moreover, $\mathcal{T^{-}}$ likely includes sounds in $\mathcal{N}$.
+$\mathcal{T^{+}}$, our positive examples, is a set of one-shot drum sounds (see Appendix~\ref{appendix:datasets} for details about our datasets).
 During the hearing test, the virtual ear continually receives synthesizer noises for classification.
@@
 The performance of the ear is measured by its precision and recall in finding the overlap between $\mathcal{H}$ and $\mathcal{N}$.
-It is important to ensure that the change in learning domains---particularly with the case of positive examples of percussive sounds---does not interfere with transformation of knowledge from the training of the ear to the hearing test.
+It is important to ensure that the change in domains---particularly with the case of positive examples of percussive sounds---does not interfere with transformation of knowledge from the training of the ear to the hearing test.
 To maximize the transference of knowledge from one domain to another, we seek to learn from agnostic feature sets that capture fundamental characteristics of the data points.
 \subsection{Feature Extraction}
-To train our virtual ear, we require generalizable, domain agnostic features.
 Various works have demonstrated effective reconstruction of signals given their Short-time Fourier Transforms (STFT)~\cite{nawab1983signal,griffin1984signal}.
 If the STFT of a signal can be used for its reconstruction, perhaps it can be utilized as a source of fundamental features.
-We defined 3 STFT transformation functions which we believe to capture important, unique attributes of percussive sounds (figure~\ref{fig:stackspectrums}).
-Our transformations are GPU based, allowing their application in tandem to the training of the classifier or tuning of STFT transformation during hyper-paramter optimization (see Appendix~\ref{appendix:hyperparam}).
+We defined 3 STFT transformation functions which we believe to capture important, unique attributes of percussive sounds.
+\begin{figure}
+\begin{center}
+% \textbf{Visual Representation of FFT Features}\par\medskip
+    \makebox[\textwidth]{\includegraphics[width=0.85\paperwidth]{templates_aimusic2020/images/ff3.pdf}}
+\caption{Graphed representation of FFT/STFT features.
+Randomly generated noise with a percussive envelop but unusual frequency features (modulated pitch).
+See Appendix~\ref{appendix:trans_funcitons} for more examples }
+\label{fig:stackspectrums}
+    \end{center}
+\end{figure}
+\begin{enumerate}
+\item Envelope Transformation: Represents changes in loudness for the duration of the signal.
+Using STFT we generate a matrix $M_{i \times j}$ with rows $i$ and columns $j$ corresponding to time steps and frequency bins.
+Values $v_{i \times j}$ indicate the magnitude of the frequency bin $j$ at each time-step $i$.
+We approximate the envelope of the signal by summing the values of $M$ for at time-step (or row $i$).
+\item Frequency Transformation:  The calculation of this feature vector is similar to the envelope, but the summation is done along the frequency axis.
+Shorter hop-sizes and wider windows were used to increase frequency resolution.
+\item Spectrum Transformation: Mel Scaled STFT with its values normalized from 0-1. 
+\end{enumerate}
+% Our transformations are GPU based, allowing their application in tandem with the training of the classifier or tuning of STFT transformation during hyper-paramter optimization (see Appendix~\ref{appendix:hyperparam}).
+Another set of features were extracted using the latent embeddings of autoencoder networks.
+We trained a number of autoencoders for the task of encoding and decoding spectrogram transformation of drum sounds, and used decoding loss to measure their performance (see appendix~\ref{appendix:hyperparam}).
+Latent embeddings at the bottleneck layer of our best spectrogram autoencoder are used as features for sound categorization.
+As a sanity check for this approach, we trained our best autoencoder using 80\% of the drums in MixedDB.
+Latent encodings of the remaining 20\% and 1000 Noise sounds were projected onto a 2 or 3-dimensional planes using t-SNE.
+We implemented interactions for our projection graphs (see Appendix~\ref{appendix:tsne}) so the sounds associated with plot points can be listened to.
+Hearing tests revealed a noticeable, positive correlation between a synthetic sound's distance and similarity to drum clusters.
 \subsection{Ear Types}
 \label{classifiers}
-
-Two groups of classifiers are implemented: \emph{two phased ears} (TPEs) and \emph{Mixed Ear Models} (MEMs).
-TPEs combine different models specializing in~\hypref{Decision.2} or~\hypref{Decision.1} and trained only with our transformation functions.
-MEMs are a proof of concept attempt at addressing the OSR problem by usage of autoencoded representation of sounds as features.
-MEMs are trained using highly compressed, automatically encoded representation of sounds and can give simultaneous answers to both questions.
-Model specifications and extended measurements for TPE and MEMs can be found in Appendix~\ref{appendix:classifier_definitions}.
-We speculate that the features used to represent sounds plays a much more important role in determining outcomes, particularly when working with relatively small datasets.
-
-The features used by MEMs are encodings extracted from the latent layer of an autoencoder trained to encode and decode spectrogram representations of sound in MixedDB.
-To better understand the delineation potential of the encoded features, 64-dimensional latent representation of 20\% of MixedDB and 1000 Noise sounds were projected onto a 2 or 3-dimensional planes using t-SNE.
-Referring to~\hypref{Decision.1} and~\hypref{Decision.2}, we expect the drum sounds to be clustered together, with the majority of the synthetic noise sounds appearing away from these clusters.
-The projections confirmed that this is the case ( see Appendix~\ref{appendix:E} for examples of these projections).
-We are most interested in synthetic noise sounds which appear within or near these clusters.
-Do these synthetic noise sounds have drum like characteristics?\\
-To test this, we implemented interactive projection graphs.
-These graphs allow interactions such as playing the samples(by hovering the cursor on-top) and movement of the scene camera.
-Manual inspections revealed a noticeable, positive correlation between a synthetic sound's distance and similarity of a synthetic sound to drum clusters.
-
+Two groups of synthetic ears are implemented: \emph{two phased ears} (TPEs) and \emph{Mixed Ear Models} (MEMs).
+TPEs combine different models specializing in ~\descfirst or ~\descsecond~ and are trained only with our FFT features.
+MEMs are trained with autoencoder embeddings and envelope features and give simultaneous answers to both questions.
+Our best TPE models achieve 82\% accuracy in a 6-way drum categorization task and 98\% accuracy in separation of drums from non-drum sounds.
+Our best MEM achieves 91\% accuracy in a 4 way drum categorization task and 99\% accuracy in separation of drums from non-drums.
+Further specifications and detailed measurements for TPE and MEMs can be found in Appendix~\ref{appendix:classifier_definitions}.
 \section{Pipelines and Surveys}
 \label{surveys}
-\begin{table}
- \begin{tabular}{|c c c c c c c|} 
- \hline
- Drop Rule & Size & H+H & H+FC & H+CNN & H+E/F & 3 models \\ [0.5ex] 
- \hline
- No Drops & 257 &0.37 & 0.35 & 0.36 & 0.36 & 0.28\\ 
- \hline
- Assigned \enquote{Bad} By Both & 236 & 0.31 & 0.37 & 0.37 & 0.38 & 0.30 \\
- \hline
- Assigned \enquote{Bad} By Either & 180 & 0.47 & 0.50 & 0.48 & 0.48 &  0.34 \\
- \hline
- Assigned \enquote{Bad} or \enquote{Other} By Either & 154 & 0.47 & 0.59 & 0.54 & 0.50 &  0.35 \\
- \hline
-\end{tabular}
-\caption{\label{kappa_table_TPE}Table of Fleiss' kappa coefficient to measure the degree of agreement between persons (H+H), persons with FC model (H+FC), persons with CNNLSTM model, persons with all models (H+E/F), and between the 3 models.
+% \begin{table}[h!]
+%  \begin{tabular}{|c | c | c | c | c | c | c|} 
+%  \hline
+%  Drop Rule & Size & H+H & H+FC & H+CNN & H+E/F & 3 models \\ [0.5ex] 
+%  \hline
+%  No Drops & 257 &0.37 & 0.35 & 0.36 & 0.36 & 0.28\\ 
+%  \hline
+%  Assigned \enquote{Bad} By Both & 236 & 0.31 & 0.37 & 0.37 & 0.38 & 0.30 \\
+%  \hline
+%  Assigned \enquote{Bad} By Either & 180 & 0.47 & 0.50 & 0.48 & 0.48 &  0.34 \\
+%  \hline
+%  Assigned \enquote{Bad} or \enquote{Other} By Either & 154 & 0.47 & 0.59 & 0.54 & 0.50 &  0.35 \\
+%  \hline
+% \end{tabular}
+% \caption{\label{kappa_table_TPE}Table of Fleiss' kappa coefficient to measure the degree of agreement between persons (H+H), persons with FC model (H+FC), persons with CNNLSTM model, persons with all models (H+E/F), and between the 3 models.
 }
-\end{table}
+% \end{table}
 
- \begin{table}
- \resizebox{\linewidth}{!}{\begin{tabular}{|c c c c|} 
- \hline
- Drop Rule & Size & H+H & H+MEM \\
- \hline
- No Drop & 300 & 0.34 & 0.25\\ 
- \hline
- Assigned Bad By Both & 249 & 0.20 & 0.26 \\
- \hline
- Assigned Bad By Either & 151 & 0.46 &  0.47 \\
- \hline
-Assigned \enquote{Bad} or \enquote{Other} By Either  & 120 & 0.62   &  0.59 \\
- \hline
-\end{tabular}}
-\caption{\label{kappa_table_MEM}Table of Fleiss' kappa coefficient to measure the degree of agreement between persons (H+H) and persons with MEM (H+MEM).}
-\end{table}
-We built two pipelines and analyzed the results.
-We the TPE pipeline uses CNNLSTM-DVN for \hypref{Decision.1}, and FC-DVD, CNNLSTM-DVD and E/F for \hypref{Decision.2}.
-The MEM pipeline uses our best MEM, which simultaneously classifies sounds as drums and categorizes them.
-The TPE pipeline produces samples in the following categories: \enquote{snare}, \enquote{kick}, \enquote{hat}, \enquote{clap} and \enquote{other} (combination of rims, shakers and unusual percussive sounds).
+%  \begin{table}[h!]
+%  \begin{tabular}{|c| p{2cm} | p{2cm}| p{2cm}|} 
+%  \hline
+%  Drop Rule & Size & H+H & H+MEM \\
+%  \hline
+%  No Drop & 300 & 0.34 & 0.25\\ 
+%  \hline
+%  Assigned Bad By Both & 249 & 0.20 & 0.26 \\
+%  \hline
+%  Assigned Bad By Either & 151 & 0.46 &  0.47 \\
+%  \hline
+% Assigned \enquote{Bad} or \enquote{Other} By Either  & 120 & 0.62   &  0.59 \\
+%  \hline
+% \end{tabular}
+% \caption{\label{kappa_table_MEM}Table of Fleiss' kappa coefficient to measure the degree of agreement between persons (H+H) and persons with MEM (H+MEM).}
+% \end{table}
+High accuracy in detection of drums vs not-drums does not necessarily make an ear more suitable for our generative system.
+Perfect detection of drums vs not-drums would create a system which generates nothing.
+We cannot know the true size of $\mathcal{H^{+}}$ without manual hearing tests.
+We conduct manual hearing tests of two generative systems.
+The TPE system uses CNNLSTM-DVN for \descfirst, and FC-DVD, CNNLSTM-DVD and E/F for \descsecond.
+The MEM system uses our best MEM, which simultaneously classifies sounds as drums and categorizes them.
+The TPE system produces samples in the following categories: \enquote{snare}, \enquote{kick}, \enquote{hat}, \enquote{clap} and \enquote{other} (combination of rims, shakers and unusual percussive sounds).
 The MEM pipeline does not output the \enquote{other} category, yet the option is available to surveyors when categorizing sounds manually.
-We assess the success rate of each pipeline---and by extension, the virtual ears---by manual inspection of sounds categorized as drums.
 Both authors categorized a subset of the results without knowledge of the assigned labels.
 Additionally, each responder has the option of labeling samples as \enquote{bad} for samples that they deemed not percussive.
-The percentage of sounds labeled as \enquote{bad} by the authors is a measurement of success with regards to \hypref{Decision.1}.
-We measure success with regards to \hypref{Decision.2}---the reliability of agreement between persons and drum categorization models---via the Fleiss' kappa coefficient \cite{fleiss1971measuring}.
+The percentage of sounds labeled as \enquote{bad} by the authors is a measurement of success with regards to \descfirst.
+We measure success with regards to \descsecond---the reliability of agreement between persons and drum categorization models---via the Fleiss' kappa coefficient \cite{fleiss1971measuring}.
 The value of 0 or less for this coefficient indicates no agreement beyond random chance, and the values of 1 indicates perfect agreement.
-We again measure this coefficient after dropping samples that were categorized as \enquote{bad} by one or both authors.
-We also show measurements after dropping all \enquote{bad} and \enquote{other} samples.
-\subsection{Survey Discussion}
-\label{survey2_takeaway}
-Due to the discrepancy in categorization and output groups, results from the two surveys must be compared with caution.
-Agree-ability scores for MEM pipeline are often lower, but we reiterate that the MEM survey has two out of six (rather than one out of six in the TPE pipeline) categories which are exclusive to survey responders.
-Supporting this hypothesis is the notable improvement in agree-ability observed after dropping all \enquote{bad} and \enquote{other} samples.
-Despite the drawbacks, the MEM pipeline remains competitive while working with a fraction of the features to learn from and simultaneously making both decisions.
-Suggesting that latent representations of autoencoder networks can be used as general, low-dimensional proxies for representation of complex inputs.
+\\
+% We again measure this coefficient after dropping samples that were categorized as \enquote{bad} by one or both authors, and after after dropping all \enquote{bad} and \enquote{other} samples.
+The majority of sounds created by our system are deemed percussive by both surveyors.
+30\% of the outputs from the TPE system and 50\% of the MEM system outputs are deemed as non-percussive by at least one person.
+This leaves much room for improvement with regards to~\descfirst.
+Our performance with regards to ~\descsecond~ is promising as we achieve moderately high agree-ability scores after dropping bad sounds.
+Despite the drawbacks, the MEM pipeline remains competitive while working with a fraction of
+the features to learn from and simultaneously making both decisions.
 
-\section{Conclusion and Future Work}
+% Suggesting that latent representations of autoencoder networks can be used as general,low-dimensional proxies for representation of complex inputs.
+
+\section{Conclusion, Validity, and Future Work} [in progress, need sleep] \\
+\textbf{Conclusion:} We successfully built a generative system for creation of percussive sounds via automatic programming of virtual synthesizers.  
+Our work enables not only the creation of new libraries of percussion sounds, but new synthesizer programs which can be modified and studied. 
+Manual listening tests revealed much room for improvement, particularly with accurate separation of percussive sounds from the infinitely large set of non-percussive sounds.
+We achieved moderate success in our utilization of latent representations of autoencoder networks as low-dimensional representations of short sound files.
+\\
+\textbf{Threats to Validity:} The lack of consistency in training and accuracy measurements makes comparisons between TPEs and MEMs difficult.
+We made many arbitrary design decisions, particularly in the design of our TPE classifiers and selection of datasets for training and testing.
+We sought to enable creative exploration by generation of sounds with limited resources, yet cannot verify or quantify the novelty of our results.
+Without an effective few-shot learning method, our requirement for training data remains high.\\
+\textbf{Future Work:} In future works, we seek to improve our virtual ear with state of the art few-shot learning models.
+Our design allows easy integration of heuristic search, an improvement we aim to make in future works.
+Our systems also allows easy experimentation with other synthesis and virtual listening methods, this may involve generation of other categories of instruments.
+We consider the integration of our system with the VST protocol as a major long term goal.
+
 \bibliographystyle{apacite}
@@
 \label{appendix:datasets}
-Our data sources are a large set of 2 second or shorter drum samples aggregated from personal libraries, free drum kits from the sample-swap project \footnote{https://sampleswap.org/} which we organized into 5 groups, and a large set of drum sounds aggregated from royalty free sources such as musicradar \footnote{https://www.musicradar.com/}.
+Our data sources are a large set of 2 second or shorter drum samples aggregated from personal libraries, free drum kits from the sample-swap project \footnote{https://sampleswap.org/} which we organized into 5 groups, and a large set of drum sounds aggregated from royalty free sources such as music radar \footnote{https://www.musicradar.com/}.
 We put together 3 databases of drums using these sources.
@@
 being categorized is switched.
+\subsection{Mixed Ear Models}
+\label{chap3:mixed_ear_models}
 
-%========
+ We compare the performance of our models before and after the addition of envelope features (a vector of size 10) to the feature space.
+We reuse the model trained on  MixedDB as our embedding feature extractor.
+We use a combination of RadarDB, FreeDB and NoiseDB for training.
+We only focus on clap,hat,kick,snares, synthetic noise groups for measuring effectiveness to prevent class overlaps as much as possible.
+We also exclude samples longer than 1 second, to exclude potentially mislabeled data.
+Our final training database for mixed ear models is described in table~\ref{db:memDB}.
 
+\subsubsection{Model Selection}
+Using our encoding and envelope features to represent audio, five classification models were trained for the task of categorizing the five different sound groups.
+For hyper-parameter optimization, the models were trained using 5-fold cross validation and 80/20 train-to-test ratio.
+The F-Score result of each cross-validation is the unweighted average F-Score of all groups.
+For inter-model comparisons, the procedure is the same except 10-fold cross validations are used.
+Our models were derived from scikit-learn's implementations of these classifiers~\cite{pedregosa2011scikit}.
+Before inter-model comparisons, we conducted a grid-search for each model on at least one of its possibly decisive hyper-parameters.
+The classifiers and other notable specifications are presented in table~\ref{table:mem_model_selection}.
+\begin{table}[t]
+    \centering \hspace*{-0.8cm}
+    \begin{threeparttable}
+    \begin{tabular}[width=0.95\paperwidth]{|l|l|l|}
+    \hline
+    Model name & Tuned Parameters\tnote{\dag}  & Used Weights? \tnote{\ddag} \\\hline
+     Support Vector Classifier (SVC) &  Gamma:0.001, C:100, kernel:rbf & Yes\\
+     LinearSVC & C:10 & Yes\\
+     K Nearest Neighbors & Num. Neighbors:30 &  No \\
+     Random Forest Classifier & Num Estimators:500 & Yes \\
+     Extra Trees Classifier & Num Estimators:1100 & Yes\\
+     \hline
+    \end{tabular}
+    \caption{Models implemented for comparison using envelope and embedded features. }
+    \begin{tablenotes}
+    \item[\dag] Tuned parameters values are based on grid-searching for best f-score.
+Parameters not mentioned have neither been tuned nor changed from scikit-learn's default values (as of version 0.23)
+    \item[\ddag] Class weights are used unless not applicable to classifier.
+    \end{tablenotes}
+    \label{table:mem_model_selection}
+    \end{threeparttable}
+\end{table}
+\begin{table}[htbp]
+\centering
+\begin{tabular}{|l|l|l|l|l|l|}
+\hline
+ DB Name & kick & snare & clap & hat & Synthetic Noise\\\hline
+ MixedEarDB & 1334 & 1035 & 401 & 1275 & 1000 \\ \hline
+\end{tabular}
+\caption{A database put together by combination of radarDB, FreeDB and NoiseDB}
+\label{db:memDB}
+\end{table}
+
+\begin{figure}[htbp!]
+    \begin{center}
+    \textbf{Cross Validation F-Scores For All Sound Groups}\par\medskip
+    \makebox[\textwidth]{\includegraphics[width=0.8\paperwidth]{images/mme_comparisons_mme.pdf}}
+    \caption{Boxplots visualizing the F-Score results for each cross-validation.
+The individual scores, means, medians, standard-deviation and outliers are depicted.
+The differences are noticeable, yet means lie within the \%88-92 range.
+Envelope features improve classification accuracy for all models.
+}
+    \label{fig:f1_allg_box}
+    \end{center}
+\end{figure}
+
+We're also interested in how these models perform on the binary drum vs not drum task.
+After grouping all drums together, we repeat the model selection process above.
+We also repeat the hyper-parameter optimization step where no changes appeared necessary except for a reduction in the number of neighbors for the K-Neighbor model (from 30 to 5).
+As show in in figures~\ref{fig:f1_allg_box} and~\ref{fig:f1_dvn_box}, the addition of envelope features had a positive effect on performance for all mdoels, yet the RandomForest and ExtraTrees models clearly outperform the other classifiers in both tasks.
+We train the top two models on \%80 of our database and use the remaining \%20 to create the confusion matrices and the F-Scores shown in figures~\ref{fig:conf_f1_dvn}.
+\begin{figure}[h!]   
+    \begin{center}
+        \textbf{Cross Validation F-Scores For Drum Vs Not-Drum}
+    \makebox[\textwidth]{\includegraphics[width=0.8\paperwidth]{images/mme_comparisons_dvn.pdf}}
+    \caption{F-Score results for each cross-validation.
+Models perform better as there are less categorization groups.
+Envelope features increase accuracy for all models.
+Random Forest and Extra Trees remain the top two models.
+}
+    \label{fig:f1_dvn_box}
+    \end{center}
+\end{figure}
+
+\begin{figure}[htbp!]
+\begin{center}
+    \textbf{ Classification Report for DvDvN and DvN  }\par\medskip
+    \makebox[\textwidth]{
+    \subfloat[Precision, recall, F1-Score, and number of supporting examples]{ \includegraphics[width=9cm,height=9cm]{images/f1_mme.pdf}
+    \includegraphics[width=9cm,height=9cm]{images/f1_dvn.pdf}
+    }
+
+    }
+\label{fig:conf_f1_dvd}
+\end{center}
+
+\begin{center}
+    \makebox[\textwidth]{
+    \subfloat[Confusion matrices]{ \includegraphics[width=9cm,height=9cm]{images/conf_mme.pdf}
+    \includegraphics[width=9cm,height=9cm]{images/conf_dvn.pdf}
+    }}
+\end{center}
+
+\caption{F-Scores and confusion matrix of ExtraTrees model for both DvDvN and drum vs not-drum categorization.}
+\label{fig:conf_f1_dvn}
+\end{figure}
+
+Based on these reports, having multiple options for drum categorization does not noticeably influence our models accuracy in categorizing synthetic noise as synthetic noise.
+However, the DvDvN models's slightly smaller false negative rate for synthetic noise (11 vs 13 false negatives) is countered by a slightly higher rate of categorizing drums as synthetic noise (12 vs 9).
+We therefore use the DvDvN implementation as it simultaneously categorizes drum types and separates noise from drums.
+However, without manual inspection, we cannot confirm the extent of this model's usefulness.
 %==============
@@
 \begin{table}[htbp]
-
 \begin{tabular}{|p{28mm}|p{50mm}|p{21mm}|p{21mm}|}
@@
     \end{center}
-
 \end{figure}
@@
 Live demos provided in project source code.
-\label{appendix:E}
+\label{appendix:tsne}
 \begin{figure}[]

### 2020-08-21 templates_aimusic2020/paper.tex
Updates from Overleaf

@@
 \usepackage{appendix}
+\usepackage{comment}
 
@@
 
-\title{Percussive Sound Generation with Virtual Listeners and Modular Synthesizers}
+% AH: If I commented it out, I think it's not great
+% AH: Please choose one
+% \title{Percussive Sound Generation with Virtual Listeners and Modular Synthesizers}
+\title{Percussive Synthesizer Generation with Virtual Listeners}
+\title{Percussive Synthesizer Program Generation with Virtual Listeners}
+\title{Generating Percussive Synthesizer Programs with Virtual Listeners}
+% \title{Listening to generative percussive synthesizer with virtual listeners}
+\title{Virtual Listeners to classify Percussive Synthesizer Programs}
+\title{Percussion program generation and filtering with Virtual Listeners}
+\title{Filtering generated percussion programs with Virtual Listeners}
+\title{Listen to it: Generating and filtering synthesizers by percussive qualities}
+\title{VirtuaListen to it: Generating and filtering synthesizers by percussive qualities}
 
 % a short form should be given in case it is too long for the running head
-\titlerunning{Virtual Percussive Sound Generation}
+\titlerunning{Percussive Synth. Generation}
 
@@
 % unless you accept that it will be published
-\institute{Department of Computing Science\\ University of Alberta \\ \email{asalimi@ualberta.ca\\ }}
+\institute{Department of Computing Science\\ University of Alberta \\ \email{asalimi@ualberta.ca\\hindle1@ualberta.ca}}
 
@@
 
- \begin{figure}[t]
+ \begin{figure}[tbp]
     \begin{center}
@@
 \section{Related Works}
-Numerous deep neural network models have been proposed for the purpose of signal generation in recent years.
+Numerous deep neural network models have been proposed for the purpose of signal generation in recent years~\cite{nsynth2017,yamamoto2020parallel,oord2017parallel,yee2018automatic,ramires2020neural}.
 WaveGans and WaveNet have been subject to significant improvements and experiments since their proposal~\cite{nsynth2017,yamamoto2020parallel,oord2017parallel}.
 Particularly relevant works are the utilization of variational autoencoders (VAE's) for generation of percussive samples~\cite{aouameur2019neural} and generation of percussive sounds by decoding a small set of latent features~\cite{ramires2020neural}.
-Automatic programming of virtual synthesizers has long been a topic of interest.
+Automatic programming~\footnote{unsupervised generation of source code or programs towards a goal} of virtual synthesizers has long been a topic of interest.
 In early 2000s, Interactive Genetic Algorithms (IGA's) were utilized for the generation of new sounds with various sound-engines~\cite{johnson1999exploring,dahlstedt2001creating}.
-More recent work by Yee-King et al.~\cite{yee2018automatic} used Long short-Term Memory (LSTM) models and genetic algorithms to find the exact parameters used to create a group of sounds.
+More recent work by Yee-King et al.~\cite{yee2018automatic} used Long short-Term Memory (LSTM) models and heuristic search to find the exact parameters used to create a group of sounds.
 The sounds approximated were made by the same virtual synthesizer and not with an external source, making the eventual replication certain even with random search.
@@
 \section{Virtual Synthesizer Design}
-\begin{table}[htbp]
+\begin{table}[tbp]
 \centering
@@
 \end{tabular}}
-\caption{Synthesizer submodule parameters.
-Despite the simplicity of the parameters and our efforts at constraining the ranges, the number of parameters that can be randomly chosen for each submodule is over $10^{15}$.
-Each synthesizer can contain any number of submodules}
+\caption{Synthesizer submodule parameters. There are $10^{15}$ unique programs are possible. Each synthesizer can contain any number of submodules}
 \label{table:submodule_params}
 \end{table}
-Digital sound is a series of discrete values.
-\textit{Digital synthesis} of audio is the process of creating these values.
-Here, we do not employ probabilistic models for the synthesizer component.
-Our decision is based on the following factors:
+ We need digital synthesizers to create sounds.
+We use classical DSP to build our synthesizer, which allows for quick, offline, and parallel generation of audio signals without the usage of GPUs.
+We made extensive use of Pippi\footnote{https://github.com/luvsound/pippi} and SciPy~\cite{jones2001scipy} libraries.
+Our virtual synthesizer contains a set of one or more submodules.
+Each submodule is a self-contained noise making unit and creates signals by taking the steps depicted in figure~\ref{fig:submodule}.
+Submodules have identical sets of parameters, but widely different outputs can be achieved depending on the values assigned.
+The set of required parameters for each submodule is highlighted in Table~\ref{table:submodule_params}.
+The sonic output of the virtual synthesizer is the normalized addition of the output of its submodules.
+Our implementation of a synthesizer can have any number of submodules.
+We call the number of submodules in each virtual synthesizer the \textit{stack size}.
+We call the sets of parameter values that characterize a synthesizer's submodules a \textit{program} (analogous to presets and submodules for a VST).
+ Rather than using probabilistic neural nets for sound synthesis, we generate programs for this virtual synthesizer Our decision is based on the following factors:
 \begin{itemize}
@@
 Boden defines this concept as an emergent property of generative work within confined rule sets~\cite{boden2009computer}.
-Ultimately, we wish to work within the limitations of any tractable sound source to create its approximations of a given sound category.
-Within the music realm, a prominent instance of exploratory creativity is the persistent aesthetics of 8-bit soundtracks, remaining popular long after the original constraints are lifted~\cite{collins2007loop}.
-    \item \textit{Interpretability}: Neural networks are often described as black boxes~\cite{basheer2000artificial}.
+An example is the perpetual popularity of 8-bit aesthetics~\cite{collins2007loop}.
+We want to work with the limitations of any tractable sound source to create its approximations of a given sound category.
+    \item \textit{Interpretability}: Neural networks are often described as black boxes with uninterruptible weights~\cite{basheer2000artificial}.
 Their highly recursive structure makes modern explanation methods such as saliency maps unreliable~\cite{rudin2019stop}.
-    \item \textit{Speed of Rendering at high sampling rates}: Despite the utilization of powerful GPUs, the standard sampling rate in most audio generation work utilizing neural networks is under 24 khz ~\cite{yamamoto2020parallel,oord2017parallel,aouameur2019neural,ramires2020neural}.
-However, a significant number of untrained human ears can detect a change in quality of audio between sampling rates of 192 khz and the industry standard of 44.1 khz \cite{reiss2016meta}.
-At our fixed sampling rate of 48 khz, synthesizers with stack sizes of 8 can create and save 1 sounds to hard-disk with an average rendering time of 50 milliseconds\footnote{Using a single process on a Macbook Air 2012 and Ubuntu 18.04}.
+    \item \textit{Speed of Rendering at high sampling rates}: Neural network synthesis is costly.
+Sub 24 khz sampling rates are common in most works~\cite{yamamoto2020parallel,oord2017parallel,aouameur2019neural,ramires2020neural}.
+This is far below CD quality sampling rates~\cite{reiss2016meta}.
+At our fixed sampling rate of 48 khz, synthesizers with 8 submodules can create and save 1 second sounds to hard-disk with an average rendering time of 50 milliseconds\footnote{Using a single process on a Macbook Air 2012 and Ubuntu 18.04}.
     \item \textit{Flexibility and Scaling}: Probabilistic audio generation is often done sequentially.
-For example, state of the art, parallel wave generation with GANs requires a fixed amount for rendering time for each time-step~\cite{yamamoto2020parallel}.
+State of the art, parallel wave generation with GANs requires a fixed amount for rendering time for each time-step~\cite{yamamoto2020parallel}.
 Our virtual synthesizer produces audio by solving a linear system of equations.
@@
     }
-\label{fig:pipeline_outline}
+\label{fig:submodule}
 \end{figure}
-We rely on a set of classical DSP methods to build our synthesizer, which allows for quick, offline, and parallel generation of audio signals without the usage of GPUs.
-We made extensive use of Pippi\footnote{https://github.com/luvsound/pippi} and SciPy~\cite{jones2001scipy} libraries.
-Our virtual synthesizer contains a set of one or more submodules.
-Each submodule is a self-contained noise making unit.
-Submodules have identical sets of parameters, but widely different outputs can be achieved depending on the values assigned.
-The set of parameters available to each submodule is highlighted in Table~\ref{table:submodule_params}.
-The sonic output of the virtual synthesizer is the normalized addition of the sonic output of its submodules.
-Our implementation of a synthesizer can have any number of submodules.
-The parameters that dictate the output signal of each submodule as well as the range of values each parameter can take are shown in table~\ref{table:submodule_params}.
-We call the number of submodules in each virtual synthesizer the \textit{stack size}.
-We call the sets of parameter values that characterize a synthesizer's submodules a \textit{program} (analogous to a preset for a VST).
 
@@
 The virtual ear receives sounds and discards those which do not resemble drums.
-Accepted sounds are assigned a drum category.
+It then classifies sounds by drum category.
 Our goal is not realism; We want the virtual ear to accept novel and unusual drum sounds.
@@
 
-\begin{figure}[htbp]
+\begin{figure}[tbp]
     \begin{center}
@@
 We defined 3 STFT transformation functions which we believe to capture important, unique attributes of percussive sounds.
-\begin{figure}
+\begin{figure}[tbp]
 \begin{center}
 % \textbf{Visual Representation of FFT Features}\par\medskip
-    \makebox[\textwidth]{\includegraphics[width=0.85\paperwidth]{templates_aimusic2020/images/ff3.pdf}}
+    \makebox[\textwidth]{\includegraphics[width=0.99\columnwidth]{templates_aimusic2020/images/ff3.pdf}}
 \caption{Graphed representation of FFT/STFT features.
@@
 \label{surveys}
-% \begin{table}[h!]
-%  \begin{tabular}{|c | c | c | c | c | c | c|} 
-%  \hline
-%  Drop Rule & Size & H+H & H+FC & H+CNN & H+E/F & 3 models \\ [0.5ex] 
-%  \hline
-%  No Drops & 257 &0.37 & 0.35 & 0.36 & 0.36 & 0.28\\ 
-%  \hline
-%  Assigned \enquote{Bad} By Both & 236 & 0.31 & 0.37 & 0.37 & 0.38 & 0.30 \\
-%  \hline
-%  Assigned \enquote{Bad} By Either & 180 & 0.47 & 0.50 & 0.48 & 0.48 &  0.34 \\
-%  \hline
-%  Assigned \enquote{Bad} or \enquote{Other} By Either & 154 & 0.47 & 0.59 & 0.54 & 0.50 &  0.35 \\
-%  \hline
-% \end{tabular}
-% \caption{\label{kappa_table_TPE}Table of Fleiss' kappa coefficient to measure the degree of agreement between persons (H+H), persons with FC model (H+FC), persons with CNNLSTM model, persons with all models (H+E/F), and between the 3 models.
-}
-% \end{table}
+
+\begin{comment}
+% AH: THIS TABLE IS COMMENTED OUT
+\begin{table}[h!]
+  \begin{tabular}{|c | c | c | c | c | c | c|} 
+  \hline
+  Drop Rule & Size & H+H & H+FC & H+CNN & H+E/F & 3 models \\ [0.5ex] 
+  \hline
+  No Drops & 257 &0.37 & 0.35 & 0.36 & 0.36 & 0.28\\ 
+  \hline
+  Assigned \enquote{Bad} By Both & 236 & 0.31 & 0.37 & 0.37 & 0.38 & 0.30 \\
+  \hline
+  Assigned \enquote{Bad} By Either & 180 & 0.47 & 0.50 & 0.48 & 0.48 &  0.34 \\
+  \hline
+  Assigned \enquote{Bad} or \enquote{Other} By Either & 154 & 0.47 & 0.59 & 0.54 & 0.50 &  0.35 \\
+  \hline
+ \end{tabular}
+ \caption{\label{kappa_table_TPE}Table of Fleiss' kappa coefficient to measure the degree of agreement between persons (H+H), persons with FC model (H+FC), persons with CNNLSTM model, persons with all models (H+E/F), and between the 3 models.
+} % AH: Which decision is this?
+ \end{table}
+\end{comment}
+
+\begin{table}[h!]
+  \begin{tabular}{|c | c | c | c | c | c | c|} 
+  \hline
+  \emph{Decision.1}\\
+  \hline
+  Drop Rule & Size & H+H & H+FC & H+CNN & H+E/F & 3 models \\ [0.5ex] 
+  \hline
+  No Drops & 257 &0.37 & 0.35 & 0.36 & 0.36 & 0.28\\ 
+  \hline
+  Assigned \enquote{Bad} By Both & 236 & 0.31 & 0.37 & 0.37 & 0.38 & 0.30 \\
+  \hline
+  Assigned \enquote{Bad} By Either & 180 & 0.47 & 0.50 & 0.48 & 0.48 &  0.34 \\
+  \hline
+  Assigned \enquote{Bad} or \enquote{Other} By Either & 154 & 0.47 & 0.59 & 0.54 & 0.50 &  0.35 \\
+  \hline
+  \emph{Decision.2}\\
+  \hline
+  Drop Rule & Size & H+H & H+MEM \\
+  \hline
+  No Drop & 300 & 0.34 & 0.25\\ 
+  \hline
+  Assigned Bad By Both & 249 & 0.20 & 0.26 \\
+  \hline
+  Assigned Bad By Either & 151 & 0.46 &  0.47 \\
+  \hline
+ Assigned \enquote{Bad} or \enquote{Other} By Either  & 120 & 0.62   &  0.59 \\
+ \end{tabular}
+ \caption{\label{kappa_table_TPE}Table of Fleiss' kappa coefficient to measure the degree of agreement between persons (H+H), persons with FC model (H+FC), persons with CNNLSTM model, persons with all models (H+E/F), and between the 3 models.
+ Table of Fleiss' kappa coefficient to measure the degree of agreement between persons (H+H) and persons with MEM (H+MEM)
+ } % AH: Which decision is this?
+ \end{table}
 
@@
 Perfect detection of drums vs not-drums would create a system which generates nothing.
-We cannot know the true size of $\mathcal{H^{+}}$ without manual hearing tests.
-We conduct manual hearing tests of two generative systems.
+We cannot know the true size of $\mathcal{H^{+}}$ without exhaustive manual hearing tests.
+We conduct small-scale (~300 each) manual hearing tests of two generative systems.
 The TPE system uses CNNLSTM-DVN for \descfirst, and FC-DVD, CNNLSTM-DVD and E/F for \descsecond.
@@
 
-\section{Conclusion, Validity, and Future Work} [in progress, need sleep] \\
+\section{Conclusion, Validity, and Future Work} 
 \textbf{Conclusion:} We successfully built a generative system for creation of percussive sounds via automatic programming of virtual synthesizers.  
@@
 Manual listening tests revealed much room for improvement, particularly with accurate separation of percussive sounds from the infinitely large set of non-percussive sounds.
-We achieved moderate success in our utilization of latent representations of autoencoder networks as low-dimensional representations of short sound files.
+We had some success in our utilization of latent representations of autoencoder networks as low-dimensional representations of short sound files.
 \\
@@
 Our systems also allows easy experimentation with other synthesis and virtual listening methods, this may involve generation of other categories of instruments.
-We consider the integration of our system with the VST protocol as a major long term goal.
+We consider the integration of our system with the VST protocol a long term goal.
 
@@
 \begin{appendices}
-\chapter{Datasets}
+%======================
+\chapter{Datasets Details and Downloads}
 \label{appendix:datasets}
+\subsection{Download Insturctions}
+FreeDB, survey data, and randomly generated sounds can be downloaded from: \url{https://zenodo.org/record/3994999}\\
+RadarDB requires lengthy downloads and processing.
+The script for its automated creation can be found under the \enquote{getting\_data} directory of our project code: \footnote{\url{https://github.com/imilas/Synths_Stacks_Search}}
+\subsection{Details}
 Our data sources are a large set of 2 second or shorter drum samples aggregated from personal libraries, free drum kits from the sample-swap project \footnote{https://sampleswap.org/} which we organized into 5 groups, and a large set of drum sounds aggregated from royalty free sources such as music radar \footnote{https://www.musicradar.com/}.
@@
 \label{appendix:trans_funcitons}
-\begin{figure}
+\begin{figure}[tbp]
 \centering

### 2020-08-22 templates_aimusic2020/paper.tex
Updates from Overleaf

@@
 \title{Listen to it: Generating and filtering synthesizers by percussive qualities}
-\title{VirtuaListen to it: Generating and filtering synthesizers by percussive qualities}
+\title{Virtual Listeners that filter percussion synthesizers}
+\title{Generating Drum synthesizers with virtual listeners}
+\title{Make your own audience, virtual listeners can filter generated drum programs}
+\title{Using AI to filter through millions of synthesizer programs to find some drums}
+\title{Finding the drum in the haystack: Using AI Listeners to filter through millions of generated drums}
+\title{Program Generation and AI listeners to search for drum synthesizers}
+\title{Intersecting AI listener and program generation to find drum synthesizers}
+\title{Percussive Synthesizer Program Generation via AI Listening}
+\title{Make Your Own Audience, Virtual Listeners Can Filter Generated Drum Programs}
 
 % a short form should be given in case it is too long for the running head
-\titlerunning{Percussive Synth. Generation}
+\titlerunning{Make Your Audience}
 
@@
 However, we cannot quantify the novelty of these sounds.
-
+\section{Datasets}
+We curated 3 databases of one-shot drums which we can use to train drum classifiers.
+\textbf{FreeDB} contains 5 categories: kicks, snares, claps, hats and other(various percussions).
+\textbf{RadarDB} contains 7 categories: kicks, snares, claps, hats, shakers, toms and rims.
+\textbf{MixedDB} contains 8 categories: kicks, snares, claps, high toms, low toms, medium toms, closed hats and open hats.
+See Appendix~\ref{appendix:datasets} for details and download links.
  \begin{figure}[tbp]
@@
 It then classifies sounds by drum category.
-Our goal is not realism; We want the virtual ear to accept novel and unusual drum sounds.
+Our goal is to produce a virtual ear that accurately discriminates between percussive and non-percussive sounds, but is tolerant of novelty.
 The virtual ear makes two critical decisions:
@@
  }
-
  \begin{figure}[tbp]
@@
 This issue is reflective of the open set recognition (OSR) problem~\cite{geng2020recent,mundt2019open}.
-We use figure~\ref{fig:ven_data} to highlight a number of caveats with our training approach: We denote $\mathcal{N}$ as the set of percussive sounds a synthesizer is capable of making.
-$\mathcal{T^{+}}$, our positive examples, is a set of one-shot drum sounds (see Appendix~\ref{appendix:datasets} for details about our datasets).
-During the hearing test, the virtual ear continually receives synthesizer noises for classification.
-The set of received noises is denoted as $\mathcal{H}$.
-The performance of the ear is measured by its precision and recall in finding the overlap between $\mathcal{H}$ and $\mathcal{N}$.
-It is important to ensure that the change in domains---particularly with the case of positive examples of percussive sounds---does not interfere with transformation of knowledge from the training of the ear to the hearing test.
-To maximize the transference of knowledge from one domain to another, we seek to learn from agnostic feature sets that capture fundamental characteristics of the data points.
-\subsection{Feature Extraction}
+We use Figure~\ref{fig:ven_data} to highlight a number of caveats with our training approach.
+If the sound is deemed percussive, the virtual ear makes \descsecond~by finding the best drum category for the sound.
+The number of categories available is dependent on the database of drums used for training.
+To maximize the transference of knowledge from training the classifiers to evaluation of programs, we need to extract concise feature sets that capture fundamental characteristics of the data points.\\
+In order to classify sounds, we need to summarize them as features.
 Various works have demonstrated effective reconstruction of signals given their Short-time Fourier Transforms (STFT)~\cite{nawab1983signal,griffin1984signal}.
@@
 We defined 3 STFT transformation functions which we believe to capture important, unique attributes of percussive sounds.
+
+\begin{enumerate}
+\item Envelope Transformation: Represents changes in loudness for the duration of the signal.
+Using STFT we generate a matrix $M_{i \times j}$ with rows $i$ and columns $j$ corresponding to time steps and frequency bins.
+Values $v_{i \times j}$ indicate the magnitude of the frequency bin $j$ at each time-step $i$.
+We approximate the envelope of the signal by summing the values of $M$ for at time-step (or row $i$).
+\item Frequency Transformation:  The calculation of this feature vector is similar to the envelope, but the summation is done along the frequency axis.
+Shorter hop-sizes and wider windows were used to increase frequency resolution.
+\item Spectrum Transformation: Mel Scaled STFT with its values normalized from 0-1. 
+\end{enumerate}
+Another set of features were extracted using the latent embeddings of autoencoder networks.
+We trained a number of autoencoders for the task of encoding and decoding spectrogram transformation of drum sounds, and used decoding loss to measure their performance (see Appendix~\ref{appendix:hyperparam}).
+Latent embeddings at the bottleneck layer of our best spectrogram autoencoder are used as features for sound categorization.
+As a sanity check for this approach, we trained our best autoencoder using 80\% of the drums in MixedDB.
+Latent encodings of the remaining 20\% and 1000 Noise sounds were projected onto a 2 or 3-dimensional planes using t-SNE.
+We implemented interactions for our projection graphs (see Appendix~\ref{appendix:tsne}) so the sounds associated with plot points can be listened to.
+Hearing tests revealed a noticeable, positive correlation between a synthetic sound's distance and similarity to drum clusters.
+
+Two groups of synthetic ears are implemented: \emph{two phased ears} (TPEs) and \emph{Mixed Ear Models} (MEMs).
+
+TPEs combine different stand-alone models specializing in~\descfirst or~\descsecond~and are trained only with our FFT features.
+To train TPEs for \descfirst, we use all drums in RadarDB and FreeDB (categories do not matter).
+For the~\descsecond, we combine the two databases and merge toms into kicks.
+Rims and shakers are merged with FreeDB's \enquote{other} category.
+MEMs are trained with autoencoder embeddings and envelope features and give simultaneous answers to both decisions.
+MEMs are trained with with the kicks, snares, claps and hat sounds from RadarDB and FreeDB.
+
+%  Our best TPE models achieve 82\% accuracy in a 6-way drum categorization task and 98\% accuracy in separation of drums from non-drum sounds.
+Our best MEM achieves 91\% accuracy in a 4 way drum categorization task and 99\% accuracy in separation of drums from non-drums.
+Detailed measurements can be found in Appendix~\ref{appendix:classifier_definitions}.
+
 \begin{figure}[tbp]
@@
 \end{figure}
-\begin{enumerate}
-\item Envelope Transformation: Represents changes in loudness for the duration of the signal.
-Using STFT we generate a matrix $M_{i \times j}$ with rows $i$ and columns $j$ corresponding to time steps and frequency bins.
-Values $v_{i \times j}$ indicate the magnitude of the frequency bin $j$ at each time-step $i$.
-We approximate the envelope of the signal by summing the values of $M$ for at time-step (or row $i$).
-\item Frequency Transformation:  The calculation of this feature vector is similar to the envelope, but the summation is done along the frequency axis.
-Shorter hop-sizes and wider windows were used to increase frequency resolution.
-\item Spectrum Transformation: Mel Scaled STFT with its values normalized from 0-1. 
-\end{enumerate}
-% Our transformations are GPU based, allowing their application in tandem with the training of the classifier or tuning of STFT transformation during hyper-paramter optimization (see Appendix~\ref{appendix:hyperparam}).
-Another set of features were extracted using the latent embeddings of autoencoder networks.
-We trained a number of autoencoders for the task of encoding and decoding spectrogram transformation of drum sounds, and used decoding loss to measure their performance (see appendix~\ref{appendix:hyperparam}).
-Latent embeddings at the bottleneck layer of our best spectrogram autoencoder are used as features for sound categorization.
-As a sanity check for this approach, we trained our best autoencoder using 80\% of the drums in MixedDB.
-Latent encodings of the remaining 20\% and 1000 Noise sounds were projected onto a 2 or 3-dimensional planes using t-SNE.
-We implemented interactions for our projection graphs (see Appendix~\ref{appendix:tsne}) so the sounds associated with plot points can be listened to.
-Hearing tests revealed a noticeable, positive correlation between a synthetic sound's distance and similarity to drum clusters.
-\subsection{Ear Types}
-\label{classifiers}
-Two groups of synthetic ears are implemented: \emph{two phased ears} (TPEs) and \emph{Mixed Ear Models} (MEMs).
-TPEs combine different models specializing in ~\descfirst or ~\descsecond~ and are trained only with our FFT features.
-MEMs are trained with autoencoder embeddings and envelope features and give simultaneous answers to both questions.
-Our best TPE models achieve 82\% accuracy in a 6-way drum categorization task and 98\% accuracy in separation of drums from non-drum sounds.
-Our best MEM achieves 91\% accuracy in a 4 way drum categorization task and 99\% accuracy in separation of drums from non-drums.
-Further specifications and detailed measurements for TPE and MEMs can be found in Appendix~\ref{appendix:classifier_definitions}.
 \section{Pipelines and Surveys}
@@
 We also repeat the hyper-parameter optimization step where no changes appeared necessary except for a reduction in the number of neighbors for the K-Neighbor model (from 30 to 5).
-As show in in figures~\ref{fig:f1_allg_box} and~\ref{fig:f1_dvn_box}, the addition of envelope features had a positive effect on performance for all mdoels, yet the RandomForest and ExtraTrees models clearly outperform the other classifiers in both tasks.
-We train the top two models on \%80 of our database and use the remaining \%20 to create the confusion matrices and the F-Scores shown in figures~\ref{fig:conf_f1_dvn}.
+As show in in Figures~\ref{fig:f1_allg_box} and~\ref{fig:f1_dvn_box}, the addition of envelope features had a positive effect on performance for all mdoels, yet the RandomForest and ExtraTrees models clearly outperform the other classifiers in both tasks.
+We train the top two models on \%80 of our database and use the remaining \%20 to create the confusion matrices and the F-Scores shown in Figures~\ref{fig:conf_f1_dvn}.
 \begin{figure}[h!]   

### 2020-08-22 templates_aimusic2020/paper.tex
Updates from Overleaf

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newcommand{\descfirst}{\textit{Descision.1~}}
-\newcommand{\descsecond}{\textit{Descision.2}}
+\newcommand{\decfirst}{\textit{Decision.1}}
+\newcommand{\decsecond}{\textit{Decision.2}}
 
@@
 \usepackage{comment}
-
+\usepackage{multirow}
 \newcommand{\keywords}[1]{\par\addvspace\baselineskip
@@
 \title{Percussive Synthesizer Program Generation via AI Listening}
-\title{Make Your Own Audience, Virtual Listeners Can Filter Generated Drum Programs}
+\title{Make Your Own Audience: Virtual Listeners Can Filter Generated Drum Programs}
 
@@
 More recent work by Yee-King et al.~\cite{yee2018automatic} used Long short-Term Memory (LSTM) models and heuristic search to find the exact parameters used to create a group of sounds.
-The sounds approximated were made by the same virtual synthesizer and not with an external source, making the eventual replication certain even with random search.
-Yet another recent work by Esling et al.
-used a large dataset of over 10,000 presets for a commercial VST synthesizer to learn a latent parameter space which can be sampled for creation of new audio~\cite{esling2019universal}.
+The sounds approximated were made by the same virtual synthesizer and not with an external source.
+Esling et al.
+used  over 10,000 a VST synthesizer's presets to learn a parameter space which can be sampled for creation of new audio~\cite{esling2019universal}.
 Here, we work towards the approximation of percussive sounds with no previous knowledge about the sonic capabilities of a virtual synthesizer.
@@
 We call the number of submodules in each virtual synthesizer the \textit{stack size}.
-We call the sets of parameter values that characterize a synthesizer's submodules a \textit{program} (analogous to presets and submodules for a VST).
- Rather than using probabilistic neural nets for sound synthesis, we generate programs for this virtual synthesizer Our decision is based on the following factors:
-\begin{itemize}
+We call the sets of parameter values that characterize a synthesizer's submodules a \textit{program} (analogous to presets and submodules for a VST).\\
+
+ Rather than directly using neural networks for sound synthesis, we generate programs for this virtual synthesizer. Our decision is based on the following factors:
+\begin{enumerate*}[label=(\roman*)]
     \item \textit{Novelty and Creativity}: Given large sets of examples, generative models such as VAEs and GANS have proven capable of generating samples similar to the exemplars.
@@
 Their highly recursive structure makes modern explanation methods such as saliency maps unreliable~\cite{rudin2019stop}.
-    \item \textit{Speed of Rendering at high sampling rates}: Neural network synthesis is costly.
+    \item \textit{Speed of Rendering }: Neural network synthesis is costly.
 Sub 24 khz sampling rates are common in most works~\cite{yamamoto2020parallel,oord2017parallel,aouameur2019neural,ramires2020neural}.
@@
 The added footprint of increasing the length of rendered sounds or higher sampling rates is relatively minuscule.
-\end{itemize}
+\end{enumerate*}
 
@@
 Each Synthesizer contains 1 or more these submodules.
+Synthesizer programs set the number of these submodules and their parameters.
 The output of a synthesizer is the normalized addition of all its submodule outputs.
-Each synthesizer program determines the number of these submodules and their parameters.
     }
@@
 $\mathcal{H}$ is a series of sounds sent to the ear for classification.
-Not to scale (true scales are not measurable and/or subjective).
     }
@@
 \end{figure}
-\descfirst requires knowledge of what drums \textbf{do not} sound like, or knowledge of an infinitely large set, which cannot be fully represented via examples.
+\decfirst~requires knowledge of what drums \textbf{do not} sound like, or knowledge of an infinitely large set, which cannot be fully represented via examples.
 An important consideration is that the source of sounds used in training the model (organic drum sounds) will be fundamentally different from the source of unlabeled sounds we wish to categorize (noise from a synthesizer).
@@
 We use Figure~\ref{fig:ven_data} to highlight a number of caveats with our training approach.
-If the sound is deemed percussive, the virtual ear makes \descsecond~by finding the best drum category for the sound.
+If the sound is deemed percussive, the virtual ear makes \decsecond~by finding the best drum category for the sound.
 The number of categories available is dependent on the database of drums used for training.
 To maximize the transference of knowledge from training the classifiers to evaluation of programs, we need to extract concise feature sets that capture fundamental characteristics of the data points.\\
+
 In order to classify sounds, we need to summarize them as features.
@@
 Using STFT we generate a matrix $M_{i \times j}$ with rows $i$ and columns $j$ corresponding to time steps and frequency bins.
-Values $v_{i \times j}$ indicate the magnitude of the frequency bin $j$ at each time-step $i$.
-We approximate the envelope of the signal by summing the values of $M$ for at time-step (or row $i$).
-\item Frequency Transformation:  The calculation of this feature vector is similar to the envelope, but the summation is done along the frequency axis.
-Shorter hop-sizes and wider windows were used to increase frequency resolution.
-\item Spectrum Transformation: Mel Scaled STFT with its values normalized from 0-1. 
+Values $v_{i \times j}$ indicate the magnitude of frequency bin $j$ at each time-step $i$.
+We approximate the envelope of the signal by summing the values of $M$ at each time-step.
+\item Frequency Transformation:  Similar to envelope calculation, but the summation is done along the frequency axis. Shorter hop-sizes and wider windows were used to increase frequency resolution. 
+\item Spectrum Transformation: Mel Scaled STFT with values normalized from 0-1. 
 \end{enumerate}
@@
 
-Two groups of synthetic ears are implemented: \emph{two phased ears} (TPEs) and \emph{Mixed Ear Models} (MEMs).
+To automatically learn from the described features, two groups of synthetic ears are implemented: \emph{two phased ears} (TPEs) and \emph{Mixed Ear Models} (MEMs).
+We train multiple neural network architectures using different subsets of the FFT features to specialize in \decfirst~ or \decsecond~.
+Our design of TPE ears allows a combination of these networks to make sequential decisions.
+To train TPEs for \decfirst, we use all drums in RadarDB and FreeDB (categories do not matter).
+To learn \enquote{not-drums}, TPEs are given 6000 examples of synthesized noise.
+For \decsecond, we combine the two databases and merge toms into kicks and rims/shakers into \enquote{other}.
+We designed and trained a number of neural net architectures with 80\% of this dataset.
+Using the remaining 20\% of sounds, we achieved 98\% accuracy in \decfirst~and 82\% accuracy in~\decsecond.
+Our best models both utilize convolutional neural net (CNN) layers that learn from spectrogram data.
+These accuracy numbers are weak as we did not account for category sizes or cross validate.
 
-TPEs combine different stand-alone models specializing in~\descfirst or~\descsecond~and are trained only with our FFT features.
-To train TPEs for \descfirst, we use all drums in RadarDB and FreeDB (categories do not matter).
-For the~\descsecond, we combine the two databases and merge toms into kicks.
-Rims and shakers are merged with FreeDB's \enquote{other} category.
-MEMs are trained with autoencoder embeddings and envelope features and give simultaneous answers to both decisions.
-MEMs are trained with with the kicks, snares, claps and hat sounds from RadarDB and FreeDB.
-
-%  Our best TPE models achieve 82\% accuracy in a 6-way drum categorization task and 98\% accuracy in separation of drums from non-drum sounds.
-Our best MEM achieves 91\% accuracy in a 4 way drum categorization task and 99\% accuracy in separation of drums from non-drums.
-Detailed measurements can be found in Appendix~\ref{appendix:classifier_definitions}.
-
+MEMs learn from autoencoder embeddings and envelope features and give simultaneous answers to both decisions.
+We use kicks, snares, claps, and hat sounds from RadarDB and FreeDB to train MEMs.
+MEMs are given 1000 examples of synthesized noise.
+Using 10-fold cross validation, our best MEM (an ExtraTrees Classifier) achieves the average f1-score of 92\% in a 5 way sound classification (4 drum categories + synthesizer noise).
+This MEM makes both decisions together.
+Although never used, we achieved an average f1-score of 99\% after grouping drums together.
+Detailed measurements and model descriptions for TPEs and MEMs can be found in Appendix~\ref{appendix:classifier_definitions}.
 \begin{figure}[tbp]
@@
 \end{figure}
-\section{Pipelines and Surveys}
-\label{surveys}
 
-\begin{comment}
-% AH: THIS TABLE IS COMMENTED OUT
-\begin{table}[h!]
-  \begin{tabular}{|c | c | c | c | c | c | c|} 
+\section{Building and Evaluating The System}
+% Please add the following required packages to your document preamble:
+% \usepackage{multirow}
+\begin{table}[]
+\centering
+\begin{tabular}{|c|c|c|c|c|c|c|c|}
 \hline
-  Drop Rule & Size & H+H & H+FC & H+CNN & H+E/F & 3 models \\ [0.5ex] 
-  \hline
-  No Drops & 257 &0.37 & 0.35 & 0.36 & 0.36 & 0.28\\ 
-  \hline
-  Assigned \enquote{Bad} By Both & 236 & 0.31 & 0.37 & 0.37 & 0.38 & 0.30 \\
-  \hline
-  Assigned \enquote{Bad} By Either & 180 & 0.47 & 0.50 & 0.48 & 0.48 &  0.34 \\
-  \hline
-  Assigned \enquote{Bad} or \enquote{Other} By Either & 154 & 0.47 & 0.59 & 0.54 & 0.50 &  0.35 \\
-  \hline
+Ear Type / System Name & Drop Rule         & Size & HvH  & H+FC & H+CNN & H+E/F & H+MEM \\ \hline
+\multirow{2}{*}{TPE} & No Drops          & 257  & 0.37 & 0.35 & 0.36  & 0.36  &       \\ \cline{2-8} 
+                     & Bads and Others   & 154  & 0.47 & 0.59 & 0.54  & 0.50  &       \\ \hline
+\multirow{2}{*}{MEM} & No Drops          & 300  & 0.34 &      &       &       & 0.25  \\ \cline{2-8} 
+                     & All Bad and Other & 120  & 0.62 &      &       &       & 0.59  \\ \hline
 \end{tabular}
- \caption{\label{kappa_table_TPE}Table of Fleiss' kappa coefficient to measure the degree of agreement between persons (H+H), persons with FC model (H+FC), persons with CNNLSTM model, persons with all models (H+E/F), and between the 3 models.
-} % AH: Which decision is this?
+
+\caption{Fleiss’ kappa coefficients as a measurement of agreement between persons (H+H) and persons with models.  }
 \end{table}
-\end{comment}
-
-\begin{table}[h!]
-  \begin{tabular}{|c | c | c | c | c | c | c|} 
-  \hline
-  \emph{Decision.1}\\
-  \hline
-  Drop Rule & Size & H+H & H+FC & H+CNN & H+E/F & 3 models \\ [0.5ex] 
-  \hline
-  No Drops & 257 &0.37 & 0.35 & 0.36 & 0.36 & 0.28\\ 
-  \hline
-  Assigned \enquote{Bad} By Both & 236 & 0.31 & 0.37 & 0.37 & 0.38 & 0.30 \\
-  \hline
-  Assigned \enquote{Bad} By Either & 180 & 0.47 & 0.50 & 0.48 & 0.48 &  0.34 \\
-  \hline
-  Assigned \enquote{Bad} or \enquote{Other} By Either & 154 & 0.47 & 0.59 & 0.54 & 0.50 &  0.35 \\
-  \hline
-  \emph{Decision.2}\\
-  \hline
-  Drop Rule & Size & H+H & H+MEM \\
-  \hline
-  No Drop & 300 & 0.34 & 0.25\\ 
-  \hline
-  Assigned Bad By Both & 249 & 0.20 & 0.26 \\
-  \hline
-  Assigned Bad By Either & 151 & 0.46 &  0.47 \\
-  \hline
- Assigned \enquote{Bad} or \enquote{Other} By Either  & 120 & 0.62   &  0.59 \\
- \end{tabular}
- \caption{\label{kappa_table_TPE}Table of Fleiss' kappa coefficient to measure the degree of agreement between persons (H+H), persons with FC model (H+FC), persons with CNNLSTM model, persons with all models (H+E/F), and between the 3 models.
- Table of Fleiss' kappa coefficient to measure the degree of agreement between persons (H+H) and persons with MEM (H+MEM)
- } % AH: Which decision is this?
- \end{table}
-
-%  \begin{table}[h!]
-%  \begin{tabular}{|c| p{2cm} | p{2cm}| p{2cm}|} 
-%  \hline
-%  Drop Rule & Size & H+H & H+MEM \\
-%  \hline
-%  No Drop & 300 & 0.34 & 0.25\\ 
-%  \hline
-%  Assigned Bad By Both & 249 & 0.20 & 0.26 \\
-%  \hline
-%  Assigned Bad By Either & 151 & 0.46 &  0.47 \\
-%  \hline
-% Assigned \enquote{Bad} or \enquote{Other} By Either  & 120 & 0.62   &  0.59 \\
-%  \hline
-% \end{tabular}
-% \caption{\label{kappa_table_MEM}Table of Fleiss' kappa coefficient to measure the degree of agreement between persons (H+H) and persons with MEM (H+MEM).}
-% \end{table}
 High accuracy in detection of drums vs not-drums does not necessarily make an ear more suitable for our generative system.
 Perfect detection of drums vs not-drums would create a system which generates nothing.
-We cannot know the true size of $\mathcal{H^{+}}$ without exhaustive manual hearing tests.
-We conduct small-scale (~300 each) manual hearing tests of two generative systems.
-The TPE system uses CNNLSTM-DVN for \descfirst, and FC-DVD, CNNLSTM-DVD and E/F for \descsecond.
+We cannot know the true size of $\mathcal{H^{+}}$ (see Figure~\ref{fig:ven_data}) without exhaustive manual hearing tests.
+We conduct manual hearing tests of two generative systems.
+For \decfirst, a network which learns from spectrogram data utilizing CNN and LSTM layers is used.
+For \decsecond, we categorize the drum types with 3 different models: FC (Fully-Connected architecture and spectrograms for learning), CNN (CNN and LSTM layers with spectrograms), and E/F (Fully-Connected architecture with frequency and envelope features).
 The MEM system uses our best MEM, which simultaneously classifies sounds as drums and categorizes them.
+
 The TPE system produces samples in the following categories: \enquote{snare}, \enquote{kick}, \enquote{hat}, \enquote{clap} and \enquote{other} (combination of rims, shakers and unusual percussive sounds).
@@
 Additionally, each responder has the option of labeling samples as \enquote{bad} for samples that they deemed not percussive.
-The percentage of sounds labeled as \enquote{bad} by the authors is a measurement of success with regards to \descfirst.
-We measure success with regards to \descsecond---the reliability of agreement between persons and drum categorization models---via the Fleiss' kappa coefficient \cite{fleiss1971measuring}.
+
+The percentage of sounds labeled as \enquote{bad} by the authors is a measurement of success with regards to \decfirst.
+We measure success with regards to \decsecond---the reliability of agreement between persons and drum categorization models---via the Fleiss' kappa coefficient \cite{fleiss1971measuring}.
 The value of 0 or less for this coefficient indicates no agreement beyond random chance, and the values of 1 indicates perfect agreement.
-\\
-% We again measure this coefficient after dropping samples that were categorized as \enquote{bad} by one or both authors, and after after dropping all \enquote{bad} and \enquote{other} samples.
+We re-measure this coefficient after dropping all \enquote{bad} and \enquote{other} samples.
+
 The majority of sounds created by our system are deemed percussive by both surveyors.
 30\% of the outputs from the TPE system and 50\% of the MEM system outputs are deemed as non-percussive by at least one person.
-This leaves much room for improvement with regards to~\descfirst.
-Our performance with regards to ~\descsecond~ is promising as we achieve moderately high agree-ability scores after dropping bad sounds.
-Despite the drawbacks, the MEM pipeline remains competitive while working with a fraction of
-the features to learn from and simultaneously making both decisions.
-
-% Suggesting that latent representations of autoencoder networks can be used as general,low-dimensional proxies for representation of complex inputs.
+This leaves much room for improvement with regards to~\decfirst.
+Our performance with regards to ~\decsecond~ is promising as we achieve moderately high agree-ability scores after dropping \enquote{bad sounds} and \enquote{other}.
+Despite the drawbacks, the MEM pipeline remains competitive while working with a fraction of the features to learn from and simultaneously making both decisions.
+Extended survey analysis is provided in Appendix~\ref{appendix:surveys}.
+Appendix~\ref{appendix:datasets} provides access to generated sounds.
 
 \section{Conclusion, Validity, and Future Work}
-\textbf{Conclusion:} We successfully built a generative system for creation of percussive sounds via automatic programming of virtual synthesizers.  
+
+\textbf{Conclusion:} We successfully built generative systems for creation of percussive sounds via automatic programming of virtual synthesizers. verified its results with human listeners.
 Our work enables not only the creation of new libraries of percussion sounds, but new synthesizer programs which can be modified and studied. 
@@
 We had some success in our utilization of latent representations of autoencoder networks as low-dimensional representations of short sound files.
-\\
+
 \textbf{Threats to Validity:} The lack of consistency in training and accuracy measurements makes comparisons between TPEs and MEMs difficult.
-We made many arbitrary design decisions, particularly in the design of our TPE classifiers and selection of datasets for training and testing.
-We sought to enable creative exploration by generation of sounds with limited resources, yet cannot verify or quantify the novelty of our results.
-Without an effective few-shot learning method, our requirement for training data remains high.\\
-\textbf{Future Work:} In future works, we seek to improve our virtual ear with state of the art few-shot learning models.
-Our design allows easy integration of heuristic search, an improvement we aim to make in future works.
-Our systems also allows easy experimentation with other synthesis and virtual listening methods, this may involve generation of other categories of instruments.
-We consider the integration of our system with the VST protocol a long term goal.
+Many arbitrary design decisions have been made, particularly in the design of our TPE classifiers and selection of datasets for training and testing.
+We cannot quantify the novelty of our results.
+Our requirement for training data remains high.
+
+\textbf{Future Work:} Effective implementation of few-shot learning is a priority.
+Program generation can be improved by reinforcement learning and other heuristics.Effective implementation of few-shot learning is a priority.
+Program generation can be improved by reinforcement learning and other heuristics.
 
@@
 \label{appendix:datasets}
-\subsection{Download Insturctions}
+\subsection{Download Instructions}
 FreeDB, survey data, and randomly generated sounds can be downloaded from: \url{https://zenodo.org/record/3994999}\\
@@
 The scripts used to download and process royalty free samples are also made available.
-Further information about downloading our dataset can be found on the project's github page.
 
@@
 \end{table}
-
-%=============
+%==========================
 \chapter{Audio Transformation Functions}
@@
 Its structure is the combination of a CNN with 2 output channels and kernel size $(7,3)$; Followed by an LSTM model of hidden size 800 and a fully connected layer of size 20x2.
-\item E/F-DVD: A fully connected model trained on a concatenation of envelope and frequency features. Reaching 80\% accuracy for 6-way drum categorization in Phase 2. Size of 50x10x2x6.
+\item E/F-DVD: A fully connected model trained on a concatenation of envelope and frequency features. Reaching 80\% accuracy for 5-way drum categorization in Phase 2. Size of 50x10x2x6.
 \item CNN-DVD: A CNN model trained on Spectrum features.
-Reaching 82\% accuracy in a 6-way drum categorization in Phase 2.
+Reaching 82\% accuracy in a 5-way drum categorization in Phase 2.
 A combination of a CNN model with output channel size of 4, kernel of size of 5, another CNN model with output channel size of 8 and kernel of size 3.
 Followed by a fully connected network of shape 100x20x6.
-\item FC-DVD: Fully connected 3 layer neural net with 78\% accuracy for 6-way drum categorization in Phase 2. Size of 400x200x50.
+\item FC-DVD: Fully connected 3 layer neural net with 78\% accuracy for 5-way drum categorization in Phase 2. Size of 400x200x50.
 \end{enumerate}
@@
 \label{appendix:surveys}
-\subsubsection{TPE Survey of 257 Samples:}
-\begin{itemize}
-    \item With 6 categorization groups, responders had the same categorization in 47\% of cases.
-    \item The agreement between the responders and AVG was 44\% and 47\%.
-    \item Of 257 samples, the responders agreed with FC, CNNLSTM and E/F respectively in 78, 76, and 46 of cases.
+\begin{table}[h!]
+  \begin{tabular}{|c | c | c | c | c | c | c|} 
+  \hline
+  Drop Rule & Size & H+H & H+FC & H+CNN & H+E/F & 3 models \\ [0.5ex] 
+  \hline
+  No Drops & 257 &0.37 & 0.35 & 0.36 & 0.36 & 0.28\\ 
+  \hline
+  Assigned \enquote{Bad} By Both & 236 & 0.31 & 0.37 & 0.37 & 0.38 & 0.30 \\
+  \hline
+  Assigned \enquote{Bad} By Either & 180 & 0.47 & 0.50 & 0.48 & 0.48 &  0.34 \\
+  \hline
+  Assigned \enquote{Bad} or \enquote{Other} By Either & 154 & 0.47 & 0.59 & 0.54 & 0.50 &  0.35 \\
+  \hline
+ \end{tabular}
+ \caption{\label{kappa_table_TPE}Table of Fleiss' kappa coefficient to measure the degree of agreement between persons (H+H), persons with FC model (H+FC), persons with CNNLSTM model, persons with all models (H+E/F), and between the 3 models.
+} % AH: Which decision is this?
+ \end{table}
+\begin{table}[h!]
+ \begin{tabular}{|c| p{2cm} | p{2cm}| p{2cm}|} 
+ \hline
+ Drop Rule & Size & H+H & H+MEM \\
+ \hline
+ No Drop & 300 & 0.34 & 0.25\\ 
+ \hline
+ Assigned Bad By Both & 249 & 0.20 & 0.26 \\
+ \hline
+ Assigned Bad By Either & 151 & 0.46 &  0.47 \\
+ \hline
+Assigned \enquote{Bad} or \enquote{Other} By Either  & 120 & 0.62   &  0.59 \\
+ \hline
+\end{tabular}
+\caption{\label{kappa_table_MEM}Table of Fleiss' kappa coefficient to measure the degree of agreement between persons (H+H) and persons with MEM (H+MEM).}
+\end{table}
+% \subsubsection{TPE Survey of 257 Samples:}
+% \begin{itemize}
+%     \item With 6 categorization groups, responders had the same categorization in 47\% of cases.
+%     \item The agreement between the responders and AVG was 44\% and 47\%.
+%     \item Of 257 samples, the responders agreed with FC, CNNLSTM and E/F respectively in 78, 76, and 46 of cases.
 The loss of spectrum data is likely the cause of E/F model's noticeably worse performance.
-    \item The survey brings into question the reliability of our phase 1 model, as 30\% of the generated samples were deemed not percussive by at least 1 reviewer and 8\% by both reviewers
-    \item The task of categorizing synthetic drums is difficult.
+%     \item The survey brings into question the reliability of our phase 1 model, as 30\% of the generated samples were deemed not percussive by at least 1 reviewer and 8\% by both reviewers
+%     \item The task of categorizing synthetic drums is difficult.
 Survey shows that the scale of agreement within persons as well as between persons and various model combinations is moderate at best, even after removal of \enquote{bad} samples.
 While the same models can easily achieve 98+ percent accuracy when tested on sounds from physical drum samples.
-    \item While there is much room for improvement, our pipelines can generate and categorize drums and percussive sounds with a promising degree of success. 
-\end{itemize}
+%     \item While there is much room for improvement, our pipelines can generate and categorize drums and percussive sounds with a promising degree of success. 
+% \end{itemize}
 

### 2020-08-22 templates_aimusic2020/paper.tex
final...

@@
 Yet unique drum sounds can be difficult or expensive to find.
-By relying on recordings of \textit{real life} drum sounds, artists are limited by what instruments exist in the real world and whether or not high-quality, one-shot recordings can be accessed.
-We believe automatic programming of virtual synthesizers for the creation of novel drum sounds can alleviate these material limitations.
+By relying on recordings of material drum sounds, artists are limited by what instruments exist in the material world and whether or not high-quality, one-shot recordings can be accessed.
+We believe automatic programming of virtual synthesizers for the creation of novel drum sounds can alleviate these limitations.
 To this end, we implement a programmable virtual synthesizer of audio, which we call the \emph{virtual synthesizer}.
@@
 \section{Datasets}
-We curated 3 databases of one-shot drums which we can use to train drum classifiers.
-\textbf{FreeDB} contains 5 categories: kicks, snares, claps, hats and other(various percussions).
+We curated 3 databases of one-shot drums which we use to train drum classifiers.
+\textbf{FreeDB} contains 5 categories: kicks, snares, claps, hats and other (various percussions).
 \textbf{RadarDB} contains 7 categories: kicks, snares, claps, hats, shakers, toms and rims.
@@
 In early 2000s, Interactive Genetic Algorithms (IGA's) were utilized for the generation of new sounds with various sound-engines~\cite{johnson1999exploring,dahlstedt2001creating}.
-More recent work by Yee-King et al.~\cite{yee2018automatic} used Long short-Term Memory (LSTM) models and heuristic search to find the exact parameters used to create a group of sounds.
+A more recent work by Yee-King et al.~\cite{yee2018automatic} used Long short-Term Memory (LSTM) models and heuristic search to find the exact parameters used to create a group of sounds.
 The sounds approximated were made by the same virtual synthesizer and not with an external source.
@@
 used  over 10,000 a VST synthesizer's presets to learn a parameter space which can be sampled for creation of new audio~\cite{esling2019universal}.
-Here, we work towards the approximation of percussive sounds with no previous knowledge about the sonic capabilities of a virtual synthesizer.
+Here, we work towards the approximation of percussive sounds with no prior knowledge about the sonic capabilities of a synthesizer.
 
@@
 \end{table}
- We need digital synthesizers to create sounds.
+To create sounds, we need digital synthesizers.
 We use classical DSP to build our synthesizer, which allows for quick, offline, and parallel generation of audio signals without the usage of GPUs.
@@
 We call the number of submodules in each virtual synthesizer the \textit{stack size}.
-We call the sets of parameter values that characterize a synthesizer's submodules a \textit{program} (analogous to presets and submodules for a VST).\\
+We call the sets of parameter values that characterize a synthesizer's submodules a \textit{program} (analogous to presets and submodules for a VST).
+ \begin{figure}[tbp]
+    \begin{center}
+    % \textbf{Synthesizer SubModule }
+    \makebox[\textwidth]{
+    \fbox{\includegraphics[width=1\linewidth]{templates_aimusic2020/images/synthesizer_block.pdf}}}
+    \end{center}
+    \caption{High level representation of pre-rendering steps for each submodule.
+Each Synthesizer contains 1 or more these submodules.
+Synthesizer programs set the number of these submodules and their parameters.
+The output of a synthesizer is the normalized addition of all its submodule outputs.
+    }
+\label{fig:submodule}
+\end{figure}
 
@@
 Their highly recursive structure makes modern explanation methods such as saliency maps unreliable~\cite{rudin2019stop}.
-    \item \textit{Speed of Rendering }: Neural network synthesis is costly.
+    \item \textit{Speed of Rendering}: Neural network synthesis is costly.
 Sub 24 khz sampling rates are common in most works~\cite{yamamoto2020parallel,oord2017parallel,aouameur2019neural,ramires2020neural}.
@@
 This makes the evaluation of a set of inputs (or parameters) to our synthesizers relatively simple.
-
- \begin{figure}[tbp]
-    \begin{center}
-    % \textbf{Synthesizer SubModule }
-    \makebox[\textwidth]{
-    \fbox{\includegraphics[width=1\linewidth]{templates_aimusic2020/images/synthesizer_block.pdf}}}
-    \end{center}
-    \caption{High level representation of pre-rendering steps for each submodule.
-Each Synthesizer contains 1 or more these submodules.
-Synthesizer programs set the number of these submodules and their parameters.
-The output of a synthesizer is the normalized addition of all its submodule outputs.
-    }
-\label{fig:submodule}
-\end{figure}
 
@@
 \decfirst~requires knowledge of what drums \textbf{do not} sound like, or knowledge of an infinitely large set, which cannot be fully represented via examples.
-An important consideration is that the source of sounds used in training the model (organic drum sounds) will be fundamentally different from the source of unlabeled sounds we wish to categorize (noise from a synthesizer).
+An important consideration is that the source of sounds used for training the model (organic drum sounds) will be fundamentally different from the source of unlabeled sounds we wish to categorize (noise from a synthesizer).
 This issue is reflective of the open set recognition (OSR) problem~\cite{geng2020recent,mundt2019open}.
@@
 The number of categories available is dependent on the database of drums used for training.
-To maximize the transference of knowledge from training the classifiers to evaluation of programs, we need to extract concise feature sets that capture fundamental characteristics of the data points.\\
+To maximize the transference of knowledge gained from training the classifiers to evaluation of programs, we need to extract concise feature sets that capture fundamental characteristics of the data points.\\
 
@@
 If the STFT of a signal can be used for its reconstruction, perhaps it can be utilized as a source of fundamental features.
-We defined 3 STFT transformation functions which we believe to capture important, unique attributes of percussive sounds.
+We defined 3 STFT (or FFT) transformation functions which we believe to capture important, unique attributes of percussive sounds.
 
@@
 MEMs are given 1000 examples of synthesized noise.
-Using 10-fold cross validation, our best MEM (an ExtraTrees Classifier) achieves the average f1-score of 92\% in a 5 way sound classification (4 drum categories + synthesizer noise).
+Using 10-fold cross validation, our best MEM (an ExtraTrees Classifier) achieves the average f1-score of 92\% in 5-way sound classification (4 drum categories + synthesizer noise).
 This MEM makes both decisions together.
@@
 
-\textbf{Conclusion:} We successfully built generative systems for creation of percussive sounds via automatic programming of virtual synthesizers. verified its results with human listeners.
+\textbf{Conclusion:} We successfully built a generative systems for creation of percussive sounds via automatic programming of virtual synthesizers. We verified its results with human listeners.
 Our work enables not only the creation of new libraries of percussion sounds, but new synthesizer programs which can be modified and studied. 
@@
 We had some success in our utilization of latent representations of autoencoder networks as low-dimensional representations of short sound files.
-
+\\
 \textbf{Threats to Validity:} The lack of consistency in training and accuracy measurements makes comparisons between TPEs and MEMs difficult.
@@
 Our requirement for training data remains high.
-
-\textbf{Future Work:} Effective implementation of few-shot learning is a priority.
-Program generation can be improved by reinforcement learning and other heuristics.Effective implementation of few-shot learning is a priority.
-Program generation can be improved by reinforcement learning and other heuristics.
+\\
+\textbf{Future Work:} Effective implementation of few-shot learning is a priority. Program generation can be improved by reinforcement learning and other heuristics.
 
@@
 \section{Two Phased models}
-Using the described features, we trained several neural network models for Phase 1 and 2 in the Pytorch environment.
-The task of Phase 1 is to separate drums from not-drums (DrumVsNotDrum, or DVN).
-The task of Phase 2 is to categorize drums and percussion (DrumVsDrum, or DVD).
+Using the described features, we trained several neural network models for  decision 1and 2 in the Pytorch environment.
+The task of decision 1 is to separate drums from not-drums (DrumVsNotDrum, or DVN).
+The task of decision 2 is to categorize drums and percussion (DrumVsDrum, or DVD).
 We kept our feature space small, making it viable for feature selection and model design to be done on a trial and error basis.
@@
 \begin {enumerate}
-\item FC-DVN: Fully connected network trained on Envelope features, reaching 97\% accuracy on our test data for Phase 1. With size of 10x5x10.
+\item FC-DVN: Fully connected network trained on Envelope features, reaching 97\% accuracy on our test data for decision1. With size of 10x5x10.
 \item CNNLSTM-DVN: A combination of CNN and LSTM models, where the CNN model extracts higher level features that are fed temporally to an LSTM cell.
@@
 Its structure is the combination of a CNN with 2 output channels and kernel size $(7,3)$; Followed by an LSTM model of hidden size 800 and a fully connected layer of size 20x2.
-\item E/F-DVD: A fully connected model trained on a concatenation of envelope and frequency features. Reaching 80\% accuracy for 5-way drum categorization in Phase 2. Size of 50x10x2x6.
+\item E/F-DVD: A fully connected model trained on a concatenation of envelope and frequency features. Reaching 80\% accuracy for 5-way drum categorization in decision2. Size of 50x10x2x6.
 \item CNN-DVD: A CNN model trained on Spectrum features.
-Reaching 82\% accuracy in a 5-way drum categorization in Phase 2.
+Reaching 82\% accuracy in a 5-way drum categorization in decision2.
 A combination of a CNN model with output channel size of 4, kernel of size of 5, another CNN model with output channel size of 8 and kernel of size 3.
 Followed by a fully connected network of shape 100x20x6.
-\item FC-DVD: Fully connected 3 layer neural net with 78\% accuracy for 5-way drum categorization in Phase 2. Size of 400x200x50.
+\item FC-DVD: Fully connected 3 layer neural net with 78\% accuracy for 5-way drum categorization in decision2. Size of 400x200x50.
 \end{enumerate}
-Unlike EE models, parameters are hand-picked and un-tuned.
-Higher accuracy rates in these models do not necessarily translate to higher agreeableness with surveyors.
-Since the positive sounds in the hearing test are sourced from a synthesizer, model accuracy on test data alone cannot be relied upon when the domain of sounds
-being categorized is switched.
+Parameters are hand-picked and un-tuned. 
 \subsection{Mixed Ear Models}
@@
 We use a combination of RadarDB, FreeDB and NoiseDB for training.
-We only focus on clap,hat,kick,snares, synthetic noise groups for measuring effectiveness to prevent class overlaps as much as possible.
+We only focus on clap,hat,kick,snares, and synthetic noise groups for measuring effectiveness to prevent class overlaps as much as possible.
 We also exclude samples longer than 1 second, to exclude potentially mislabeled data.
@@
 Before inter-model comparisons, we conducted a grid-search for each model on at least one of its possibly decisive hyper-parameters.
-The classifiers and other notable specifications are presented in table~\ref{table:mem_model_selection}.
+The classifiers and other notable specifications are presented in Table~\ref{table:mem_model_selection}.
 \begin{table}[t]

### 2020-08-22 templates_aimusic2020/paper.tex
Updates from Overleaf

@@
 To automatically learn from the described features, two groups of synthetic ears are implemented: \emph{two phased ears} (TPEs) and \emph{Mixed Ear Models} (MEMs).
-We train multiple neural network architectures using different subsets of the FFT features to specialize in \decfirst~ or \decsecond~.
+We train multiple neural network architectures using different subsets of the FFT features to specialize in \decfirst~or \decsecond~.
 Our design of TPE ears allows a combination of these networks to make sequential decisions.
@@
 The TPE system produces samples in the following categories: \enquote{snare}, \enquote{kick}, \enquote{hat}, \enquote{clap} and \enquote{other} (combination of rims, shakers and unusual percussive sounds).
-The MEM pipeline does not output the \enquote{other} category, yet the option is available to surveyors when categorizing sounds manually.
+The MEM system does not output the \enquote{other} category, yet the option is available to surveyors when categorizing sounds manually.
 Both authors categorized a subset of the results without knowledge of the assigned labels.
@@
 This leaves much room for improvement with regards to~\decfirst.
-Our performance with regards to ~\decsecond~ is promising as we achieve moderately high agree-ability scores after dropping \enquote{bad sounds} and \enquote{other}.
+Our performance with regards to \decsecond~is promising as we achieve moderately high agree-ability scores after dropping \enquote{bad sounds} and \enquote{other}.
 Despite the drawbacks, the MEM pipeline remains competitive while working with a fraction of the features to learn from and simultaneously making both decisions.
@@
 
-\textbf{Conclusion:} We successfully built a generative systems for creation of percussive sounds via automatic programming of virtual synthesizers. We verified its results with human listeners.
+\textbf{Conclusion:} We successfully built a generative system for creation of percussive sounds via automatic programming of virtual synthesizers. We verified its results with human listeners.
 Our work enables not only the creation of new libraries of percussion sounds, but new synthesizer programs which can be modified and studied. 
@@
 \end{tabular}
-\caption{A database put together by combination of radarDB, FreeDB and NoiseDB}
+\caption{A database put together by combination of RadarDB, FreeDB and NoiseDB}
 \label{db:memDB}

### 2020-08-22 templates_aimusic2020/paper.tex
Updates from Overleaf

@@
 \multirow{2}{*}{TPE} & No Drops          & 257  & 0.37 & 0.35 & 0.36  & 0.36  &       \\ \cline{2-8} 
-                     & Bads and Others   & 154  & 0.47 & 0.59 & 0.54  & 0.50  &       \\ \hline
+                     & All Bad and Other   & 154  & 0.47 & 0.59 & 0.54  & 0.50  &       \\ \hline
 \multirow{2}{*}{MEM} & No Drops          & 300  & 0.34 &      &       &       & 0.25  \\ \cline{2-8} 
@@
 \\
-\textbf{Future Work:} Effective implementation of few-shot learning is a priority. Program generation can be improved by reinforcement learning and other heuristics.
+\textbf{Future Work:} Effective implementation of few-shot learning is a priority. Program generation may be improved by reinforcement learning and other heuristics.
 
@@
 %======================
-\chapter{Datasets Details and Downloads}
+\chapter{Datasets, Details, and Downloads}
 \label{appendix:datasets}

### 2020-09-30 templates_aimusic2020/paper.tex
Updates from Overleaf
some writing errors corrected as pointed out by reviewers

@@
 \usepackage{multirow}
+\usepackage[T1]{fontenc}
 \newcommand{\keywords}[1]{\par\addvspace\baselineskip
@@
 Esling et al.
-used  over 10,000 a VST synthesizer's presets to learn a parameter space which can be sampled for creation of new audio~\cite{esling2019universal}.
+used  over 10,000 VST synthesizer presets to learn a parameter space which can be sampled for creation of new audio~\cite{esling2019universal}.
 Here, we work towards the approximation of percussive sounds with no prior knowledge about the sonic capabilities of a synthesizer.
@@
 Pitches(notes) & list of pitches &  range of C0(16.35hz) to B9 \\
-HP filter Cuttoff & 0-20000hz & -\\
-LP filter Cuttoff & 20000-HP & never lower than HP cutoff\\
+HP filter Cutoff & 0-20000hz & -\\
+LP filter Cutoff & 20000-HP & never lower than HP cutoff\\
 Filter Order & 4,8,16 & butterworth filter order \\
@@
 \end{tabular}}
-\caption{Synthesizer submodule parameters. There are $10^{15}$ unique programs are possible. Each synthesizer can contain any number of submodules}
+\caption{Synthesizer submodule parameters. $10^{15}$ unique programs are possible. Each synthesizer can contain any number of submodules}
 \label{table:submodule_params}
 \end{table}
-To create sounds, we need digital synthesizers.
+To create sounds, we build digital synthesizers.
 We use classical DSP to build our synthesizer, which allows for quick, offline, and parallel generation of audio signals without the usage of GPUs.
@@
 \end{table}
-High accuracy in detection of drums vs not-drums does not necessarily make an ear more suitable for our generative system.
+High accuracy in detection of organic drums vs synthetic sounds does not necessarily make an ear more suitable for our generative system.
 Perfect detection of drums vs not-drums would create a system which generates nothing.
@@
 \end{table}
-% \subsubsection{TPE Survey of 257 Samples:}
-% \begin{itemize}
-%     \item With 6 categorization groups, responders had the same categorization in 47\% of cases.
-%     \item The agreement between the responders and AVG was 44\% and 47\%.
-%     \item Of 257 samples, the responders agreed with FC, CNNLSTM and E/F respectively in 78, 76, and 46 of cases.
-The loss of spectrum data is likely the cause of E/F model's noticeably worse performance.
-%     \item The survey brings into question the reliability of our phase 1 model, as 30\% of the generated samples were deemed not percussive by at least 1 reviewer and 8\% by both reviewers
-%     \item The task of categorizing synthetic drums is difficult.
-Survey shows that the scale of agreement within persons as well as between persons and various model combinations is moderate at best, even after removal of \enquote{bad} samples.
-While the same models can easily achieve 98+ percent accuracy when tested on sounds from physical drum samples.
-%     \item While there is much room for improvement, our pipelines can generate and categorize drums and percussive sounds with a promising degree of success. 
-% \end{itemize}
 

### 2020-10-06 templates_aimusic2020/paper.tex
Updates from Overleaf

@@
 \begin{enumerate*}[label=(\roman*)]
-    \item \textit{Novelty and Creativity}: Given large sets of examples, generative models such as VAEs and GANS have proven capable of generating samples similar to the exemplars.
-In this work, we are not aiming for perfect imitations.
-We seek to create \emph{novel sounds} by via artificial, exploratory creativity.
+    \item \textit{Novelty and Creativity}: The goal here is to work with the limitations of any tractable sound source to create its approximations of a given sound category.
+We seek to create novel sounds via artificial, exploratory creativity.
 Boden defines this concept as an emergent property of generative work within confined rule sets~\cite{boden2009computer}.
 An example is the perpetual popularity of 8-bit aesthetics~\cite{collins2007loop}.
-We want to work with the limitations of any tractable sound source to create its approximations of a given sound category.
     \item \textit{Interpretability}: Neural networks are often described as black boxes with uninterruptible weights~\cite{basheer2000artificial}.
 Their highly recursive structure makes modern explanation methods such as saliency maps unreliable~\cite{rudin2019stop}.
-    \item \textit{Speed of Rendering}: Neural network synthesis is costly.
-Sub 24 khz sampling rates are common in most works~\cite{yamamoto2020parallel,oord2017parallel,aouameur2019neural,ramires2020neural}.
+    \item \textit{Speed of Rendering}: Neural network synthesis is costly; Sub 24 khz sample rates are common in most relevant works~\cite{yamamoto2020parallel,oord2017parallel,aouameur2019neural,ramires2020neural}.
 This is far below CD quality sampling rates~\cite{reiss2016meta}.

### 2020-10-06 templates_aimusic2020/paper.tex

@@
 \usepackage[T1]{fontenc}
+\usepackage[bottom]{footmisc}
 \newcommand{\keywords}[1]{\par\addvspace\baselineskip
@@
 We also implement machine learning classifiers for automatic separation of percussive sounds from non-percussive sounds.
-To effectively train the classifiers with small datasets, we simplify the representation of audio data by experimenting with fast Fourier transform (FFT) features and autoencoder embeddings.
+To effectively train the classifiers with small datasets, we simplify the representation of audio data by experimenting with fast Fourier transforms (FFT) and autoencoder embeddings.
 We call our system of feature extraction and classification of sounds the \emph{virtual ear}.
@@
 We save not just the desirable sounds, but also the programs which generated these sounds.
-These programs can be modified and experimented on by sound designers, or used for an improved search algorithm in future works.
+These programs can be modified and experimented on by sound designers.
+In this work, only random search is used for program generation, but other heuristics can be integrated for an improved search algorithm in future works.
 We build generative systems using different implementations of the virtual ear, and conduct manual hearing tests of the generated sounds.
@@
 However, we cannot quantify the novelty of these sounds.
-\section{Datasets}
-We curated 3 databases of one-shot drums which we use to train drum classifiers.
+
+We curated 3 data-sets of one-shot drums which we use to train drum classifiers.
 \textbf{FreeDB} contains 5 categories: kicks, snares, claps, hats and other (various percussions).
@@
 We call the sets of parameter values that characterize a synthesizer's submodules a \textit{program} (analogous to presets and submodules for a VST).
- \begin{figure}[tbp]
+ \begin{figure}[pb]
     \begin{center}
@@
 State of the art, parallel wave generation with GANs requires a fixed amount for rendering time for each time-step~\cite{yamamoto2020parallel}.
-Our virtual synthesizer produces audio by solving a linear system of equations.
-The added footprint of increasing the length of rendered sounds or higher sampling rates is relatively minuscule.
+With our virtual synthesizer, the added footprint of increasing the length of rendered sounds or higher sampling rates is relatively minuscule.
 \end{enumerate*}
@@
  }
- \begin{figure}[tbp]
+ \begin{figure}[bh]
     \begin{center}

### 2020-10-08 templates_aimusic2020/paper.tex
pre-halving blocks

@@
 \usepackage[bottom]{footmisc}
+\usepackage{makecell}
+\usepackage{xcolor}
 \newcommand{\keywords}[1]{\par\addvspace\baselineskip
@@
 However, we cannot quantify the novelty of these sounds.
-
-We curated 3 data-sets of one-shot drums which we use to train drum classifiers.
-\textbf{FreeDB} contains 5 categories: kicks, snares, claps, hats and other (various percussions).
-\textbf{RadarDB} contains 7 categories: kicks, snares, claps, hats, shakers, toms and rims.
-\textbf{MixedDB} contains 8 categories: kicks, snares, claps, high toms, low toms, medium toms, closed hats and open hats.
-See Appendix~\ref{appendix:datasets} for details and download links.
- \begin{figure}[tbp]
+ \begin{figure}[t!]
     \begin{center}
@@
 \end{figure}
+\begin{table}[b]
+% \captionof{table}{Table Title} 
+\centering
+\begin{tabular}{ |c|c| } 
+\hline
+DB Name & Categories                                                        \\ \hline
+FreeDB  & Kicks:533 - Snares:372 - Claps:230 - Hats:105 - Other:281            \\ \hline
+RadarDB & \makecell{Kicks:1054 - Snares:842 - Claps:353 \\ Toms:349 - Hats:1561 - Rims:131 - Shakers:121} \\ \hline
+MixedDB & Kicks:533 - Snares : 372 - Claps : 230 - Hats : 105 - Others : 281                     \\ \hline
+% NoiseDB & Generatable      & 1 Stack:2000 3 Stacks:2000  5 Stacks:2000                         \\ \hline
+\end{tabular}
+    % \caption{Overview of our datasets.}
+    \label{table:datasets_overview}
+\end{table}
+% \section{Datasets}
 
+Furthermore, we provide a subset of our curated datasets to facilitate future research.
+We curated 3 datasets of one-shot drums which we use to train and validate drum classifiers.
+We provide unrestricted access to \textbf{FreeDB} via Zenodo\footnote{\url{https://zenodo.org/record/3994999}}.
+\textbf{RadarDB} cannot be shared directly, we provide the script for its automated creation\footnote{\url{https://github.com/imilas/Synths_Stacks_Search}}.
+We cannot provide a copy of \textbf{MixedDB}, which is curated from various sources and personal libraries.
+ % \section{Datasets}
+% We curated 3 data-sets of one-shot drums which we use to train drum classifiers.
+\textbf{FreeDB} contains 5 categories: kicks, snares, claps, hats and other (various percussions).
+\textbf{RadarDB} contains 7 categories: kicks, snares, claps, hats, shakers, toms and rims.
+\textbf{MixedDB} contains 8 categories: kicks, snares, claps, high toms, low toms, medium toms, closed hats and open hats.
+See Appendix~\ref{appendix:datasets} for details and download links.
 \section{Related Works}
@@
 used  over 10,000 VST synthesizer presets to learn a parameter space which can be sampled for creation of new audio~\cite{esling2019universal}.
-Here, we work towards the approximation of percussive sounds with no prior knowledge about the sonic capabilities of a synthesizer.
+Here, we work towards the approximation of percussive sounds with no prior knowledge about the parameter space of a synthesizer.
 
 \section{Virtual Synthesizer Design}
-\begin{table}[tbp]
+\begin{table}[th]
 \centering
@@
 HP filter Cutoff & 0-20000hz & -\\
-LP filter Cutoff & 20000-HP & never lower than HP cutoff\\
+LP filter Cutoff & 20000hz-HP & never lower than HP cutoff\\
 Filter Order & 4,8,16 & butterworth filter order \\
@@
 We call the sets of parameter values that characterize a synthesizer's submodules a \textit{program} (analogous to presets and submodules for a VST).
- \begin{figure}[pb]
+ \begin{figure}[]
     \begin{center}
@@
 \end{figure}
-
  Rather than directly using neural networks for sound synthesis, we generate programs for this virtual synthesizer. Our decision is based on the following factors:
@@
 We defined 3 STFT (or FFT) transformation functions which we believe to capture important, unique attributes of percussive sounds.
-
 \begin{enumerate}
@@
 \end{enumerate}
+
 Another set of features were extracted using the latent embeddings of autoencoder networks.
@@
 Latent embeddings at the bottleneck layer of our best spectrogram autoencoder are used as features for sound categorization.
-As a sanity check for this approach, we trained our best autoencoder using 80\% of the drums in MixedDB.
+\textcolor{red}{ As a sanity check for this approach, we trained our best autoencoder using 80\% of the drums in MixedDB.
 Latent encodings of the remaining 20\% and 1000 Noise sounds were projected onto a 2 or 3-dimensional planes using t-SNE.
 We implemented interactions for our projection graphs (see Appendix~\ref{appendix:tsne}) so the sounds associated with plot points can be listened to.
-Hearing tests revealed a noticeable, positive correlation between a synthetic sound's distance and similarity to drum clusters.
+Hearing tests revealed a noticeable, positive correlation between a synthetic sound's distance and similarity to drum clusters.}
 
-To automatically learn from the described features, two groups of synthetic ears are implemented: \emph{two phased ears} (TPEs) and \emph{Mixed Ear Models} (MEMs).
+To automatically learn from the extracted features, two groups of synthetic ears are implemented: \emph{two phased ears} (TPEs) and \emph{Mixed Ear Models} (MEMs).
+For TPEs, we train multiple neural network architectures using different subsets of the FFT features to specialize in \decfirst~or \decsecond~ and combine them to make decisions sequentially.
+To train TPEs for \decfirst, we use all drums in RadarDB and FreeDB and 6000 examples of synthesized noise.
+For \decsecond, we combine the two databases and merge toms into kicks and rims/shakers into \enquote{other}.
+We trained the TPE models with 80\% of this dataset.
+Using the remaining 20\% of sounds, we achieved 98\% accuracy in \decfirst~and 82\% accuracy in~\decsecond~with our best models.
+These accuracy numbers are weak as we did not account for category sizes or cross validate.
+
+% To automatically learn from the described features, two groups of synthetic ears are implemented: \emph{two phased ears} (TPEs) and \emph{Mixed Ear Models} (MEMs).
 We train multiple neural network architectures using different subsets of the FFT features to specialize in \decfirst~or \decsecond~.
@@
 MEMs learn from autoencoder embeddings and envelope features and give simultaneous answers to both decisions.
-We use kicks, snares, claps, and hat sounds from RadarDB and FreeDB to train MEMs.
-MEMs are given 1000 examples of synthesized noise.
-Using 10-fold cross validation, our best MEM (an ExtraTrees Classifier) achieves the average f1-score of 92\% in 5-way sound classification (4 drum categories + synthesizer noise).
-This MEM makes both decisions together.
+We use kicks, snares, claps, and hat sounds from RadarDB and FreeDB as well as 1000 examples of synthesized noise to train MEMs.
+Using 10-fold cross validation, our best MEM (an ExtraTrees Classifier) achieves the average f1-score of 92\% in 5-way sound classification (4 drum categories + synthesized noise).
+\textcolor{red}{  This MEM makes both decisions together.
 Although never used, we achieved an average f1-score of 99\% after grouping drums together.
-Detailed measurements and model descriptions for TPEs and MEMs can be found in Appendix~\ref{appendix:classifier_definitions}.
+} Detailed measurements and model descriptions for TPEs and MEMs can be found in Appendix~\ref{appendix:classifier_definitions}.
+
 \begin{figure}[tbp]
@@
     \makebox[\textwidth]{\includegraphics[width=0.99\columnwidth]{templates_aimusic2020/images/ff3.pdf}}
-\caption{Graphed representation of FFT/STFT features.
-Randomly generated noise with a percussive envelop but unusual frequency features (modulated pitch).
-See Appendix~\ref{appendix:trans_funcitons} for more examples }
+\caption{Visualized representation of FFT features for a randomly synthesized noise. More examples in Appendix~\ref{appendix:trans_funcitons}.}
 \label{fig:stackspectrums}
@@
 % \usepackage{multirow}
-\begin{table}[]
-\centering
-\begin{tabular}{|c|c|c|c|c|c|c|c|}
-\hline
-Ear Type / System Name & Drop Rule         & Size & HvH  & H+FC & H+CNN & H+E/F & H+MEM \\ \hline
-\multirow{2}{*}{TPE} & No Drops          & 257  & 0.37 & 0.35 & 0.36  & 0.36  &       \\ \cline{2-8} 
-                     & All Bad and Other   & 154  & 0.47 & 0.59 & 0.54  & 0.50  &       \\ \hline
-\multirow{2}{*}{MEM} & No Drops          & 300  & 0.34 &      &       &       & 0.25  \\ \cline{2-8} 
-                     & All Bad and Other & 120  & 0.62 &      &       &       & 0.59  \\ \hline
-\end{tabular}
 
-\caption{Fleiss’ kappa coefficients as a measurement of agreement between persons (H+H) and persons with models.  }
-\end{table}
 High accuracy in detection of organic drums vs synthetic sounds does not necessarily make an ear more suitable for our generative system.
@@
 We cannot know the true size of $\mathcal{H^{+}}$ (see Figure~\ref{fig:ven_data}) without exhaustive manual hearing tests.
-We conduct manual hearing tests of two generative systems.
+We conduct blinded hearing tests of two generative systems.
 For \decfirst, a network which learns from spectrogram data utilizing CNN and LSTM layers is used.
@@
 Appendix~\ref{appendix:datasets} provides access to generated sounds.
+\begin{table}[tbp]
+\centering
+\begin{tabular}{|c|c|c|c|c|c|c|c|}
+\hline
+Ear Type / System Name & Drop Rule         & Size & HvH  & H+FC & H+CNN & H+E/F & H+MEM \\ \hline
+\ultirow{2}{*}{TPE} & No Drops          & 257  & 0.37 & 0.35 & 0.36  & 0.36  &       \\ \cline{2-8} 
+                     & All Bad and Other   & 154  & 0.47 & 0.59 & 0.54  & 0.50  &       \\ \hline
+\multirow{2}{*}{MEM} & No Drops          & 300  & 0.34 &      &       &       & 0.25  \\ \cline{2-8} 
+                     & All Bad and Other & 120  & 0.62 &      &       &       & 0.59  \\ \hline
+\end{tabular}
 
+\caption{Fleiss’ kappa coefficients as a measurement of agreement between persons (H+H) and persons with models.  }
+\end{table}
 \section{Conclusion, Validity, and Future Work}
 
-\textbf{Conclusion:} We successfully built a generative system for creation of percussive sounds via automatic programming of virtual synthesizers. We verified its results with human listeners.
+\textbf{Conclusion:} We built a generative system for creation of percussive sounds via automatic programming of virtual synthesizers. We verified its results with human listeners.
 Our work enables not only the creation of new libraries of percussion sounds, but new synthesizer programs which can be modified and studied. 

### 2020-10-09 templates_aimusic2020/paper.tex
thin blocks graph
model architectures table

@@
 \usepackage{xcolor}
+
 \newcommand{\keywords}[1]{\par\addvspace\baselineskip
@@
 \centering
+\caption{Synthesizer submodule parameters. $10^{15}$ unique programs are possible. Each synthesizer can contain any number of submodules}
 \resizebox{\columnwidth}{!}{\begin{tabular}{ |p{4cm}|p{4cm}|p{4cm}| } 
@@
 \end{tabular}}
-\caption{Synthesizer submodule parameters. $10^{15}$ unique programs are possible. Each synthesizer can contain any number of submodules}
+
 \label{table:submodule_params}
@@
 We call the sets of parameter values that characterize a synthesizer's submodules a \textit{program} (analogous to presets and submodules for a VST).
- \begin{figure}[]
+ \begin{figure}[tbp]
     \begin{center}
@@
     \makebox[\textwidth]{
-    \fbox{\includegraphics[width=1\linewidth]{templates_aimusic2020/images/synthesizer_block.pdf}}}
+    \includegraphics[width=1\linewidth]{templates_aimusic2020/images/synthesizer_block_thin.pdf}}
     \end{center}
@@
  }
- \begin{figure}[bh]
+ \begin{figure}[]
     \begin{center}
@@
 
+% Please add the following required packages to your document preamble:
+\begin{table}[]
+\caption{Overview of model architectures. Further details in Appendix~\ref{appendix:classifier_definitions}}
+\resizebox{\textwidth}{!}{%
+    \begin{tabular}{|>{\centering\arraybackslash}p{1cm}|>{\centering\arraybackslash}p{10cm}|>{\centering\arraybackslash}p{2cm}|}
+    \hline
+    Model & Architecture Layout                                                                             & Features                 \\ \hline
+    CNN   & CNN(2 channel convolution) -\textgreater LSTM(800 hidden states) -\textgreater Linear (shape 400x5)                                 & Spectrogram          \\ \hline
+    FC    & Fully connected Linear layers with shape: 400x10x5x10x5                                & Spectrogram          \\ \hline
+    E+F   & Fully connected network of size ix10x2x5 & Env. + Freq. \\ \hline
+    MEM   & Encoder -\textgreater Trees Classifier                                              & Spectrogram          \\ \hline
+    \end{tabular}
+}
+\end{table}
+
 To automatically learn from the extracted features, two groups of synthetic ears are implemented: \emph{two phased ears} (TPEs) and \emph{Mixed Ear Models} (MEMs).
@@
 % \textbf{Visual Representation of FFT Features}\par\medskip
-    \makebox[\textwidth]{\includegraphics[width=0.99\columnwidth]{templates_aimusic2020/images/ff3.pdf}}
+    \includegraphics[width=0.99\columnwidth]{templates_aimusic2020/images/ff3.pdf}
 \caption{Visualized representation of FFT features for a randomly synthesized noise. More examples in Appendix~\ref{appendix:trans_funcitons}.}
@@
 \centering
+\caption{Fleiss’ kappa coefficients as a measurement of agreement between persons (H+H) and persons with models.  }
 \begin{tabular}{|c|c|c|c|c|c|c|c|}
 \hline
-Ear Type / System Name & Drop Rule         & Size & HvH  & H+FC & H+CNN & H+E/F & H+MEM \\ \hline
+System's Ear Type  & Drop Rule         & Size & HvH  & H+FC & H+CNN & H+E/F & H+MEM \\ \hline
 \ultirow{2}{*}{TPE} & No Drops          & 257  & 0.37 & 0.35 & 0.36  & 0.36  &       \\ \cline{2-8} 
@@
 
-\caption{Fleiss’ kappa coefficients as a measurement of agreement between persons (H+H) and persons with models.  }
 \end{table}

### 2020-10-09 templates_aimusic2020/paper.tex
Updates from Overleaf

@@
 This audio is then categorized by the virtual ear.
-We save not just the desirable sounds, but also the programs which generated these sounds.
-These programs can be modified and experimented on by sound designers.
+We save not just the desirable sounds, but also the programs which generated these sounds, which can be modified and experimented on by sound designers.
 In this work, only random search is used for program generation, but other heuristics can be integrated for an improved search algorithm in future works.
-We build generative systems using different implementations of the virtual ear, and conduct manual hearing tests of the generated sounds.
+We build generative systems using different implementations of the virtual ear, and conduct manual, blinded hearing tests of the generated sounds.
 Our results are promising as the majority of sounds generated from our systems are deemed percussive by human listeners.
@@
 RadarDB & \makecell{Kicks:1054 - Snares:842 - Claps:353 \\ Toms:349 - Hats:1561 - Rims:131 - Shakers:121} \\ \hline
-MixedDB & Kicks:533 - Snares : 372 - Claps : 230 - Hats : 105 - Others : 281                     \\ \hline
+MixedDB & Kicks:533 - Snares:372 - Claps:230 - Hats:105 - Others:281                     \\ \hline
 % NoiseDB & Generatable      & 1 Stack:2000 3 Stacks:2000  5 Stacks:2000                         \\ \hline
@@
 Another set of features were extracted using the latent embeddings of autoencoder networks.
-We trained a number of autoencoders for the task of encoding and decoding spectrogram transformation of drum sounds, and used decoding loss to measure their performance (see Appendix~\ref{appendix:hyperparam}).
+Here, an autoencoder is a combination of an encoder which encodes spectrograms into a lower dimension and a decoder which tries to decode these embeddings into the original data.
+We trained a number of autoencoders with spectrogram transformations, and used the encoder from the autoencoder network with the lowest decoding loss as a feature extractor~\footnote{Appendix~\ref{appendix:hyperparam} has further details on the hyperparameter search process}.
 Latent embeddings at the bottleneck layer of our best spectrogram autoencoder are used as features for sound categorization.
@@
 \resizebox{\textwidth}{!}{%
-    \begin{tabular}{|>{\centering\arraybackslash}p{1cm}|>{\centering\arraybackslash}p{10cm}|>{\centering\arraybackslash}p{2cm}|}
+    \begin{tabular}{|>{\centering\arraybackslash}p{2cm}|>{\centering\arraybackslash}p{10cm}|>{\centering\arraybackslash}p{2cm}|}
     \hline
     Model & Architecture Layout                                                                             & Features                 \\ \hline
-    CNN   & CNN(2 channel convolution) -\textgreater LSTM(800 hidden states) -\textgreater Linear (shape 400x5)                                 & Spectrogram          \\ \hline
-    FC    & Fully connected Linear layers with shape: 400x10x5x10x5                                & Spectrogram          \\ \hline
-    E+F   & Fully connected network of size ix10x2x5 & Env. + Freq. \\ \hline
-    MEM   & Encoder -\textgreater Trees Classifier                                              & Spectrogram          \\ \hline
+    CNN(TPE)   & CNN(2 channel convolution)~ -\textgreater~LSTM(800 hidden states)~-\textgreater\newline ~Linear Layers (shape 400x5)                                 & Spectrogram          \\ \hline
+    FC(TPE)    & Fully connected Linear layers with shape: 400x10x5x10x5                                & Spectrogram          \\ \hline
+    E+F(TPE)   & Fully connected network of size 50x10x2x5 & Env. + Freq. \\ \hline
+    MEM   & Encoder -\textgreater~Embedded Spectrogram(size 64) -\textgreater~Extra-Trees                                              & Spectrogram          \\ \hline
     \end{tabular}
@@
 System's Ear Type  & Drop Rule         & Size & HvH  & H+FC & H+CNN & H+E/F & H+MEM \\ \hline
-\ultirow{2}{*}{TPE} & No Drops          & 257  & 0.37 & 0.35 & 0.36  & 0.36  &       \\ \cline{2-8} 
+\ultirow{TPE} & No Drops          & 257  & 0.37 & 0.35 & 0.36  & 0.36  &       \\ \cline{2-8} 
                      & All Bad and Other   & 154  & 0.47 & 0.59 & 0.54  & 0.50  &       \\ \hline

### 2020-10-09 templates_aimusic2020/paper.tex
Updates from Overleaf

@@
 
-% a short form should be given in case it is too long for the running head
 \titlerunning{Make Your Audience}
-
-% the name(s) of the author(s) follow(s) next
 \author{Amir Salimi \and Abram Hindle}
-
 \authorrunning{Amir Salimi and Abram Hindle }
-
-% the affiliations are given next; don't give your e-mail address
-% unless you accept that it will be published
 \institute{Department of Computing Science\\ University of Alberta \\ \email{asalimi@ualberta.ca\\hindle1@ualberta.ca}}
 
-% intro, 1 page
-% background and methodology 2 pages
-% implementation 
-% results 2.5
 \maketitle
@@
 However, we cannot quantify the novelty of these sounds.
- \begin{figure}[t!]
+ \begin{figure}[tbp]
     \begin{center}
@@
 \end{figure}
-\begin{table}[b]
-% \captionof{table}{Table Title} 
+\begin{table}[tbp]
 \centering
+\caption{Curated databases}
 \begin{tabular}{ |c|c| } 
@@
     % \caption{Overview of our datasets.}
-    \label{table:datasets_overview}
+    \label{table:drumdb}
 \end{table}
@@
 We curated 3 datasets of one-shot drums which we use to train and validate drum classifiers.
+The number of samples per group in these databases is provided in Table ~\ref{table:drumdb}.
 We provide unrestricted access to \textbf{FreeDB} via Zenodo\footnote{\url{https://zenodo.org/record/3994999}}.
@@
 Automatic programming~\footnote{unsupervised generation of source code or programs towards a goal} of virtual synthesizers has long been a topic of interest.
-In early 2000s, Interactive Genetic Algorithms (IGA's) were utilized for the generation of new sounds with various sound-engines~\cite{johnson1999exploring,dahlstedt2001creating}.
+Genetic Algorithms (GA's) have long been utilized for the generation of new sounds with various sound-engines~\cite{hornermachinetongues,macret2012automatic}.
 A more recent work by Yee-King et al.~\cite{yee2018automatic} used Long short-Term Memory (LSTM) models and heuristic search to find the exact parameters used to create a group of sounds.
@@
 \section{Virtual Synthesizer Design}
-\begin{table}[th]
+\begin{table}[tbp]
 \centering
@@
  }
- \begin{figure}[]
+ \begin{figure}[tbp]
     \begin{center}
@@
 Various works have demonstrated effective reconstruction of signals given their Short-time Fourier Transforms (STFT)~\cite{nawab1983signal,griffin1984signal}.
-If the STFT of a signal can be used for its reconstruction, perhaps it can be utilized as a source of fundamental features.
+If the STFT of a signal can be used for its reconstruction, perhaps it can be utilized as a source of fundamental features~\cite{lee2009unsupervised,hershey2017cnn}.
 We defined 3 STFT (or FFT) transformation functions which we believe to capture important, unique attributes of percussive sounds.
@@
 Latent embeddings at the bottleneck layer of our best spectrogram autoencoder are used as features for sound categorization.
-\textcolor{red}{ As a sanity check for this approach, we trained our best autoencoder using 80\% of the drums in MixedDB.
-Latent encodings of the remaining 20\% and 1000 Noise sounds were projected onto a 2 or 3-dimensional planes using t-SNE.
-We implemented interactions for our projection graphs (see Appendix~\ref{appendix:tsne}) so the sounds associated with plot points can be listened to.
-Hearing tests revealed a noticeable, positive correlation between a synthetic sound's distance and similarity to drum clusters.}
 
 % Please add the following required packages to your document preamble:
-\begin{table}[]
+\begin{table}[tbp]
 \caption{Overview of model architectures. Further details in Appendix~\ref{appendix:classifier_definitions}}
@@
 Using 10-fold cross validation, our best MEM (an ExtraTrees Classifier) achieves the average f1-score of 92\% in 5-way sound classification (4 drum categories + synthesized noise).
-\textcolor{red}{  This MEM makes both decisions together.
-Although never used, we achieved an average f1-score of 99\% after grouping drums together.
-} Detailed measurements and model descriptions for TPEs and MEMs can be found in Appendix~\ref{appendix:classifier_definitions}.
+Detailed measurements and model descriptions for TPEs and MEMs can be found in Appendix~\ref{appendix:classifier_definitions}.
 
@@
 \bibliographystyle{apacite}
-\bibliography{CSMC_MUME_LaTeX_Template.bib}
+\bibliography{citations.bib}
 
@@
 At times, we merged or purged drum groups to simplify tasks.
-\begin{table}[]
+
+\begin{table}[tbp]
+% \captionof{table}{Table Title} 
 \centering
-\begin{tabular}[width=\paperwidth]{|l|l|l|l|l|l|l|l|l|l|}
+\begin{tabular}{ |c|c| } 
 \hline
-DB Name & kick & snare & clap & tom\_high & tom\_mid & tom\_low & hihat\_closed &  hihat\_open & rim \\ \hline
-MixedDB & 648 & 732 & 118 & 179 & 139 &  188 & 187 & 280 & 105 \\\hline
+DB Name & Categories                                                        \\ \hline
+FreeDB  & Kicks:533 - Snares:372 - Claps:230 - Hats:105 - Other:281            \\ \hline
+RadarDB & \makecell{Kicks:1054 - Snares:842 - Claps:353 \\ Toms:349 - Hats:1561 - Rims:131 - Shakers:121} \\ \hline
+MixedDB & Kicks:533 - Snares:372 - Claps:230 - Hats:105 - Others:281                     \\ \hline
+NoiseDB & Generatable      & 1 Stack:2000 3 Stacks:2000  5 Stacks:2000                         \\ \hline
 \end{tabular}
-\caption{Database 1: Mixed sources}
-\label{db:self}
+    % \caption{Overview of our datasets.}
+    \label{table:datasets_overview}
 \end{table}
+% \begin{table}[]
+% \centering
+% \begin{tabular}[width=\paperwidth]{|l|l|l|l|l|l|l|l|l|l|}
+% \hline
+% DB Name & kick & snare & clap & tom\_high & tom\_mid & tom\_low & hihat\_closed &  hihat\_open & rim \\ \hline
+% MixedDB & 648 & 732 & 118 & 179 & 139 &  188 & 187 & 280 & 105 \\\hline
+% \end{tabular}
+% \caption{Database 1: Mixed sources}
+% \label{db:self}
+% \end{table}
 
-\begin{table}[]
-\centering
-\begin{tabular}{|l|l|l|l|l|l|l|l|l|}
-\hline
-DB Name & kick & snare & clap & tom & clap & hat & rim & shaker  \\ \hline
-RadarDB & 1054 & 842   & 353 & 349 &  353 & 1561& 131 & 121 \\ \hline
-\end{tabular}
-\caption{Database 2: Royalty free sounds sourced from \enquote{Music Radar}}
-\label{db:radar}
-\end{table}
+% \begin{table}[]
+% \centering
+% \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
+% \hline
+% DB Name & kick & snare & clap & tom & clap & hat & rim & shaker  \\ \hline
+% RadarDB & 1054 & 842   & 353 & 349 &  353 & 1561& 131 & 121 \\ \hline
+% \end{tabular}
+% \caption{Database 2: Royalty free sounds sourced from \enquote{Music Radar}}
+% \label{db:radar}
+% \end{table}
 
-\begin{table}[]
-\centering
-\begin{tabular}{|l|l|l|l|l|l|}
-\hline
- DB Name & kick & snare & clap & hat & other \\\hline
- FreeDB & 533 & 372 & 230 & 105 & 281 \\ \hline
-\end{tabular}
-\caption{Database 3: Free sounds sourced from the \enquote{Sample Swap} project.
+% \begin{table}[]
+% \centering
+% \begin{tabular}{|l|l|l|l|l|l|}
+% \hline
+%  DB Name & kick & snare & clap & hat & other \\\hline
+%  FreeDB & 533 & 372 & 230 & 105 & 281 \\ \hline
+% \end{tabular}
+% \caption{Database 3: Free sounds sourced from the \enquote{Sample Swap} project.
 Simplified for our purposes.
@@
 The \enquote{other} category contains a variety of percussive sounds.}
-\label{db:sampleswap}
-\end{table}
+% \label{db:sampleswap}
+% \end{table}
 
-\begin{table}[]
-\centering
-\begin{tabular}{|l|l|l|l|}
-\hline
- Synth Noise Type & 1 Stack & 3 Stacks  & 5 Stacks \\ \hline
- Number of Examples & 2000 & 2000 & 2000 \\ \hline
-\end{tabular}
-\caption{Database of random noise examples from our virtual synthesizers}
-\label{db:noise}
-\end{table}
+% \begin{table}[]
+% \centering
+% \begin{tabular}{|l|l|l|l|}
+% \hline
+%  Synth Noise Type & 1 Stack & 3 Stacks  & 5 Stacks \\ \hline
+%  Number of Examples & 2000 & 2000 & 2000 \\ \hline
+% \end{tabular}
+% \caption{Database of random noise examples from our virtual synthesizers}
+% \label{db:noise}
+% \end{table}
+
 %==========================
@@
 \label{appendix:surveys}
-\begin{table}[h!]
-  \begin{tabular}{|c | c | c | c | c | c | c|} 
-  \hline
-  Drop Rule & Size & H+H & H+FC & H+CNN & H+E/F & 3 models \\ [0.5ex] 
-  \hline
-  No Drops & 257 &0.37 & 0.35 & 0.36 & 0.36 & 0.28\\ 
-  \hline
-  Assigned \enquote{Bad} By Both & 236 & 0.31 & 0.37 & 0.37 & 0.38 & 0.30 \\
-  \hline
-  Assigned \enquote{Bad} By Either & 180 & 0.47 & 0.50 & 0.48 & 0.48 &  0.34 \\
-  \hline
-  Assigned \enquote{Bad} or \enquote{Other} By Either & 154 & 0.47 & 0.59 & 0.54 & 0.50 &  0.35 \\
-  \hline
- \end{tabular}
- \caption{\label{kappa_table_TPE}Table of Fleiss' kappa coefficient to measure the degree of agreement between persons (H+H), persons with FC model (H+FC), persons with CNNLSTM model, persons with all models (H+E/F), and between the 3 models.
+% \begin{table}[h!]
+%   \begin{tabular}{|c | c | c | c | c | c | c|} 
+%   \hline
+%   Drop Rule & Size & H+H & H+FC & H+CNN & H+E/F & 3 models \\ [0.5ex] 
+%   \hline
+%   No Drops & 257 &0.37 & 0.35 & 0.36 & 0.36 & 0.28\\ 
+%   \hline
+%   Assigned \enquote{Bad} By Both & 236 & 0.31 & 0.37 & 0.37 & 0.38 & 0.30 \\
+%   \hline
+%   Assigned \enquote{Bad} By Either & 180 & 0.47 & 0.50 & 0.48 & 0.48 &  0.34 \\
+%   \hline
+%   Assigned \enquote{Bad} or \enquote{Other} By Either & 154 & 0.47 & 0.59 & 0.54 & 0.50 &  0.35 \\
+%   \hline
+%  \end{tabular}
+%  \caption{\label{kappa_table_TPE}Table of Fleiss' kappa coefficient to measure the degree of agreement between persons (H+H), persons with FC model (H+FC), persons with CNNLSTM model, persons with all models (H+E/F), and between the 3 models.
 } % AH: Which decision is this?
- \end{table}
-\begin{table}[h!]
- \begin{tabular}{|c| p{2cm} | p{2cm}| p{2cm}|} 
- \hline
- Drop Rule & Size & H+H & H+MEM \\
- \hline
- No Drop & 300 & 0.34 & 0.25\\ 
- \hline
- Assigned Bad By Both & 249 & 0.20 & 0.26 \\
- \hline
- Assigned Bad By Either & 151 & 0.46 &  0.47 \\
- \hline
-Assigned \enquote{Bad} or \enquote{Other} By Either  & 120 & 0.62   &  0.59 \\
- \hline
-\end{tabular}
-\caption{\label{kappa_table_MEM}Table of Fleiss' kappa coefficient to measure the degree of agreement between persons (H+H) and persons with MEM (H+MEM).}
-\end{table}
+%  \end{table}
+% \begin{table}[h!]
+%  \begin{tabular}{|c| p{2cm} | p{2cm}| p{2cm}|} 
+%  \hline
+%  Drop Rule & Size & H+H & H+MEM \\
+%  \hline
+%  No Drop & 300 & 0.34 & 0.25\\ 
+%  \hline
+%  Assigned Bad By Both & 249 & 0.20 & 0.26 \\
+%  \hline
+%  Assigned Bad By Either & 151 & 0.46 &  0.47 \\
+%  \hline
+% Assigned \enquote{Bad} or \enquote{Other} By Either  & 120 & 0.62   &  0.59 \\
+%  \hline
+% \end{tabular}
+% \caption{\label{kappa_table_MEM}Table of Fleiss' kappa coefficient to measure the degree of agreement between persons (H+H) and persons with MEM (H+MEM).}
+% \end{table}
 

### 2020-10-09 templates_aimusic2020/CSMC_TEMPLATE.tex
pre-running title change

%%%%%%%%%%%%%%%%%%%% file CSMC_MUME_LaTeX_Template.tex %%%%%%%%%%%%%%%%%%%%%
%
% This is the LaTeX source for the instructions to authors using
% the LaTeX document class 'llncs.cls' for contributions to
% the Journal of Creative Music Systems.
% Copyright: http://www.springer.com/lncs       Springer Heidelberg 2006/05/04
%
% It may be used as a template for your own input - copy it
% to a new file with a new name and use it as the basis
% for your article.
%
% NB: the document class 'llncs' has its own and detailed documentation, see
% ftp://ftp.springer.de/data/pubftp/pub/tex/latex/llncs/latex2e/llncsdoc.pdf
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[runningheads,a4paper]{llncs}

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{url}
\usepackage{apacite}
%added 
\usepackage[inline]{enumitem}    
\usepackage{subcaption}
\usepackage{caption}
\usepackage{threeparttable} %annotations for table
\usepackage{csquotes}

\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

\pagestyle{headings}

\begin{document}

\mainmatter  % start of an individual contribution

% first the title is needed
\title{Percussive Sound Generation with Virtual Listeners and Modular Synthesizers}

% a short form should be given in case it is too long for the running head
\titlerunning{Running Title}

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
\author{Amir Salimi \and Abram Hindle}
%
% if the names of the authors are too long for the running head, please use the format: AuthorA et al.
\authorrunning{Amir Salimi and Abram Hindle }

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{Department of Computing Science\\ University of Alberta \\ \email{asalimi@ualberta.ca}}

%
% NB: a more complex sample for affiliations and the mapping to the
% corresponding authors can be found in the file "llncs.dem"
% (search for the string "\mainmatter" where a contribution starts).
% "llncs.dem" accompanies the document class "llncs.cls".
%

\maketitle

\begin{abstract}
Digital sound artists often require a variety of percussive samples for their music. For more than two decades research involving digital synthesis, heuristic search, and neural networks has been used for the generation of novel sounds. Our goal is to generate one-shot percussive samples by leveraging modern AI technologies alongside scalable signal generation methods. We centered our approach around the combination of two central components: \begin {enumerate*} [label=(\roman*)] \item a \emph{virtual ear} capable of evaluating the proximity of unheard sounds to  and \item a dynamic \emph{virtual synthesizer} with a rich set of tractable parameters\end{enumerate*}. We present a generative pipeline that utilizes robust digital signal processing methods guided by supervised learning towards the generation of one-shot percussive sounds. We present our findings and measurements of the various approaches taken. Advantages, shortcomings and practicality of the employed methodologies are demonstrated. We share our curated dataset of sounds and codebase\footnote{\url{https://github.com/imilas/Synths_Stacks_Search}} which can be used for its further expansion.
\keywords{Automatic Synthesizer design. Machine Listening. Sound Analysis. Novelty and Originality}
\end{abstract}

\section{Introduction}

This is a \LaTeX{} template for submission to the \textit{2020 Joint Conference on AI Music Creativity (CSMC + MuMe)}.

\section{Paper Preparation}

When you use \LaTeX\ together with our document class file,
\texttt{llncs.cls},
your text is typeset automatically in Computer Modern Roman (CM) fonts.
Please do
\emph{not} change the preset fonts. If you have to use fonts other
than the preset fonts, kindly submit these with your files.

Please use the commands \verb+\label+ and \verb+\ref+ for
cross-references and the commands \verb+\bibitem+ and \verb+\cite+ for
references to the bibliography, to enable us to create hyperlinks at
these places.

For preparing your figures electronically and integrating them into
your source file we recommend using the standard \LaTeX{} \verb+graphics+ or
\verb+graphicx+ package. These provide the \verb+\includegraphics+ command.
In general, please refrain from using the \verb+\special+ command.

Remember to submit any further style files and
fonts you have used together with your source files.

\subsubsection{Headings.}

Headings should be capitalized
(i.e., nouns, verbs, and all other words
except articles, prepositions, and conjunctions should be set with an
initial capital) and should,
with the exception of the title, be aligned to the left.
Words joined by a hyphen are subject to a special rule. If the first
word can stand alone, the second word should be capitalized.

Here are some examples of headings: ``Criteria to Disprove
Context-Freeness of Collage Language'', ``On Correcting the Intrusion of
Tracing Non-deterministic Programs by Software'', ``A User-Friendly and
Extendable Data Distribution System'', ``Multi-flip Networks:
Parallelizing GenSAT'', ``Self-determinations of Man''.

\subsubsection{Lemmas, Propositions, and Theorems.}

The numbers accorded to lemmas, propositions, and theorems, etc. should
appear in consecutive order, starting with Lemma 1, and not, for
example, with Lemma 11.

\subsection{Figures}

For \LaTeX\ users, we recommend using the \emph{graphics} or \emph{graphicx}
package and the \verb+\includegraphics+ command.

Please check that the lines in line drawings are not
interrupted and are of a constant width. Grids and details within the
figures must be clearly legible and may not be written one on top of
the other. Line drawings should have a resolution of at least 800 dpi
(preferably 1200 dpi). The lettering in figures should have a height of
2~mm (10-point type). Figures should be numbered and should have a
caption which should always be positioned \emph{under} the figures, in
contrast to the caption belonging to a table, which should always appear
\emph{above} the table; this is simply achieved as matter of sequence in
your source.

Please centre the figures or your tabular material by using the \verb+\centering+
declaration. Short captions are centred by default between the margins
and typeset in 9-point type (Fig.~\ref{fig:example} shows an example).
The distance between text and figure is preset to be about 8~mm, the
distance between figure and caption about 6~mm.

To ensure that the reproduction of your illustrations is of a reasonable
quality, we advise against the use of shading. The contrast should be as
pronounced as possible.

If screenshots are necessary, please make sure that you are happy with
the print quality before you send the files.

\begin{figure}
	\centering
	\includegraphics[height=6.2cm]{graphic.pdf}
	\caption{One kernel at $x_s$ (\emph{dotted kernel}) or two kernels at
	$x_i$ and $x_j$ (\textit{left and right}) lead to the same summed estimate
	at $x_s$. This shows a figure consisting of different types of
	lines. Elements of the figure described in the caption should be set in
	italics, in parentheses, as shown in this sample caption.}
	\label{fig:example}
\end{figure}

Please define figures (and tables) as floating objects. Please avoid
using optional location parameters like ``\verb+[h]+'' for ``here''.

\subsection{Formulas}

Displayed equations or formulas are centred and set on a separate
line (with an extra line or halfline space above and below). Displayed
expressions should be numbered for reference. The numbers should be
consecutive within each section or within the contribution,
with numbers enclosed in parentheses and set on the right margin --
which is the default if you use the \emph{equation} environment, e.g.,

\begin{equation}
  \psi (u) = \int_{o}^{T} \left[\frac{1}{2}
  \left(\Lambda_{o}^{-1} u,u\right) + N^{\ast} (-u)\right] dt \;  .
\end{equation}

Equations should be punctuated in the same way as ordinary
text but with a small space before the end punctuation mark.

\subsection{Footnotes}

The superscript numeral used to refer to a footnote appears in the text
either directly after the word to be discussed or -- in relation to a
phrase or a sentence -- following the punctuation sign (comma,
semicolon, or period). Footnotes should appear at the bottom of
the normal text area, with a line of about 2~cm set
immediately above them.\footnote{The footnote numeral is set flush left
and the text follows with the usual word spacing.}

\subsection{Program Code}

Program listings or program commands in the text are normally set in
typewriter font, e.g., CMTT10 or Courier.

\medskip

\noindent
{\it Example of a Computer Program}
\begin{verbatim}
program Inflation (Output)
  {Assuming annual inflation rates of 7%, 8%, and 10%,...
   years};
   const
     MaxYears = 10;
   var
     Year: 0..MaxYears;
     Factor1, Factor2, Factor3: Real;
   begin
     Year := 0;
     Factor1 := 1.0; Factor2 := 1.0; Factor3 := 1.0;
     WriteLn('Year  7% 8% 10%'); WriteLn;
     repeat
       Year := Year + 1;
       Factor1 := Factor1 * 1.07;
       Factor2 := Factor2 * 1.08;
       Factor3 := Factor3 * 1.10;
       WriteLn(Year:5,Factor1:7:3,Factor2:7:3,Factor3:7:3)
     until Year = MaxYears
end.
\end{verbatim}
%
\noindent
{\small (Example from Jensen K., Wirth N. (1991). \textit{Pascal user manual and
report}. New York: Springer)}

\subsection{Citations}

For citations in the text please use the APA6 system (\url{http://www.apastyle.org/}).

Examples:
\cite{einstein}
\cite<e.g.,>{knuthwebsite}
\cite[p.~10]{latexcompanion}
\citeA{latexcompanion}
(\citeNP{einstein}; \citeNP{latexcompanion})
\cite[pp.~10--11]{einstein}

\subsection{Page Numbering and Running Heads}

There is no need to include page numbers. If your paper title is too
long to serve as a running head, it will be shortened. Your suggestion
as to how to shorten it would be most welcome.

\subsubsection*{Acknowledgements} The heading should be treated as a
subsubsection heading and should not be assigned a number.

\section{The References Section}\label{references}

Please use the APA6 style for references.
The reference section must be complete. You may not omit references.
Instructions as to where to find a fuller version of the references are
not permissible.

We only accept references written using the Latin alphabet. If the title
of the book you are referring to is in Russian or Chinese, then please write
(in Russian) or (in Chinese) at the end of the transcript or translation
of the title.

The following section shows a sample reference list.

\bibliographystyle{apacite}
% Place your own .bib file here:
\bibliography{CSMC_MUME_LaTeX_Template.bib}

\end{document}

### 2020-10-09 templates_aimusic2020/paper.tex
pre-running title change

@@
 However, we cannot quantify the novelty of these sounds.
- \begin{figure}[tbp]
+ \begin{figure}[tb]
     \begin{center}
@@
 \end{figure}
-\begin{table}[tbp]
+
+\begin{table}[tb]
 \centering
@@
 \end{table}
+
 % \section{Datasets}
@@
 \section{Virtual Synthesizer Design}
-\begin{table}[tbp]
+\begin{table}[tb]
 \centering
@@
 We call the sets of parameter values that characterize a synthesizer's submodules a \textit{program} (analogous to presets and submodules for a VST).
- \begin{figure}[tbp]
+ \begin{figure}[tb]
     \begin{center}
@@
  }
- \begin{figure}[tbp]
+ \begin{figure}[tb]
     \begin{center}
@@
 
+% \textcolor{red}{ As a sanity check for this approach, we trained our best autoencoder using 80\% of the drums in MixedDB.
+Latent encodings of the remaining 20\% and 1000 Noise sounds were projected onto a 2 or 3-dimensional planes using t-SNE.
+We implemented interactions for our projection graphs (see Appendix~\ref{appendix:tsne}) so the sounds associated with plot points can be listened to.
+Hearing tests revealed a noticeable, positive correlation between a synthetic sound's distance and similarity to drum clusters.}
+
 % Please add the following required packages to your document preamble:
-\begin{table}[tbp]
+\begin{table}[tb]
 \caption{Overview of model architectures. Further details in Appendix~\ref{appendix:classifier_definitions}}
@@
 
-\begin{figure}[tbp]
+\begin{figure}[tb]
 \begin{center}
@@
 Appendix~\ref{appendix:datasets} provides access to generated sounds.
-\begin{table}[tbp]
+\begin{table}[tb]
 \centering
@@
 We also created a database of synthetic noise from 1, 3, and 5 stacked virtual synthesizers.
-Specifications about our datasets can be found in tables~\ref{db:self},~\ref{db:radar},~\ref{db:sampleswap} and~\ref{db:noise}.
+Specifications about our datasets can be found in tables~\ref{table:all_db}.
 We have made our dataset of free-drum sounds available for download.
@@
 
-\begin{table}[tbp]
-% \captionof{table}{Table Title} 
+\begin{table}[tb]
 \centering
+\caption{Curated databases, including NoiseDB}
 \begin{tabular}{ |c|c| } 
@@
 MixedDB & Kicks:533 - Snares:372 - Claps:230 - Hats:105 - Others:281                     \\ \hline
-NoiseDB & Generatable      & 1 Stack:2000 3 Stacks:2000  5 Stacks:2000                         \\ \hline
+NoiseDB & 1 Stack:2000 - 3 Stacks:2000 - 5 Stacks:2000                         \\ \hline
 \end{tabular}
     % \caption{Overview of our datasets.}
-    \label{table:datasets_overview}
+    \label{table:all_db}
 \end{table}
@@
 \label{appendix:trans_funcitons}
-\begin{figure}[tbp]
+Figure ~\ref{stackspectrums} contains the graphed representation of features extracted for 3 different samples.
+Sample $a$ is a recorded hat from our database.
+sample $b$ is an example of randomly generated noise with percussive qualities that we found suitably similar to a snare sound.
+Sample $c$ is an example of a randomly generated noise where the spectrum features are necessary for proper classification.
+\begin{figure}[h]
 \centering
@@
     { \includegraphics[width=1\columnwidth]{images/ff3.pdf}}
-\caption{Graphed representation of features extracted for 3 different samples.
-Sample $a$ is a recorded hat from our database.
-sample $b$ is an example of randomly generated noise with percussive qualities that we found suitably similar to a snare sound.
-Sample $c$ is an example of a randomly generated noise where the spectrum features are necessary for proper classification.}
-\label{fig:stackspectrums}
+\label{stackspectrums}
 \end{figure}
-\begin{enumerate}
-\item Envelope Transformation: Represents changes in loudness for the duration of the signal.
+% \begin{enumerate}
+% \item Envelope Transformation: Represents changes in loudness for the duration of the signal.
 Using STFT we generate a matrix $M_{i \times j}$ with rows $i$ and columns $j$ corresponding to time steps and frequency bins respectively.
@@
 The information contained in this vector is an alternative to Root-Mean-Square measurements of a sliding window over the signal.
-\item Frequency Transformation: A static, normalized snap-shot of the the frequencies present within the audio.
+% \item Frequency Transformation: A static, normalized snap-shot of the the frequencies present within the audio.
 The calculation of this feature vector is similar to the envelope, but the summation is done along the frequency axis.
@@
 A Mel Scale transformation was also applied in hopes that the captured features better represent human perception of frequencies.
-\item Spectrum Transformation: This function is simply a Mel Scaled STFT with its values normalized from 0-1.
+% \item Spectrum Transformation: This function is simply a Mel Scaled STFT with its values normalized from 0-1.
 Spectrograms contain more information about the original signal but their analysis requires more complex computational methods.
-\end{enumerate}
+% \end{enumerate}
 
@@
 \end{table}
-\begin{table}[htbp]
+\begin{table}[htb]
 \centering
@@
 
-\begin{figure}[htbp!]
+\begin{figure}[htb!]
     \begin{center}
@@
 
-\begin{figure}[htbp!]
+\begin{figure}[htb!]
 \begin{center}
@@
 \\
-\begin{table}[htbp]
+\begin{table}[htb]
 \begin{tabular}{|p{28mm}|p{50mm}|p{21mm}|p{21mm}|}
@@
 
-\begin{figure}[htbp]
+\begin{figure}[htb]
 \centering
@@
 
-\begin{table}[htbp!]
+\begin{table}[htb!]
 \centering
@@
 %==============
-\chapter{Embedded Feature Visualization}
-Live demos provided in project source code.
-\label{appendix:tsne}
-\begin{figure}[]
-\centering
-\textbf{2 Dimensional Projection of Latent Variables}\par\medskip
- \includegraphics[width=0.90\linewidth]{images/t-SNE_2d.pdf}
-\caption{Projection of an embedding model's low dimensional encoding on to a 2D plane. We implemented interactions for these graphs for manual inspection of samples. }
-\label{fig:2d_tsne}
-\end{figure}
+% \chapter{Embedded Feature Visualization}
+% Live demos provided in project source code.
+% \label{appendix:tsne}
+% \begin{figure}[]
+% \centering
+% \textbf{2 Dimensional Projection of Latent Variables}\par\medskip
+%  \includegraphics[width=0.90\linewidth]{images/t-SNE_2d.pdf}
+% \caption{Projection of an embedding model's low dimensional encoding on to a 2D plane. We implemented interactions for these graphs for manual inspection of samples. }
+% \label{fig:2d_tsne}
+% \end{figure}
 
-\begin{figure}[]
-\centering
-\textbf{3D t-SNE Projection}\par\medskip
-\mbox{\subfloat[]{\label{subfig:1} \fbox{\includegraphics[width=12cm,height=6.8cm]{images/3d_t-SNE_symdrum_type_cam0.pdf}}}}
+% \begin{figure}[]
+% \centering
+% \textbf{3D t-SNE Projection}\par\medskip
+% \mbox{\subfloat[]{\label{subfig:1} \fbox{\includegraphics[width=12cm,height=6.8cm]{images/3d_t-SNE_symdrum_type_cam0.pdf}}}}
 
-\mbox{\subfloat[]{\label{subfig:2} \fbox{\includegraphics[width=12cm,height=6.8cm]{images/3d_t-SNE_symdrum_type_cam3.pdf}}}}
+% \mbox{\subfloat[]{\label{subfig:2} \fbox{\includegraphics[width=12cm,height=6.8cm]{images/3d_t-SNE_symdrum_type_cam3.pdf}}}}
 
-\fbox{\mbox{\subfloat[]{\label{subfig:2} \includegraphics[width=6cm,height=6cm]{images/3d_t-SNE_symdrum_type_cam1.pdf}}}
-\mbox{\subfloat[]{\label{subfig:2} \includegraphics[width=6cm,height=6cm]{images/3d_t-SNE_symdrum_type_cam2.pdf}}}}
-\caption{3D projections of the data used for Figure~\ref{fig:2d_tsne}. Interactive demos are also implemented for 3D projections.}
-\label{fig:3d_tsne}
-\end{figure}
+% \fbox{\mbox{\subfloat[]{\label{subfig:2} \includegraphics[width=6cm,height=6cm]{images/3d_t-SNE_symdrum_type_cam1.pdf}}}
+% \mbox{\subfloat[]{\label{subfig:2} \includegraphics[width=6cm,height=6cm]{images/3d_t-SNE_symdrum_type_cam2.pdf}}}}
+% \caption{3D projections of the data used for Figure~\ref{fig:2d_tsne}. Interactive demos are also implemented for 3D projections.}
+% \label{fig:3d_tsne}
+% \end{figure}
 
-%==============
+% %==============
 \chapter{Survey Details}
 \label{appendix:surveys}
+Details of survey responses are presented in figures~\ref{fig:freq-survey-2p} and~\ref{fig:freq-survey-mme}. The surveys were done blinded with the two authors assigning categories to unlabled sounds.
 % \begin{table}[h!]
@@
 % \end{table}
-
 \begin{figure}[h!]
@@
 
-\subsubsection{MEM Survey of 300 Samples:}
-
-\begin{figure}[htpb]
+\begin{figure}[h!]
     \begin{center}
@@
     \caption{Frequency of assigned labels by persons vs the true number of labels}
-\label{fig:freq-survey-2p}
+\label{fig:freq-survey-mme}
 \end{figure} 
-
 \end{appendices}

### 2020-10-09 templates_aimusic2020/paper.tex
appendix shortened

@@
 \usepackage{csquotes}
-\usepackage{appendix}
+\usepackage[title]{appendix}
 \usepackage{comment}
@@
 If the STFT of a signal can be used for its reconstruction, perhaps it can be utilized as a source of fundamental features~\cite{lee2009unsupervised,hershey2017cnn}.
-We defined 3 STFT (or FFT) transformation functions which we believe to capture important, unique attributes of percussive sounds.
+We defined 3 STFT (or FFT) transformation functions to capture important features of percussive sounds.
 \begin{enumerate}
@@
 \item Frequency Transformation:  Similar to envelope calculation, but the summation is done along the frequency axis. Shorter hop-sizes and wider windows were used to increase frequency resolution. 
-\item Spectrum Transformation: Mel Scaled STFT with values normalized from 0-1. 
+\item Spectrum Transformation: Mel Scaled STFT. Values normalized from 0-1. 
 \end{enumerate}
@@
 \bibliography{citations.bib}
+\clearpage
 
 \begin{appendices}
-%======================
+\markboth{Appendix}{Appendix}
+
 \chapter{Datasets, Details, and Downloads}
@@
 \label{appendix:trans_funcitons}
-Figure ~\ref{stackspectrums} contains the graphed representation of features extracted for 3 different samples.
+Figure~\ref{fig:stackspectrums} contains the graphed representation of features extracted for 3 different samples.
 Sample $a$ is a recorded hat from our database.
@@
 Sample $c$ is an example of a randomly generated noise where the spectrum features are necessary for proper classification.
-\begin{figure}[h]
+\begin{figure}
 \centering
@@
     { \includegraphics[width=1\columnwidth]{images/ff3.pdf}}
-\label{stackspectrums}
+\caption{Graphed representation of features extracted for 3 different samples. }
+\label{fig:stackspectrums}
 \end{figure}
+
 % \begin{enumerate}
@@
     \textbf{Cross Validation F-Scores For All Sound Groups}\par\medskip
-    \makebox[\textwidth]{\includegraphics[width=0.8\paperwidth]{images/mme_comparisons_mme.pdf}}
+    \makebox[\textwidth]{\includegraphics[width=0.7\paperwidth]{images/mme_comparisons_mme.pdf}}
     \caption{Boxplots visualizing the F-Score results for each cross-validation.
+The individual scores, means, medians, standard-deviation and outliers are depicted.
+Envelope features improve classification accuracy.
+}
+    \label{fig:f1_allg_box}
+\end{center}
+
+\begin{center}
+        \textbf{Cross Validation F-Scores For Drum Vs Not-Drum}
+    \makebox[\textwidth]{\includegraphics[width=0.7\paperwidth]{images/mme_comparisons_dvn.pdf}}
+    \caption{F-Score results for each cross-validation. Models perform better as there are less categorization groups.  }
+    \label{fig:f1_dvn_box}
+\end{center}
+
+\label{fig:conf_f1_dvn}
+\end{figure}
+
+% \begin{figure}[h!]
+%     \begin{center}
+%     \textbf{Cross Validation F-Scores For All Sound Groups}\par\medskip
+%     \makebox[\textwidth]{\includegraphics[width=0.8\paperwidth]{images/mme_comparisons_mme.pdf}}
+%     \caption{Boxplots visualizing the F-Score results for each cross-validation.
 The individual scores, means, medians, standard-deviation and outliers are depicted.
@@
 }
-    \label{fig:f1_allg_box}
-    \end{center}
-\end{figure}
-
-We're also interested in how these models perform on the binary drum vs not drum task.
-After grouping all drums together, we repeat the model selection process above.
-We also repeat the hyper-parameter optimization step where no changes appeared necessary except for a reduction in the number of neighbors for the K-Neighbor model (from 30 to 5).
-As show in in Figures~\ref{fig:f1_allg_box} and~\ref{fig:f1_dvn_box}, the addition of envelope features had a positive effect on performance for all mdoels, yet the RandomForest and ExtraTrees models clearly outperform the other classifiers in both tasks.
-We train the top two models on \%80 of our database and use the remaining \%20 to create the confusion matrices and the F-Scores shown in Figures~\ref{fig:conf_f1_dvn}.
-\begin{figure}[h!]   
-    \begin{center}
-        \textbf{Cross Validation F-Scores For Drum Vs Not-Drum}
-    \makebox[\textwidth]{\includegraphics[width=0.8\paperwidth]{images/mme_comparisons_dvn.pdf}}
-    \caption{F-Score results for each cross-validation.
+%     \label{fig:f1_allg_box}
+%     \end{center}
+% \end{figure}
+% \begin{figure}[h!]   
+%     \begin{center}
+%         \textbf{Cross Validation F-Scores For Drum Vs Not-Drum}
+%     \makebox[\textwidth]{\includegraphics[width=0.8\paperwidth]{images/mme_comparisons_dvn.pdf}}
+%     \caption{F-Score results for each cross-validation.
 Models perform better as there are less categorization groups.
@@
 }
-    \label{fig:f1_dvn_box}
-    \end{center}
-\end{figure}
+%     \label{fig:f1_dvn_box}
+%     \end{center}
+% \end{figure}
+% We're also interested in how these models perform on the binary drum vs not drum task.
+% After grouping all drums together, we repeat the model selection process above.
+We also repeat the hyper-parameter optimization step where no changes appeared necessary except for a reduction in the number of neighbors for the K-Neighbor model (from 30 to 5).
+As show in in Figures~\ref{fig:f1_allg_box} and~\ref{fig:f1_dvn_box}, the addition of envelope features had a positive effect on performance for all mdoels, yet the RandomForest and ExtraTrees models clearly outperform the other classifiers in both tasks.
+We train the top two models on \%80 of our database and use the remaining \%20 to create the confusion matrices and the F-Scores shown in Figures~\ref{fig:conf_f1_dvn}.
 
@@
     \makebox[\textwidth]{
-    \subfloat[Precision, recall, F1-Score, and number of supporting examples]{ \includegraphics[width=9cm,height=9cm]{images/f1_mme.pdf}
-    \includegraphics[width=9cm,height=9cm]{images/f1_dvn.pdf}
+    \subfloat[Precision, recall, F1-Score, and number of supporting examples]{ \includegraphics[width=7cm,height=7cm]{images/f1_mme.pdf}
+    \includegraphics[width=7cm,height=7cm]{images/f1_dvn.pdf}
     }
@@
     \makebox[\textwidth]{
-    \subfloat[Confusion matrices]{ \includegraphics[width=9cm,height=9cm]{images/conf_mme.pdf}
-    \includegraphics[width=9cm,height=9cm]{images/conf_dvn.pdf}
+    \subfloat[Confusion matrices]{ \includegraphics[width=7cm,height=7cm]{images/conf_mme.pdf}
+    \includegraphics[width=7cm,height=7cm]{images/conf_dvn.pdf}
     }}
 \end{center}
-
-\caption{F-Scores and confusion matrix of ExtraTrees model for both DvDvN and drum vs not-drum categorization.}
+\caption{F-Scores and confusion matrix of ExtraTrees model for both DvDvN and DvN.}
 \label{fig:conf_f1_dvn}
@@
 
-Based on these reports, having multiple options for drum categorization does not noticeably influence our models accuracy in categorizing synthetic noise as synthetic noise.
+% Based on these reports, having multiple options for drum categorization does not noticeably influence our models accuracy in categorizing synthetic noise as synthetic noise.
 However, the DvDvN models's slightly smaller false negative rate for synthetic noise (11 vs 13 false negatives) is countered by a slightly higher rate of categorizing drums as synthetic noise (12 vs 9).
@@
 The trial's success is measured in their final loss value, calculated by applying the model to test data-set.
-Each trials consisted of 20 epoch of training using a selected set of hyper-parameters.
-An additional 100 trials with 40 epochs of training were conducted following the initial 500 to test the effect of longer epochs.
-Each trial's intermediate results (loss at every n epoch,s where $0<n<20$) were reported to a multi-armed bandit based pruner for early stoppage of unpromising trials~\cite{li2017hyperband}.
-We employed a tree-structured parzen estimator for better navigation of the search space~\cite{bergstra2011algorithms,akiba2019optuna} but found short reversions to a random sampling coupled with a decrease in the frequency of pruning helpful in exiting local minima.
-\\
+Each trial consisted of 20 epochs of training.
+
+\begin{table}[b!]
+\centering
+\begin{tabular}{|p{6cm}|p{6cm}|}
+\hline
+Hyper-Param. & Value  \\ \hline
+Model Type      &  CNN  \\ \hline
+Optimizer       & Adam  \\ \hline
+Hidden Layers   & Not Applicable  \\\hline
+Learning Rate   &  0.001145\\ \hline
+Frequency Bins & 30 \\ \hline
+Time Steps & 20 \\ \hline
+Latent Size & 64 \\ \hline
+Regularization & 3.25^{-6}\\ \hline
+Dropout Rate & 0.5 \\ \hline
+\end{tabular}
+\caption{Top performing hyper-parameter set}
+\label{table:best_params}
+\end{table}
 \begin{table}[htb]
@@
 
-\begin{figure}[htb]
-\centering
-\textbf{Tracing the Best Loss Values}
-\includegraphics[width=12cm,height=7cm]{images/Optimization_History.pdf}
-\caption{Best loss values found during hyper-parameter optimization. The effect of a switch to random sampling and an increase of the pruning threshold can be observed during trials 270 and 310.}
-\label{chap3:bestvalues}
-\end{figure}
+% \begin{figure}[htb]
+% \centering
+% \textbf{Tracing the Best Loss Values}
+% \includegraphics[width=12cm,height=7cm]{images/Optimization_History.pdf}
+% \caption{Best loss values found during hyper-parameter optimization. The effect of a switch to random sampling and an increase of the pruning threshold can be observed during trials 270 and 310.}
+% \label{chap3:bestvalues}
+% \end{figure}
 
-\begin{figure}
+\begin{figure}[tb]
 \begin{center}
@@
 \end{figure}
-
-\begin{table}[htb!]
-\centering
-\begin{tabular}{|p{6cm}|p{6cm}|}
-\hline
-Hyper-Param. & Value  \\ \hline
-Model Type      &  CNN  \\ \hline
-Optimizer       & Adam  \\ \hline
-Hidden Layers   & Not Applicable  \\\hline
-Learning Rate   &  0.001145\\ \hline
-Frequency Bins & 30 \\ \hline
-Time Steps & 20 \\ \hline
-Latent Size & 64 \\ \hline
-Regularization & 3.25^{-6}\\ \hline
-Dropout Rate & 0.5 \\ \hline
-\end{tabular}
-\caption{Top performing hyper-parameter set}
-\label{table:best_params}
-\end{table}
 

### 2020-10-10 templates_aimusic2020/paper.tex
Updates from Overleaf

@@
 Automatic programming~\footnote{unsupervised generation of source code or programs towards a goal} of virtual synthesizers has long been a topic of interest.
-Genetic Algorithms (GA's) have long been utilized for the generation of new sounds with various sound-engines~\cite{hornermachinetongues,macret2012automatic}.
+Genetic Algorithms (GA's) have been utilized for the generation of new sounds with various sound-engines~\cite{hornermachinetongues,macret2012automatic}.
 A more recent work by Yee-King et al.~\cite{yee2018automatic} used Long short-Term Memory (LSTM) models and heuristic search to find the exact parameters used to create a group of sounds.
@@
 Various works have demonstrated effective reconstruction of signals given their Short-time Fourier Transforms (STFT)~\cite{nawab1983signal,griffin1984signal}.
-If the STFT of a signal can be used for its reconstruction, perhaps it can be utilized as a source of fundamental features~\cite{lee2009unsupervised,hershey2017cnn}.
+If the STFT of a signal can be used for its reconstruction, perhaps it can be utilized as a source of fundamental features~\cite{lee2009unsupervised,huzaifah2017comparison}.
 We defined 3 STFT (or FFT) transformation functions to capture important features of percussive sounds.
@@
 
-To automatically learn from the extracted features, two groups of synthetic ears are implemented: \emph{two phased ears} (TPEs) and \emph{Mixed Ear Models} (MEMs).
+To automatically learn from the extracted features, two groups of virtual ears are implemented: \emph{two phased ears} (TPEs) and \emph{Mixed Ear Models} (MEMs).
 For TPEs, we train multiple neural network architectures using different subsets of the FFT features to specialize in \decfirst~or \decsecond~ and combine them to make decisions sequentially.
-To train TPEs for \decfirst, we use all drums in RadarDB and FreeDB and 6000 examples of synthesized noise.
+To train TPEs for \decfirst, we use all drums in RadarDB and FreeDB and 6000 examples of virtual synthesizer noise.
 For \decsecond, we combine the two databases and merge toms into kicks and rims/shakers into \enquote{other}.
@@
 High accuracy in detection of organic drums vs synthetic sounds does not necessarily make an ear more suitable for our generative system.
-Perfect detection of drums vs not-drums would create a system which generates nothing.
+Perfect detection of organic drums vs synthetic noise would create a system which generates nothing.
 We cannot know the true size of $\mathcal{H^{+}}$ (see Figure~\ref{fig:ven_data}) without exhaustive manual hearing tests.
@@
 
+\appendix
 \begin{appendices}
 \markboth{Appendix}{Appendix}
+\addcontentsline{toc}{section}{Appendices}
+\section*{Appendices}
 
-\chapter{Datasets, Details, and Downloads}
+\section{Datasets, Details, and Downloads}
 \label{appendix:datasets}
 \subsection{Download Instructions}
-FreeDB, survey data, and randomly generated sounds can be downloaded from: \url{https://zenodo.org/record/3994999}\\
-RadarDB requires lengthy downloads and processing.
-The script for its automated creation can be found under the \enquote{getting\_data} directory of our project code: \footnote{\url{https://github.com/imilas/Synths_Stacks_Search}}
+FreeDB, survey data, and randomly generated sounds can be downloaded from: \url{https://zenodo.org/record/3994999}\\\\
+RadarDB requires lengthy downloads and processing. The script for its automated creation can be found under the \enquote{getting\_data} directory of the project:\\
+\url{https://github.com/imilas/Synths_Stacks_Search}
+
 \subsection{Details}
@@
 
-\begin{table}[tb]
+\begin{table}[b]
 \centering
@@
 %==========================
-\chapter{Audio Transformation Functions}
+\clearpage
+\section{Audio Transformation Functions}
 \label{appendix:trans_funcitons}
@@
 %================
-\chapter{Virtual Ear Classifier Definitions}
+\clearpage
+\section{Virtual Ear Classifier Definitions}
 \label{appendix:classifier_definitions}
-\section{Two Phased models}
-Using the described features, we trained several neural network models for  decision 1and 2 in the Pytorch environment.
+\subsection{Two Phased models}
+Using the described features, we trained several neural network models for  decision 1 and 2 with the pytorch library.
 The task of decision 1 is to separate drums from not-drums (DrumVsNotDrum, or DVN).
@@
 We kept our feature space small, making it viable for feature selection and model design to be done on a trial and error basis.
-For all models, accuracy is calculated by prediction of all test dataset labels and the loss function and optimizer are Categorical-CrossEntropy and Adam respectively.
+For all models, accuracy is calculated by prediction of all test dataset labels and the loss function and optimizer are Categorical Cross-Entropy and Adam respectively.
 Training continues until no reduction in loss and accuracy is observed in 10 epochs.
@@
 %==============
-\chapter{AutoEncoder Structures and Hyper-Parameter Optimization}
+\clearpage
+\section{AutoEncoder Structures and Hyper-Parameter Optimization}
 \label{appendix:hyperparam}
@@
     \textbf{Hyper-Parameters' Loss Correlation}
-    \makebox[\textwidth]{\includegraphics[width=0.95\paperwidth]{images/slice_plot.pdf}}
+    \makebox[\textwidth]{\includegraphics[width=0.85\paperwidth]{images/slice_plot.pdf}}
       \caption{Sliced plot depicting the correlation between hyper-parameters and loss values.
@@
 % %==============
-\chapter{Survey Details}
+\clearpage
+\section{Survey Details}
 \label{appendix:surveys}

### 2020-10-10 templates_aimusic2020/paper.tex
spell &grammar check/table fixes

@@
 \caption{Synthesizer submodule parameters. $10^{15}$ unique programs are possible. Each synthesizer can contain any number of submodules}
-\resizebox{\columnwidth}{!}{\begin{tabular}{ |p{4cm}|p{4cm}|p{4cm}| } 
+\resizebox{\columnwidth}{!}{\begin{tabular}{ |>{\centering\arraybackslash}p{4cm}|>{\centering\arraybackslash}p{4cm}|>{\centering\arraybackslash}p{4cm}| } 
 \hline
-Parameters & Value Range & notes and constraints\\
+Parameters & Value Range & Notes and Constraints\\
 \hline \hline
@@
 
-\section{Datasets, Details, and Downloads}
+\section{Dataset Details and Downloads}
 \label{appendix:datasets}
@@
 RadarDB requires lengthy downloads and processing. The script for its automated creation can be found under the \enquote{getting\_data} directory of the project:\\
-\url{https://github.com/imilas/Synths_Stacks_Search}
+\url{https://github.com/imilas/Synths_Stacks_Search}. 
+\\\\
+Also included on github is our source-code, models, and extra output examples.
 
@@
 Specifications about our datasets can be found in tables~\ref{table:all_db}.
-We have made our dataset of free-drum sounds available for download.
-The scripts used to download and process royalty free samples are also made available.
 

### 2020-10-11 templates_aimusic2020/paper.tex
Updates from Overleaf

@@
 Automatic programming~\footnote{unsupervised generation of source code or programs towards a goal} of virtual synthesizers has long been a topic of interest.
-Genetic Algorithms (GA's) have been utilized for the generation of new sounds with various sound-engines~\cite{hornermachinetongues,macret2012automatic}.
+Genetic Algorithms (GA's) have been utilized for the generation of new sounds with various sound engines~\cite{hornermachinetongues,macret2012automatic}.
 A more recent work by Yee-King et al.~\cite{yee2018automatic} used Long short-Term Memory (LSTM) models and heuristic search to find the exact parameters used to create a group of sounds.
@@
 We call the number of submodules in each virtual synthesizer the \textit{stack size}.
-We call the sets of parameter values that characterize a synthesizer's submodules a \textit{program} (analogous to presets and submodules for a VST).
+We call the sets of parameter values that characterize a synthesizer's submodules a \textit{program}(analogous to presets and submodules for a VST).
  \begin{figure}[tb]
@@
     \item \textit{Flexibility and Scaling}: Probabilistic audio generation is often done sequentially.
-State of the art, parallel wave generation with GANs requires a fixed amount for rendering time for each time-step~\cite{yamamoto2020parallel}.
+State of the art, parallel wave generation with GANs requires a fixed amount of rendering time for each time-step~\cite{yamamoto2020parallel}.
 With our virtual synthesizer, the added footprint of increasing the length of rendered sounds or higher sampling rates is relatively minuscule.
@@
 \begin{table}[tb]
-\caption{Overview of model architectures. Further details in Appendix~\ref{appendix:classifier_definitions}}
+\caption{Overview of survey model architectures. Further details in Appendix~\ref{appendix:classifier_definitions}}
 \resizebox{\textwidth}{!}{%
@@
 }
+\label{table:brief_models}
 \end{table}
@@
 To automatically learn from the extracted features, two groups of virtual ears are implemented: \emph{two phased ears} (TPEs) and \emph{Mixed Ear Models} (MEMs).
-For TPEs, we train multiple neural network architectures using different subsets of the FFT features to specialize in \decfirst~or \decsecond~ and combine them to make decisions sequentially.
+For TPEs, we train multiple neural network architectures using different subsets of the FFT features to specialize in \decfirst~or \decsecond~and combine them to make decisions sequentially.
 To train TPEs for \decfirst, we use all drums in RadarDB and FreeDB and 6000 examples of virtual synthesizer noise.
@@
 Using 10-fold cross validation, our best MEM (an ExtraTrees Classifier) achieves the average f1-score of 92\% in 5-way sound classification (4 drum categories + synthesized noise).
-Detailed measurements and model descriptions for TPEs and MEMs can be found in Appendix~\ref{appendix:classifier_definitions}.
+Detailed measurements and model descriptions for TPEs and MEMs can be found in table~\ref{table:brief_models} and Appendix~\ref{appendix:classifier_definitions}.
 
@@
 High accuracy in detection of organic drums vs synthetic sounds does not necessarily make an ear more suitable for our generative system.
-Perfect detection of organic drums vs synthetic noise would create a system which generates nothing.
+Perfect detection would create a system which generates nothing.
 We cannot know the true size of $\mathcal{H^{+}}$ (see Figure~\ref{fig:ven_data}) without exhaustive manual hearing tests.
@@
 
-The percentage of sounds labeled as \enquote{bad} by the authors is a measurement of success with regards to \decfirst.
-We measure success with regards to \decsecond---the reliability of agreement between persons and drum categorization models---via the Fleiss' kappa coefficient \cite{fleiss1971measuring}.
-The value of 0 or less for this coefficient indicates no agreement beyond random chance, and the values of 1 indicates perfect agreement.
+The percentage of sounds labeled as \enquote{bad} by the authors is a measurement of success with regard to \decfirst.
+We measure success with regard to \decsecond---the reliability of agreement between persons and drum categorization models---via the Fleiss' kappa coefficient \cite{fleiss1971measuring}.
+The value of 0 or less for this coefficient indicates no agreement beyond random chance, and the value of 1 indicates perfect agreement.
 We re-measure this coefficient after dropping all \enquote{bad} and \enquote{other} samples.
@@
 RadarDB requires lengthy downloads and processing. The script for its automated creation can be found under the \enquote{getting\_data} directory of the project:\\
-\url{https://github.com/imilas/Synths_Stacks_Search}. 
+\url{https://github.com/imilas/Synths_Stacks_Search} 
+\\
+Also included on the project page is our full source-code, models, and extra output examples.
 \\\\
-Also included on github is our source-code, models, and extra output examples.
+The latex source for this paper can be found at:\\
+\url{https://github.com/imilas/CSMC-MuMe-2020}
 
@@
 We also created a database of synthetic noise from 1, 3, and 5 stacked virtual synthesizers.
-Specifications about our datasets can be found in tables~\ref{table:all_db}.
+Specifications about our datasets can be found in table~\ref{table:all_db}.
 
@@
 Using the optuna optimization tools \cite{akiba2019optuna}, we conducted 500 search trials.
-The trial's success is measured in their final loss value, calculated by applying the model to test data-set.
+The trial's success is measured in their final loss value, calculated by applying the model to the test data-set.
 Each trial consisted of 20 epochs of training.
